### 2021-11-02 Manuscript/Tmatrix.tex
starting working on manuscript

\documentclass[aip,jcp,reprint,noshowkeys,superscriptaddress]{revtex4-1}
\usepackage{graphicx,dcolumn,bm,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,longtable,wrapfig,txfonts}
\usepackage[version=4]{mhchem}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{txfonts}

\usepackage[
	colorlinks=true,
    citecolor=blue,
    breaklinks=true
	]{hyperref}
\urlstyle{same}

\newcommand{\ie}{\textit{i.e.}}
\newcommand{\eg}{\textit{e.g.}}
\newcommand{\alert}[1]{\textcolor{red}{#1}}
\usepackage[normalem]{ulem}
\newcommand{\titou}[1]{\textcolor{red}{#1}}
\newcommand{\trashPFL}[1]{\textcolor{red}{\sout{#1}}}
\newcommand{\trashXB}[1]{\textcolor{darkgreen}{\sout{#1}}}
\newcommand{\PFL}[1]{\titou{(\underline{\bf PFL}: #1)}}

\newcommand{\mc}{\multicolumn}
\newcommand{\fnm}{\footnotemark}
\newcommand{\fnt}{\footnotetext}
\newcommand{\tabc}[1]{\multicolumn{1}{c}{#1}}
\newcommand{\SI}{\textcolor{blue}{supporting information}}
\newcommand{\QP}{\textsc{quantum package}}
\newcommand{\T}[1]{#1^{\intercal}}

% coordinates
\newcommand{\br}{\mathbf{r}}
\newcommand{\bx}{\mathbf{x}}

% methods
\newcommand{\evGW}{ev$GW$}	
\newcommand{\qsGW}{qs$GW$}	
\newcommand{\GOWO}{$G_0W_0$}	
\newcommand{\Hxc}{\text{Hxc}}
\newcommand{\xc}{\text{xc}}
\newcommand{\Ha}{\text{H}}
\newcommand{\co}{\text{c}}
\newcommand{\x}{\text{x}}

% 
\newcommand{\Norb}{N_\text{orb}}
\newcommand{\Nocc}{O}
\newcommand{\Nvir}{V}

% operators
\newcommand{\hH}{\Hat{H}}
\newcommand{\hS}{\Hat{S}}

% methods
\newcommand{\KS}{\text{KS}}
\newcommand{\HF}{\text{HF}}
\newcommand{\RPA}{\text{RPA}}
\newcommand{\ppRPA}{\text{pp-RPA}}
\newcommand{\BSE}{\text{BSE}}
\newcommand{\dBSE}{\text{dBSE}}
\newcommand{\GW}{GW}
\newcommand{\GT}{GT}
\newcommand{\stat}{\text{stat}}
\newcommand{\dyn}{\text{dyn}}
\newcommand{\TDA}{\text{TDA}}

% energies
\newcommand{\Enuc}{E^\text{nuc}}
\newcommand{\Ec}{E_\text{c}}
\newcommand{\EHF}{E^\text{HF}}
\newcommand{\EBSE}{E^\text{BSE}}
\newcommand{\EcRPA}{E_\text{c}^\text{RPA}}
\newcommand{\EcBSE}{E_\text{c}^\text{BSE}}

% orbital energies
\newcommand{\e}[2]{\eps_{#1}^{#2}}
\newcommand{\eHF}[1]{\eps^\text{HF}_{#1}}
\newcommand{\eKS}[1]{\eps^\text{KS}_{#1}}
\newcommand{\eQP}[1]{\eps^\text{QP}_{#1}}
\newcommand{\eGOWO}[1]{\eps^\text{\GOWO}_{#1}}
\newcommand{\eGW}[1]{\eps^{GW}_{#1}}
\newcommand{\eevGW}[1]{\eps^\text{\evGW}_{#1}}
\newcommand{\eGnWn}[2]{\eps^\text{\GnWn{#2}}_{#1}}
\newcommand{\Om}[2]{\Omega_{#1}^{#2}}
\newcommand{\tOm}[2]{\Tilde{\Omega}_{#1}^{#2}}

% Matrix elements
\newcommand{\tA}[2]{\Tilde{A}_{#1}^{#2}}
\renewcommand{\S}[1]{S_{#1}}
\newcommand{\ABSE}[2]{A_{#1}^{#2,\text{BSE}}}
\newcommand{\BBSE}[2]{B_{#1}^{#2,\text{BSE}}}
\newcommand{\ARPA}[2]{A_{#1}^{#2,\text{RPA}}}
\newcommand{\BRPA}[2]{B_{#1}^{#2,\text{RPA}}}
\newcommand{\ARPAx}[2]{A_{#1}^{#2,\text{RPAx}}}
\newcommand{\BRPAx}[2]{B_{#1}^{#2,\text{RPAx}}}
\newcommand{\G}[1]{G_{#1}}
\newcommand{\LBSE}[1]{L_{#1}}
\newcommand{\XiBSE}[1]{\Xi_{#1}}
\newcommand{\Po}[1]{P_{#1}}
\newcommand{\W}[2]{W_{#1}^{#2}}
\newcommand{\tW}[2]{\widetilde{W}_{#1}^{#2}}
\newcommand{\Wc}[1]{W^\text{c}_{#1}}
\newcommand{\vc}[1]{v_{#1}}
\newcommand{\Sig}[2]{\Sigma_{#1}^{#2}}
\newcommand{\SigC}[1]{\Sigma^\text{c}_{#1}}
\newcommand{\SigX}[1]{\Sigma^\text{x}_{#1}}
\newcommand{\SigXC}[1]{\Sigma^\text{xc}_{#1}}
\newcommand{\Z}[1]{Z_{#1}}
\newcommand{\MO}[1]{\phi_{#1}}
\newcommand{\SO}[1]{\psi_{#1}}
\newcommand{\ERI}[2]{(#1|#2)}
\newcommand{\rbra}[1]{(#1|}
\newcommand{\rket}[1]{|#1)}
\newcommand{\sERI}[2]{[#1|#2]}

%% bold in Table
\newcommand{\bb}[1]{\textbf{#1}}
\newcommand{\rb}[1]{\textbf{\textcolor{red}{#1}}}
\newcommand{\gb}[1]{\textbf{\textcolor{darkgreen}{#1}}}

% excitation energies
\newcommand{\OmRPA}[1]{\Omega_{#1}^{\text{RPA}}}
\newcommand{\OmRPAx}[1]{\Omega_{#1}^{\text{RPAx}}}
\newcommand{\OmBSE}[1]{\Omega_{#1}^{\text{BSE}}}

% Matrices
\newcommand{\bO}{\mathbf{0}}
\newcommand{\bI}{\mathbf{1}}
\newcommand{\bvc}{\mathbf{v}}
\newcommand{\bSig}{\mathbf{\Sigma}}
\newcommand{\bSigX}{\mathbf{\Sigma}^\text{x}}
\newcommand{\bSigC}{\mathbf{\Sigma}^\text{c}}
\newcommand{\bSigGW}{\mathbf{\Sigma}^{GW}}
\newcommand{\be}{\mathbf{\epsilon}}
\newcommand{\beGW}{\mathbf{\epsilon}^{GW}}
\newcommand{\beGnWn}[1]{\mathbf{\epsilon}^\text{\GnWn{#1}}}
\newcommand{\bde}{\mathbf{\Delta\epsilon}}
\newcommand{\bdeHF}{\mathbf{\Delta\epsilon}^\text{HF}}
\newcommand{\bdeGW}{\mathbf{\Delta\epsilon}^{GW}}
\newcommand{\bOm}[1]{\mathbf{\Omega}^{#1}}
\newcommand{\bA}[2]{\mathbf{A}_{#1}^{#2}}
\newcommand{\bB}[2]{\mathbf{B}_{#1}^{#2}}
\newcommand{\bC}[2]{\mathbf{C}_{#1}^{#2}}
\newcommand{\bX}[2]{\mathbf{X}_{#1}^{#2}}
\newcommand{\bY}[2]{\mathbf{Y}_{#1}^{#2}}
\newcommand{\bZ}[2]{\mathbf{Z}_{#1}^{#2}}
\newcommand{\bK}{\mathbf{K}}
\newcommand{\bP}[1]{\mathbf{P}^{#1}}

% units
\newcommand{\IneV}[1]{#1 eV}
\newcommand{\InAU}[1]{#1 a.u.}
\newcommand{\InAA}[1]{#1 \AA}
\newcommand{\kcal}{kcal/mol}

% orbitals, gaps, etc
\newcommand{\eps}{\varepsilon}
\newcommand{\IP}{I}
\newcommand{\EA}{A}
\newcommand{\HOMO}{\text{HOMO}}
\newcommand{\LUMO}{\text{LUMO}}
\newcommand{\Eg}{E_\text{g}}
\newcommand{\EgFun}{\Eg^\text{fund}}
\newcommand{\EgOpt}{\Eg^\text{opt}}
\newcommand{\EB}{E_B}

\newcommand{\sig}{\sigma}
\newcommand{\bsig}{{\Bar{\sigma}}}
\newcommand{\sigp}{{\sigma'}}
\newcommand{\bsigp}{{\Bar{\sigma}'}}
\newcommand{\taup}{{\tau'}}

\newcommand{\up}{\uparrow}
\newcommand{\dw}{\downarrow}
\newcommand{\upup}{\uparrow\uparrow}
\newcommand{\updw}{\uparrow\downarrow}
\newcommand{\dwup}{\downarrow\uparrow}
\newcommand{\dwdw}{\downarrow\downarrow}
\newcommand{\spc}{\text{sc}}
\newcommand{\spf}{\text{sf}}
\newcommand{\ssp}{\text{ss}}
\newcommand{\osp}{\text{os}}

% addresses
\newcommand{\LCPQ}{Laboratoire de Chimie et Physique Quantiques (UMR 5626), Universit\'e de Toulouse, CNRS, UPS, France}
\newcommand{\LPT}{Laboratoire de Physique Th\'eorique, Universit\'e de Toulouse, CNRS, UPS, France}
\newcommand{\ETSF}{European Theoretical Spectroscopy Facility (ETSF)}
\begin{document}

\title{Static and Dynamic Bethe-Salpeter Equations in the $T$-Matrix Approximation}
\author{Pierre-Fran\c{c}ois \surname{Loos}}
	\email{loos@irsamc.ups-tlse.fr}
	\affiliation{\LCPQ}
\author{Pina Romaniello}
	\email{romaniello@irsamc.ups-tlse.fr}
	\affiliation{\LPT}
	\affiliation{\ETSF}

\begin{abstract}
We report, for the first time, the static and dynamic Bethe-Salpeter equations (BSE) within the so-called $T$-matrix approximation (BSE@$GT$).
The performance of the (static) BSE@$GT$ scheme and its perturbative dynamical correction (dBSE@$GT$) are assessed by computed the neutral excited states of molecular systems.
%\bigskip
%\begin{center}
%	\boxed{\includegraphics[width=0.5\linewidth]{TOC}}
%\end{center}
%\bigskip
\end{abstract}

\maketitle

Let us consider a closed-shell electronic system consisting of $N$ electrons and $K$ one-electron basis functions.
The number of singly-occupied and virtual (\ie, unoccupied) orbitals are $O = N$ and $V = K - O$, respectively.
Let us denote as $\SO{p}(\bx)$ the $p$th spinorbital and $\e{p}{}$ its one-electron energy.
The composite variable $\bx = (\sigma,\br)$ gathers spin ($\sigma$) and spatial ($\br$) variables.
We assume real quantities throughout this manuscript, $i$, $j$, $k$, and $l$ are occupied orbitals, $a$, $b$, $c$, and $d$ are unoccupied orbitals, $p$, $q$, $r$, and $s$ indicate arbitrary orbitals, $m$ labels single excitations, while $n$ labels double electron attachments or double electron detachments.

By definition, the one-body Green's function is
\begin{equation}
\label{eq:G}
	G(\bx_1,\bx_2;\omega) 
	= \sum_i \frac{\SO{i}(\bx_1) \SO{i}(\bx_2)}{\omega - \e{i}{} - i\eta}	
	+ \sum_a \frac{\SO{a}(\bx_1) \SO{a}(\bx_2)}{\omega - \e{a}{} + i\eta}	
\end{equation}
where $\eta$ is a positive infinitesimal, and its nature is completely defined by the set of orbitals and corresponding energies that are used to build it.

Contrary to the $GW$ approximation which relies on the (two-point) dynamically-screened Coulomb potential $W$ computed from a particle-hole random-phase approximation (ph-RPA) problem to target charged excitations, here we consider the $GT$ approximation where one employs the (four-point) $T$ matrix obtained from solving the particle-particle RPA (pp-RPA) equations.
The non-Hermitian pp-RPA problem reads
\begin{equation}
\label{eq:LR-RPA}
	\begin{pmatrix}
		\bA{}{\ppRPA}			&	\bB{}{\ppRPA}	\\
		-\T{(\bB{}{\ppRPA})}	&	-\bC{}{\ppRPA}	\\
	\end{pmatrix}
	\cdot
	\begin{pmatrix}
		\bX{n}{N\pm2}	\\
		\bY{n}{N\pm2}	\\
	\end{pmatrix}
	=
	\Om{n}{N\pm2}
	\begin{pmatrix}
		\bX{n}{N\pm2}	\\
		\bY{n}{N\pm2}	\\
	\end{pmatrix}
\end{equation}
where the elements of the various matrices are defined as
\begin{subequations}
\begin{align}
	A_{ab,cd}^{\ppRPA} & = \delta_{ab} \delta_{cd} (\e{a}{} + \e{b}{}) + \mel{ab}{}{cd}
	\\ 
	B_{ab,ij}^{\ppRPA} & = \mel{ab}{}{ij}
	\\ 
	C_{ij,kl}^{\ppRPA} & = - \delta_{ik} \delta_{jl} (\e{i}{} + \e{j}{}) +\mel{ij}{}{kl}
\end{align}
\end{subequations}
and 
\begin{equation}
	\mel{pq}{}{rs} = \braket{pq}{rs} - \braket{pq}{sr}
\end{equation}
are two-electron integrals in the spinorbital basis, \ie,
\begin{equation}
	\braket{pq}{rs} = \iint \SO{p}(\bx_1) \SO{q}(\bx_1) \frac{1}{\abs{\br_1 - \br_2}} \SO{r}(\bx_2) \SO{s}(\bx_2)  d\bx_1 d\bx_2
\end{equation}
The pp-RPA problem yields, in the absence of instabilities, $V(V-1)/2$ positive eigenvalues $\Om{n}{N+2}$ and $O(O-1)/2$ negative eigenvalues $\Om{n}{N-2}$, which  correspond respectively to double attachments and double detachments.
The pp-RPA correlation energies is given by \cite{Peng_2013,Scuseria_2013}
\begin{equation}
\begin{split}
	\Ec^\ppRPA 
	& = + \sum_n \Om{n}{N+2} - \Tr(\bA{}{\ppRPA}) 
	\\
	& = - \sum_n \Om{n}{N-2} - \Tr(\bC{}{\ppRPA})
\end{split}
\end{equation}

Based on the knowledge of the pp-RPA eigenvalues and eigenvectors, one can then construct the $T$ matrix.
In the spinorbital basis, the correlation part of the $T$ matrix has the following expression
\begin{equation}
\label{eq:T}
	T_{pq,rs}(\omega) 
		= \sum_{n} \frac{\braket*{pq}{\chi_n^{N+2}}\braket*{rs}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2}}
		\titou{-} \sum_{n} \frac{\braket*{pq}{\chi_n^{N-2}}\braket*{rs}{\chi_n^{N-2}}}{\omega - \Om{n}{N-2}}
\end{equation}
with
\begin{subequations}
\begin{align}
	\braket*{pq}{\chi_n^{N+2}} & = \sum_{c < d} \mel{pq}{}{cd} X_{cd,n}^{N+2} + \sum_{k < l}  \mel{pq}{}{kl} Y_{kl,n}^{N+2}
	\\
	\braket*{pq}{\chi_n^{N-2}} & = \sum_{c < d} \mel{pq}{}{cd} X_{cd,n}^{N-2} + \sum_{k < l}  \mel{pq}{}{kl} X_{kl,n}^{N-2}
\end{align}
\end{subequations}

Combining Eqs.~\eqref{eq:G} and \eqref{eq:T}, the correlation part of the $T$-matrix self-energy reads \cite{Zhang_2017}
\begin{equation}
	\Sigma^{T}_{pq}(\omega)
	= \sum_{in} \frac{\braket*{pi}{\chi_n^{N+2}}\braket*{qi}{\chi_n^{N+2}}}{\omega + \e{i}{} - \Om{n}{N+2}}
	+ \sum_{an} \frac{\braket*{pa}{\chi_n^{N-2}}\braket*{qa}{\chi_n^{N-2}}}{\omega + \e{a}{} - \Om{n}{N-2}}
\end{equation}

Within the (perturbative) one-shot $GT$ scheme (labeled as $G_0T_0$ in the following), the quasiparticle energies are obtained via linearization of the quasiparticle equation, \ie,
\begin{equation}
	\e{p}{G_0T_0} = \e{p}{\HF} + Z_p \Sigma^{T}_{pp}(\e{p}{\HF})
\end{equation}
where we have assumed a HF starting point and
\begin{equation}
	Z_p = \qty[ 1 - \eval{\pdv{\Sigma^{T}_{pq}(\omega)}{\omega}}_{\omega = \e{p}{\HF}} ]
\end{equation}
is the renormalization factor.
Other levels of self-consistency can be considered like the partially self-consistent \textit{``eigenvalue''} $GT$ (ev$GT$) or the quasiparticle self-consistent $GT$ (qs$GT$) scheme.

In order to target neutral excited states, we now consider the static version of the Bethe-Salpeter equation (BSE) employing the $G_0T_0$ quasiparticle energies as well as $T$-matrix kernel.
In this case, the BSE@$GT$ eigenvalue problem reads
\begin{equation}
\label{eq:LR-RPA}
	\begin{pmatrix}
		\bA{}{\BSE}		&	\bB{}{\BSE}	\\
		-\bB{}{\BSE}	&	-\bA{}{\BSE}	\\
	\end{pmatrix}
	\cdot
	\begin{pmatrix}
		\bX{m}{\BSE}	\\
		\bY{m}{\BSE}	\\
	\end{pmatrix}
	=
	\Om{m}{\BSE}
	\begin{pmatrix}
		\bX{m}{\BSE}	\\
		\bY{m}{\BSE}	\\
	\end{pmatrix}
\end{equation}
with 
\begin{subequations}
\begin{align}
	A_{ia,jb}^{\BSE} & = \delta_{ij} \delta_{ab} (\e{a}{\GT} + \e{i}{\GT}) + \mel{ib}{}{aj} + T_{ij,ba}(\omega=0)
	\\ 
	B_{ia,jb}^{\BSE} & = \mel{ij}{}{ab} + T_{ib,ja}(\omega=0)
\end{align}
\end{subequations}

In order to go beyond the static approximation, it is possible to consider a dynamical correction of the BSE (dBSE) within the Tamm-Dancoff approximation:
\begin{equation}
\label{eq:LR-RPA}
	\begin{pmatrix}
		\bA{}{\dBSE}(\omega)	&	\bB{}{\BSE}	\\
		-\bB{}{\BSE}	&	-\bA{}{\dBSE}(-\omega)	\\
	\end{pmatrix}
	\cdot
	\begin{pmatrix}
		\bX{S}{\dBSE}	\\
		\bY{S}{\dBSE}	\\
	\end{pmatrix}
	=
	\Om{S}{\dBSE}
	\begin{pmatrix}
		\bX{S}{\dBSE}	\\
		\bY{S}{\dBSE}	\\
	\end{pmatrix}
\end{equation}
with 
\begin{equation}
	A_{ia,jb}^{\dBSE}(\omega) = \delta_{ij} \delta_{ab} (\e{a}{\GT} + \e{i}{\GT}) + \mel{ib}{}{aj} + \widetilde{T}_{ij,ba}(\omega)
\end{equation}
where, following Strinati, \cite{Strinati_1988} one can derive the following expression for the elements of the dynamical $T$ matrix
\begin{equation}
\label{eq:dT}
\begin{split}
	\widetilde{T}_{pq,rs}(\omega) 
		& = \sum_{n} \frac{\braket*{pq}{\chi_n^{N+2}}\braket*{rs}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2} + (\e{i}{\GT} + \e{j}{\GT})}
		\\
		& + \sum_{n} \frac{\braket*{pq}{\chi_n^{N-2}}\braket*{rs}{\chi_n^{N-2}}}{\omega + \Om{n}{N-2} - (\e{a}{\GT} + \e{b}{\GT})}
\end{split}
\end{equation}
Equation \eqref{eq:dT} highlights the interesting dynamical structure of the $T$ matrix, where, similarly to the dBSE@$GW$ scheme, the 2h2p configurations are downfolded on the 1h1p configurations.
Although one can potentially access double excitations within this formalism (due to the dynamical nature of the equations), here we rely on the perturbative scheme developed in Ref.~\onlinecite{Loos_2020h} in order to access corrected single excitations.

%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{Tmatrix}
%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2021-11-03 Manuscript/Tmatrix.tex
saving work

@@
 Let us consider a closed-shell electronic system consisting of $N$ electrons and $K$ one-electron basis functions.
-The number of singly-occupied and virtual (\ie, unoccupied) orbitals are $O = N$ and $V = K - O$, respectively.
+The number of singly-occupied and virtual (\ie, unoccupied) spinorbitals are $O = N$ and $V = K - O$, respectively.
 Let us denote as $\SO{p}(\bx)$ the $p$th spinorbital and $\e{p}{}$ its one-electron energy.
@@
 
-By definition, the one-body Green's function is
+By definition, the one-body Green's function is \cite{Martin_2016}
 \begin{equation}
@@
 where $\eta$ is a positive infinitesimal, and its nature is completely defined by the set of orbitals and corresponding energies that are used to build it.
+For example, $G^{\HF}(\bx_1,\bx_2;\omega)$ is the Hartree-Fock (HF) Green's function built from the HF spinorbitals $\SO{p}^{\HF}(\bx)$ and energies $\e{p}{\HF}$.
 
-Contrary to the $GW$ approximation which relies on the (two-point) dynamically-screened Coulomb potential $W$ computed from a particle-hole random-phase approximation (ph-RPA) problem to target charged excitations, here we consider the $GT$ approximation where one employs the (four-point) $T$ matrix obtained from solving the particle-particle RPA (pp-RPA) equations.
-The non-Hermitian pp-RPA problem reads
+Contrary to the $GW$ approximation which relies on the (two-point) dynamically-screened Coulomb potential $W$ computed from a particle-hole random-phase approximation (ph-RPA) problem to target charged excitations (\ie, ionization potentials and electron affinities), \cite{Hedin_1965,Aryasetiawan_1998,Onida_2002,Martin_2016,Reining_2017,Golze_2019} here we consider the $GT$ approximation where one employs the (four-point) $T$ matrix obtained from solving the particle-particle RPA (pp-RPA) equations.
+The non-Hermitian pp-RPA problem reads \cite{Schuck_Book,vanAggelen_2013,Peng_2013,Scuseria_2013,Yang_2013,Yang_2013b,Yang_2014a}
 \begin{equation}
@@
 		= \sum_{n} \frac{\braket*{pq}{\chi_n^{N+2}}\braket*{rs}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2}}
-		\titou{-} \sum_{n} \frac{\braket*{pq}{\chi_n^{N-2}}\braket*{rs}{\chi_n^{N-2}}}{\omega - \Om{n}{N-2}}
+		+ \sum_{n} \frac{\braket*{pq}{\chi_n^{N-2}}\braket*{rs}{\chi_n^{N-2}}}{\omega - \Om{n}{N-2}}
 \end{equation}
@@
 
-Combining Eqs.~\eqref{eq:G} and \eqref{eq:T}, the correlation part of the $T$-matrix self-energy reads \cite{Zhang_2017}
+Combining Eqs.~\eqref{eq:G} and \eqref{eq:T}, the correlation part of the $T$-matrix self-energy reads \cite{Romaniello_2012,Martin_2016,Zhang_2017,Li_2021b}
 \begin{equation}
@@
 \begin{equation}
-	Z_p = \qty[ 1 - \eval{\pdv{\Sigma^{T}_{pq}(\omega)}{\omega}}_{\omega = \e{p}{\HF}} ]
+	Z_p = \qty[ 1 - \eval{\pdv{\Sigma^{T}_{pq}(\omega)}{\omega}}_{\omega = \e{p}{\HF}} ]^{-1}
 \end{equation}
@@
 
-In order to target neutral excited states, we now consider the static version of the Bethe-Salpeter equation (BSE) employing the $G_0T_0$ quasiparticle energies as well as $T$-matrix kernel.
-In this case, the BSE@$GT$ eigenvalue problem reads
+In order to target neutral (or optical) optical excitations, we now consider the static version of the Bethe-Salpeter equation (BSE) \cite{Salpeter_1951,Strinati_1988,Blase_2018,Blase_2020} employing the $GT$ quasiparticle energies as well as $T$-matrix kernel.
+In this case, the BSE@$GT$ linear eigenvalue problem reads
 \begin{equation}
-\label{eq:LR-RPA}
+\label{eq:BSE}
 	\begin{pmatrix}
@@
 \end{subequations}
+The eigenvalues of Eq.~\eqref{eq:BSE} provide $OV$ singlet and $OV$ triplet single excitations.
+Due to the frequency-independent nature of static BSE equations , it is well known that one cannot access higher excitations.
 
-In order to go beyond the static approximation, it is possible to consider a dynamical correction of the BSE (dBSE) within the Tamm-Dancoff approximation:
+In order to go beyond the static approximation, it is possible to consider a dynamical correction of the BSE (dBSE) within the Tamm-Dancoff approximation: \cite{Rohlfing_2000,Romaniello_2009b,Ma_2009a,Ma_2009b,Zhang_2013,Rebolini_2016,Olevano_2019,Loos_2020h,Authier_2020,Monino_2021}
 \begin{equation}

### 2021-11-03 Manuscript/Tmatrix.tex
saving work

@@
 
+The $GW$ approximation \cite{Hedin_1965} is an elegant resummation of all direct ring diagrams from the particle-hole (ph) channel and is justified in the high-density or weakly-correlated regime. 
+Within the $GW$ approximation, a key quantity of many-body perturbation theory, the self-energy $\Sigma$, reads
+\begin{equation}
+	\Sigma^{GW}(1,2) = i G(1,2) W(1,2)
+\end{equation}
+where $G(1,2)$ is the one-body Green's function and $W(1,2)$ is the dynamically-screened Coulomb potential, while, \eg, $1 \equiv (\sigma_1,\br_1,t_1)$ is a composite coordinate gathering spin, space, and time variables.
+
+Alternatives to $GW$ do exist.
+For example, the $T$-matrix (or Bethe-Goldstone) approximation, first introduced in nuclear physics and then in condensed matter physics, sums the ladder diagrams from the particle-particle (pp) channel
+and is justified in the low-density or strongly-correlated regime.
+While $GW$ considers a two-point interaction, the $T$-matrix approximation relies on a more complex (four-point) effective interaction --- the so-called $T$ matrix --- yielding the following self-energy:
+\begin{equation}
+	\Sigma^{GT}(1,2) = i \int G(4,3) T(1,3;2,4) d3 d4
+\end{equation}
+Combining these two channels, which sounds like a natural thing to do, is also possible and has been explored in the Hubbard dimer. \cite{Romaniello_2012}
+
 Let us consider a closed-shell electronic system consisting of $N$ electrons and $K$ one-electron basis functions.
@@
 
-Contrary to the $GW$ approximation which relies on the (two-point) dynamically-screened Coulomb potential $W$ computed from a particle-hole random-phase approximation (ph-RPA) problem to target charged excitations (\ie, ionization potentials and electron affinities), \cite{Hedin_1965,Aryasetiawan_1998,Onida_2002,Martin_2016,Reining_2017,Golze_2019} here we consider the $GT$ approximation where one employs the (four-point) $T$ matrix obtained from solving the particle-particle RPA (pp-RPA) equations.
+Contrary to the $GW$ approximation which relies on the (two-point) dynamically-screened Coulomb potential $W$ computed from a ph-random-phase approximation (ph-RPA) problem to target charged excitations (\ie, ionization potentials and electron affinities), \cite{Hedin_1965,Aryasetiawan_1998,Onida_2002,Martin_2016,Reining_2017,Golze_2019} here we consider the $GT$ approximation where one employs the (four-point) $T$ matrix obtained from solving the pp-RPA equations.
 The non-Hermitian pp-RPA problem reads \cite{Schuck_Book,vanAggelen_2013,Peng_2013,Scuseria_2013,Yang_2013,Yang_2013b,Yang_2014a}
@@
 	T_{pq,rs}(\omega) 
-		= \sum_{n} \frac{\braket*{pq}{\chi_n^{N+2}}\braket*{rs}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2}}
-		+ \sum_{n} \frac{\braket*{pq}{\chi_n^{N-2}}\braket*{rs}{\chi_n^{N-2}}}{\omega - \Om{n}{N-2}}
+		= \sum_{n} \frac{\braket*{pq}{\chi_n^{N+2}}\braket*{rs}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2} + i\eta}
+		- \sum_{n} \frac{\braket*{pq}{\chi_n^{N-2}}\braket*{rs}{\chi_n^{N-2}}}{\omega - \Om{n}{N-2} - i\eta}
 \end{equation}
@@
 \begin{equation}
-	\Sigma^{T}_{pq}(\omega)
-	= \sum_{in} \frac{\braket*{pi}{\chi_n^{N+2}}\braket*{qi}{\chi_n^{N+2}}}{\omega + \e{i}{} - \Om{n}{N+2}}
-	+ \sum_{an} \frac{\braket*{pa}{\chi_n^{N-2}}\braket*{qa}{\chi_n^{N-2}}}{\omega + \e{a}{} - \Om{n}{N-2}}
+	\Sigma^{GT}_{pq}(\omega)
+	= \sum_{in} \frac{\braket*{pi}{\chi_n^{N+2}}\braket*{qi}{\chi_n^{N+2}}}{\omega + \e{i}{} - \Om{n}{N+2} + i\eta}
+	+ \sum_{an} \frac{\braket*{pa}{\chi_n^{N-2}}\braket*{qa}{\chi_n^{N-2}}}{\omega + \e{a}{} - \Om{n}{N-2} - i\eta}
 \end{equation}
@@
 \begin{equation}
-	\e{p}{G_0T_0} = \e{p}{\HF} + Z_p \Sigma^{T}_{pp}(\e{p}{\HF})
+	\e{p}{G_0T_0} = \e{p}{\HF} + Z_p \Sigma^{GT}_{pp}(\e{p}{\HF})
 \end{equation}
@@
 
-In order to go beyond the static approximation, it is possible to consider a dynamical correction of the BSE (dBSE) within the Tamm-Dancoff approximation: \cite{Rohlfing_2000,Romaniello_2009b,Ma_2009a,Ma_2009b,Zhang_2013,Rebolini_2016,Olevano_2019,Loos_2020h,Authier_2020,Monino_2021}
+In order to go beyond the static approximation, it is possible to consider the dynamical version of the BSE (dBSE). \cite{Strinati_1988}
+In this case, one must solve the (non-linear) dynamical eigenvalue problem
 \begin{equation}
@@
 	\begin{pmatrix}
-		\bA{}{\dBSE}(\omega)	&	\bB{}{\BSE}	\\
-		-\bB{}{\BSE}	&	-\bA{}{\dBSE}(-\omega)	\\
+		\bA{}{\dBSE}(\Om{S}{\dBSE})	&	\bB{}{\BSE}	\\
+		-\bB{}{\BSE}	&	-\bA{}{\dBSE}(-\Om{S}{\dBSE})	\\
 	\end{pmatrix}
@@
 	\widetilde{T}_{pq,rs}(\omega) 
-		& = \sum_{n} \frac{\braket*{pq}{\chi_n^{N+2}}\braket*{rs}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2} + (\e{i}{\GT} + \e{j}{\GT})}
+		& = \sum_{n} \frac{\braket*{pq}{\chi_n^{N+2}}\braket*{rs}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2} + (\e{i}{\GT} + \e{j}{\GT}) + i\eta}
 		\\
-		& + \sum_{n} \frac{\braket*{pq}{\chi_n^{N-2}}\braket*{rs}{\chi_n^{N-2}}}{\omega + \Om{n}{N-2} - (\e{a}{\GT} + \e{b}{\GT})}
+		& + \sum_{n} \frac{\braket*{pq}{\chi_n^{N-2}}\braket*{rs}{\chi_n^{N-2}}}{\omega + \Om{n}{N-2} - (\e{a}{\GT} + \e{b}{\GT}) + i\eta}
 \end{split}
@@
 Equation \eqref{eq:dT} highlights the interesting dynamical structure of the $T$ matrix, where, similarly to the dBSE@$GW$ scheme, the 2h2p configurations are downfolded on the 1h1p configurations.
-Although one can potentially access double excitations within this formalism (due to the dynamical nature of the equations), here we rely on the perturbative scheme developed in Ref.~\onlinecite{Loos_2020h} in order to access corrected single excitations.
+Because solving a non-linear eigenvalue problem is computationally challenging, here we rely on the dynamical perturbative scheme within the Tamm-Dancoff approximation.
+\cite{Rohlfing_2000,Romaniello_2009b,Ma_2009a,Ma_2009b,Zhang_2013,Rebolini_2016,Olevano_2019,Loos_2020h,Authier_2020,Monino_2021}
+%lthough one can potentially access double excitations within this formalism (due to the dynamical nature of the equations), here we rely on the perturbative scheme developed in Ref.~\onlinecite{Loos_2020h} in order to access corrected single excitations.
+
+The present formalism has been implemented in QuAcK \cite{QuAcK} and we consider here only systems with closed-shell singlet ground states.
+The $GW$ and $GT$ calculations are performed by considering a (restricted) HF starting point and standard gaussian basis sets (defined with cartesian functions) are considered.
 

### 2021-11-03 Manuscript/Tmatrix.tex
improving BSE part

@@
 
-The $GW$ approximation \cite{Hedin_1965} is an elegant resummation of all direct ring diagrams from the particle-hole (ph) channel and is justified in the high-density or weakly-correlated regime. 
-Within the $GW$ approximation, a key quantity of many-body perturbation theory, the self-energy $\Sigma$, reads
+The $GW$ approximation \cite{Hedin_1965} is becoming a method of choice to target charged excitations (\ie, ionization potentials and electron affinities) in molecular systems.
+\cite{Aryasetiawan_1998,Onida_2002,Martin_2016,Reining_2017,Golze_2019}
+These so-called quasiparticle energies can be experimentally measured from direct and inverse photoemission spectroscopies.
+From a more theoretical point of view, it corresponds to an elegant resummation of all direct ring diagrams from the particle-hole (ph) channel which is particularly justified in the high-density or weakly-correlated regime.
+\cite{Gell-Mann_1957,Nozieres_1958}
+Within the $GW$ approximation, the self-energy --- one of the key quantity of Hedin's equations \cite{Hedin_1965} in many-body perturbation theory --- reads
 \begin{equation}
@@
 \end{equation}
-where $G(1,2)$ is the one-body Green's function and $W(1,2)$ is the dynamically-screened Coulomb potential, while, \eg, $1 \equiv (\sigma_1,\br_1,t_1)$ is a composite coordinate gathering spin, space, and time variables.
+where $G$ is the one-body Green's function, $W$ is the dynamically-screened Coulomb potential, and, \eg, $1 \equiv (\sigma_1,\br_1,t_1)$ is a composite coordinate gathering spin, space, and time variables.
 
 Alternatives to $GW$ do exist.
-For example, the $T$-matrix (or Bethe-Goldstone) approximation, first introduced in nuclear physics and then in condensed matter physics, sums the ladder diagrams from the particle-particle (pp) channel
-and is justified in the low-density or strongly-correlated regime.
-While $GW$ considers a two-point interaction, the $T$-matrix approximation relies on a more complex (four-point) effective interaction --- the so-called $T$ matrix --- yielding the following self-energy:
+For example, the $T$-matrix (or Bethe-Goldstone) approximation, first introduced in nuclear physics, \cite{Bethe_1957,Baym_1961,Baym_1962,Danielewicz_1984a,Danielewicz_1984b} then in condensed matter physics \cite{Liebsch_1981,Bickers_1989,Bickers_1991,Katsnelson_1999,Katsnelson_2002,Zhukov_2005,vonFriesen_2010,Romaniello_2012,Gukelberger_2015} and more recently in quantum chemistry, \cite{Zhang_2017,Li_2021b} sums to infinity the ladder diagrams from the particle-particle (pp) channel and is justified in the low-density or strongly-correlated regime.
+\cite{Danielewicz_1984a,Danielewicz_1984b,Liebsch_1981,Shepherd_2014}
+While the two-point screened interaction $W$ is the cornerstone of $GW$, the $T$-matrix approximation relies on a more complex (four-point) effective interaction --- the so-called $T$ matrix --- yielding the following self-energy:
 \begin{equation}
@@
 \end{equation}
-Combining these two channels, which sounds like a natural thing to do, is also possible and has been explored in the Hubbard dimer. \cite{Romaniello_2012}
+The natural idea of combining these two channels is also possible and has been explored in the Hubbard dimer. \cite{Romaniello_2012}
+One of the key features of the $T$-matrix approximation is its exactness up to the second order thanks to the inclusion of second-order exchange diagrams.
+This class of diagrams, which are particularly important in molecular systems, are missing in the $GW$ approximation.
 
-Let us consider a closed-shell electronic system consisting of $N$ electrons and $K$ one-electron basis functions.
+Let us consider closed-shell electronic systems consisting of $N$ electrons and $K$ one-electron basis functions.
 The number of singly-occupied and virtual (\ie, unoccupied) spinorbitals are $O = N$ and $V = K - O$, respectively.
@@
 
-Contrary to the $GW$ approximation which relies on the (two-point) dynamically-screened Coulomb potential $W$ computed from a ph-random-phase approximation (ph-RPA) problem to target charged excitations (\ie, ionization potentials and electron affinities), \cite{Hedin_1965,Aryasetiawan_1998,Onida_2002,Martin_2016,Reining_2017,Golze_2019} here we consider the $GT$ approximation where one employs the (four-point) $T$ matrix obtained from solving the pp-RPA equations.
+Contrary to the $GW$ approximation which relies on the (two-point) dynamically-screened Coulomb potential $W$ computed from a ph-random-phase approximation (ph-RPA) problem to target charged excitations, \cite{Hedin_1965,Aryasetiawan_1998,Onida_2002,Martin_2016,Reining_2017,Golze_2019} here we consider the $GT$ approximation where one employs the (four-point) $T$ matrix obtained from solving the pp-RPA equations.
 The non-Hermitian pp-RPA problem reads \cite{Schuck_Book,vanAggelen_2013,Peng_2013,Scuseria_2013,Yang_2013,Yang_2013b,Yang_2014a}
@@
 
-Within the (perturbative) one-shot $GT$ scheme (labeled as $G_0T_0$ in the following), the quasiparticle energies are obtained via linearization of the quasiparticle equation, \ie,
+Within the (perturbative) one-shot $GT$ scheme (labeled as $G_0T_0$ in the following), the quasiparticle energies are obtained via linearization of the quasiparticle equation, \cite{Strinati_1980,Hybertsen_1985a,Hybertsen_1986,Godby_1988,Linden_1988,Northrup_1991,Blase_1994,Rohlfing_1995,Shishkin_2007} \ie,
 \begin{equation}
+\label{eq:G0T0}
 	\e{p}{G_0T_0} = \e{p}{\HF} + Z_p \Sigma^{GT}_{pp}(\e{p}{\HF})
@@
 is the renormalization factor.
-Other levels of self-consistency can be considered like the partially self-consistent \textit{``eigenvalue''} $GT$ (ev$GT$) or the quasiparticle self-consistent $GT$ (qs$GT$) scheme.
+Other levels of self-consistency can be considered like the partially self-consistent \textit{``eigenvalue''} $GT$ (ev$GT$)  \cite{Hybertsen_1986,Shishkin_2007,Blase_2011,Faber_2011,Rangel_2016,Gui_2018} or the quasiparticle self-consistent $GT$ (qs$GT$) \cite{Faleev_2004,vanSchilfgaarde_2006,Kotani_2007,Ke_2011,Kaplan_2016} schemes.
 
-In order to target neutral (or optical) optical excitations, we now consider the static version of the Bethe-Salpeter equation (BSE) \cite{Salpeter_1951,Strinati_1988,Blase_2018,Blase_2020} employing the $GT$ quasiparticle energies as well as $T$-matrix kernel.
+Like the one-body Green's function is the pillar of the $GW$ and $GT$ approximations, the two-body Green's function $G_2$ is the key quantity of the Bethe-Salpeter equation (BSE) formalism of many-body perturbation theory \cite{Salpeter_1951,Strinati_1988,Blase_2018,Blase_2020} via its link with the two-body correlation function $L$ which satisfies the self-consistent BSE
+\begin{multline}
+	 iL(1,2;1',2') = L_0(1,2;1',2') 
+	 \\
+	 + \int L_0(1,4;1',3) \Xi(3,5;4,6) L(6,2;5,2') d3d4d5d6
+\end{multline}
+where
+\begin{subequations}
+\begin{align}
+	 iL_0(1,4;1',3) & = G(1,3) G(4,1')
+	 \\
+	 iL(1,2;1',2') & = -G_2(1,2;1',2') + G(1,1')G(2,2')
+\end{align}
+\end{subequations}
+and 
+\begin{equation}
+\label{eq:Xi}
+	\Xi(3,5;4,6) = i \fdv{\Sigma(3,4)}{G(6,5)}
+\end{equation}
+is the so-called BSE kernel that takes into account the self-consistent variation of $\Sigma$ with respect to the variation of $G$.
+By taking into account the interaction of the excited electron and its hole left behind (the infamous excitonic effect), the BSE is able to faithfully model (neutral) optical excitations as measured by absorption spectroscopy.
+The moderate cost of the BSE [which scales as $\order*{K^4}$ in its standard implementation] and its overall accuracy are the main reasons behind its growing popularity in the molecular electronic structure community.
+\cite{Rohlfing_1999a,Horst_1999,Puschnig_2002,Tiago_2003,Boulanger_2014,Jacquemin_2015a,Bruneval_2015,Jacquemin_2015b,Hirose_2015,Jacquemin_2017a,Jacquemin_2017b,Rangel_2017,Krause_2017,Gui_2018,Blase_2018,Liu_2020,Blase_2020,Holzer_2018a,Holzer_2018b,Loos_2020e,Loos_2021}
+
+In order to target neutral excited states, we first consider the static version of the Bethe-Salpeter equation (BSE) employing the $GT$ quasiparticle energies [see Eq.~\eqref{eq:G0T0}] as well as $T$-matrix kernel [\ie, $\Sigma^{\GT}$ in Eq.~\eqref{eq:Xi}].
 In this case, the BSE@$GT$ linear eigenvalue problem reads
@@
 The eigenvalues of Eq.~\eqref{eq:BSE} provide $OV$ singlet and $OV$ triplet single excitations.
-Due to the frequency-independent nature of static BSE equations , it is well known that one cannot access higher excitations.
+Due to the frequency-independent nature of static BSE equations it is well known that one cannot access double (and higher) excitations.
+\cite{Loos_2019,Romaniello_2009b,Sangalli_2011,Loos_2020h,Authier_2020,Monino_2021}
 
@@
 The present formalism has been implemented in QuAcK \cite{QuAcK} and we consider here only systems with closed-shell singlet ground states.
-The $GW$ and $GT$ calculations are performed by considering a (restricted) HF starting point and standard gaussian basis sets (defined with cartesian functions) are considered.
+The $GW$ and $GT$ calculations are performed by considering a (restricted) HF starting point and standard gaussian basis sets (defined with cartesian functions) are employed.
 

### 2021-11-03 Manuscript/Tmatrix.tex
introducing perturbative correction

@@
 By taking into account the interaction of the excited electron and its hole left behind (the infamous excitonic effect), the BSE is able to faithfully model (neutral) optical excitations as measured by absorption spectroscopy.
-The moderate cost of the BSE [which scales as $\order*{K^4}$ in its standard implementation] and its overall accuracy are the main reasons behind its growing popularity in the molecular electronic structure community.
+The moderate cost of the BSE [which scales as $\order*{K^4}$ in its standard implementation] and its all-round accuracy are the main reasons behind its growing popularity in the molecular electronic structure community.
 \cite{Rohlfing_1999a,Horst_1999,Puschnig_2002,Tiago_2003,Boulanger_2014,Jacquemin_2015a,Bruneval_2015,Jacquemin_2015b,Hirose_2015,Jacquemin_2017a,Jacquemin_2017b,Rangel_2017,Krause_2017,Gui_2018,Blase_2018,Liu_2020,Blase_2020,Holzer_2018a,Holzer_2018b,Loos_2020e,Loos_2021}
 
-In order to target neutral excited states, we first consider the static version of the Bethe-Salpeter equation (BSE) employing the $GT$ quasiparticle energies [see Eq.~\eqref{eq:G0T0}] as well as $T$-matrix kernel [\ie, $\Sigma^{\GT}$ in Eq.~\eqref{eq:Xi}].
+In order to target neutral excited states, we first consider the static version of the BSE employing the $GT$ quasiparticle energies [see Eq.~\eqref{eq:G0T0}] as well as $T$-matrix kernel [\ie, $\Sigma^{\GT}$ in Eq.~\eqref{eq:Xi}].
 In this case, the BSE@$GT$ linear eigenvalue problem reads
@@
 \begin{align}
-	A_{ia,jb}^{\BSE} & = \delta_{ij} \delta_{ab} (\e{a}{\GT} + \e{i}{\GT}) + \mel{ib}{}{aj} + T_{ij,ba}(\omega=0)
+	A_{ia,jb}^{\BSE} & = \delta_{ij} \delta_{ab} (\e{a}{\GT} - \e{i}{\GT}) + \mel{ib}{}{aj} + T_{ij,ba}(\omega=0)
 	\\ 
@@
 \end{subequations}
-The eigenvalues of Eq.~\eqref{eq:BSE} provide $OV$ singlet and $OV$ triplet single excitations.
-Due to the frequency-independent nature of static BSE equations it is well known that one cannot access double (and higher) excitations.
+The eigenvalues of Eq.~\eqref{eq:BSE} provide $OV$ singlet (\ie, spin-conserved) and $OV$ triplet  (\ie, spin-flip) single excitations.
+Due to the frequency-independent nature of static BSE, it is well known that one cannot access double (and higher) excitations.
 \cite{Loos_2019,Romaniello_2009b,Sangalli_2011,Loos_2020h,Authier_2020,Monino_2021}
 
-In order to go beyond the static approximation, it is possible to consider the dynamical version of the BSE (dBSE). \cite{Strinati_1988}
+In order to go beyond the static approximation, it is possible to consider the dynamical version of the BSE (dBSE) within the Tamm-Dancoff approximation. \cite{Strinati_1988}
 In this case, one must solve the (non-linear) dynamical eigenvalue problem
 \begin{equation}
-\label{eq:LR-RPA}
+\label{eq:dBSE}
 	\begin{pmatrix}
-		\bA{}{\dBSE}(\Om{S}{\dBSE})	&	\bB{}{\BSE}	\\
-		-\bB{}{\BSE}	&	-\bA{}{\dBSE}(-\Om{S}{\dBSE})	\\
+		\bA{}{\dBSE}(\Om{S}{})	&	\bB{}{\BSE}	\\
+		-\bB{}{\BSE}	&	-\bA{}{\dBSE}(-\Om{S}{})	\\
 	\end{pmatrix}
@@
 	=
-	\Om{S}{\dBSE}
+	\Om{S}{}
 	\begin{pmatrix}
@@
 \begin{equation}
-	A_{ia,jb}^{\dBSE}(\omega) = \delta_{ij} \delta_{ab} (\e{a}{\GT} + \e{i}{\GT}) + \mel{ib}{}{aj} + \widetilde{T}_{ij,ba}(\omega)
+	A_{ia,jb}^{\dBSE}(\omega) = \delta_{ij} \delta_{ab} (\e{a}{\GT} - \e{i}{\GT}) + \mel{ib}{}{aj} + \widetilde{T}_{ij,ba}(\omega)
 \end{equation}
-where, following Strinati, \cite{Strinati_1988} one can derive the following expression for the elements of the dynamical $T$ matrix
+where, following Strinati's seminal work, \cite{Strinati_1988} one can derive the following expression for the elements of the dynamical $T$ matrix
 \begin{equation}
@@
 \end{equation}
-Equation \eqref{eq:dT} highlights the interesting dynamical structure of the $T$ matrix, where, similarly to the dBSE@$GW$ scheme, the 2h2p configurations are downfolded on the 1h1p configurations.
-Because solving a non-linear eigenvalue problem is computationally challenging, here we rely on the dynamical perturbative scheme within the Tamm-Dancoff approximation.
+Equation \eqref{eq:dT} highlights the interesting dynamical structure of the $T$ matrix, where, similarly to the dBSE@$GW$ scheme, \cite{Strinati_1988,Romaniello_2009b,Loos_2020h} the 2h2p configurations are downfolded on the 1h1p configurations.
+
+Because solving a non-linear eigenvalue problem is computationally challenging, here we rely on the perturbative scheme developed in Ref.~\onlinecite{Loos_2020h} in order to access corrected single excitations.
 \cite{Rohlfing_2000,Romaniello_2009b,Ma_2009a,Ma_2009b,Zhang_2013,Rebolini_2016,Olevano_2019,Loos_2020h,Authier_2020,Monino_2021}
-%lthough one can potentially access double excitations within this formalism (due to the dynamical nature of the equations), here we rely on the perturbative scheme developed in Ref.~\onlinecite{Loos_2020h} in order to access corrected single excitations.
+For the sake of self-containedness, we quickly recap this dynamical perturbative scheme below.
+
+Based on Rayleigh-Schr\"odinger perturbation theory, the non-linear eigenproblem \eqref{eq:dBSE} can be split as a zeroth-order static (hence linear) reference and a first-order dynamic (hence non-linear) perturbation, such that
+\begin{multline}
+\label{eq:LR-PT}
+	\begin{pmatrix}
+		\bA{}{\dBSE}(\Om{S}{})		&	\bB{}{\BSE}(\Om{S}{})	\\
+		-\bB{}{\BSE}(-\Om{S}{})	&	-\bA{}{\BSE}(-\Om{S}{})	\\
+	\end{pmatrix}
+	\\
+	=
+	\begin{pmatrix}
+		\bA{}{\BSE}	&	\bB{}{\BSE}	
+		\\
+		-\bB{}{\BSE}	&	-\bA{}{\BSE}	
+		\\
+	\end{pmatrix}
+	+
+	\begin{pmatrix}
+		\bA{}{(1)}(\Om{S}{})		&	\bO	\\
+		\bO	&	-\bA{}{(1)}(-\Om{S}{})	\\
+	\end{pmatrix}
+\end{multline}
+with
+\begin{equation}
+	\label{eq:BSE-A1}
+	A_{ia,jb}^{(1)}(\omega) = \widetilde{T}_{ij,ab}(\omega) - T_{ij,ab}(\omega = 0)
+\end{equation}
+
+Perturbation theory teaches us that the $S$th BSE excitation energy and its corresponding eigenvector can then be expanded as
+\begin{subequations}
+\begin{gather}
+	\Om{S}{} = \Om{S}{\BSE} + \Om{S}{(1)} + \ldots,
+	\\
+	\begin{pmatrix}
+		\bX{S}{}	\\
+		\bY{S}{}	\\
+	\end{pmatrix}
+	= 
+	\begin{pmatrix}
+		\bX{S}{\BSE}	\\
+		\bY{S}{\BSE}	\\
+	\end{pmatrix}
+	+
+	\begin{pmatrix}
+		\bX{S}{(1)}	\\
+		\bY{S}{(1)}	\\
+	\end{pmatrix}
+	+ \ldots
+\end{gather}
+\end{subequations}
+Solving the static BSE [see Eq.~\eqref{eq:BSE}] yields the zeroth-order (static) $\Om{S}{\BSE}$ excitation energies and their corresponding eigenvectors $\bX{S}{\BSE}$ and $\bY{S}{\BSE}$. 
+Thanks to first-order perturbation theory, the first-order correction to the $S$th excitation energy is, within the Tamm-Dancoff approximation,
+\begin{equation}
+\label{eq:Om1-TDA}
+	\Om{S}{(1)} = \T{(\bX{S}{\BSE})} \cdot \bA{}{(1)}(\Om{S}{\BSE}) \cdot \bX{S}{\BSE}
+\end{equation}
+This correction can be renormalized by computing, at basically no extra cost, the renormalization factor which reads
+\begin{equation}
+\label{eq:Z}
+	\zeta_{S} = \qty[ 1 - \T{(\bX{S}{\BSE})} \cdot \left. \pdv{\bA{}{(1)}(\Om{S}{})}{\Om{S}{}} \right|_{\Om{S}{} = \Om{S}{\BSE}} \cdot \bX{S}{\BSE} ]^{-1}
+\end{equation}
+This finally yields
+\begin{equation}
+	\Om{S}{\text{dyn}} = \Om{S}{\text{stat}} + \Delta\Om{S}{\text{dyn}} = \Om{S}{\BSE} + \zeta_{S} \Om{S}{(1)}
+\end{equation}
+with $\Om{S}{\text{stat}} \equiv \Om{S}{\BSE}$ and $\Delta\Om{S}{\text{dyn}} = \zeta_{S} \Om{S}{(1)}$.
+Note that the present perturbative scheme does not allow to access double excitations as only excitations calculated within the static approach can be dynamically corrected.
+
+%In terms of computational cost, if one decides to compute the dynamical correction of the $M$ lowest excitation energies, one must perform, first, a conventional (static) BSE calculation and extract the $M$ lowest eigenvalues and their corresponding eigenvectors [see Eq.~\eqref{eq:LR-BSE-stat}].
+%These are then used to compute the first-order correction from Eq.~\eqref{eq:Om1-TDA}, which also require to construct and evaluate the dynamical part of the BSE Hamiltonian for each excitation one wants to dynamically correct.
+%The static BSE Hamiltonian is computed once during the static BSE calculation and does not dependent on the targeted excitation.
+%
+%Searching iteratively for the lowest eigenstates, via Davidson's algorithm for instance, can be performed in $\order*{\Norb^4}$ computational cost.
+%Constructing the static and dynamic BSE Hamiltonians is much more expensive as it requires the complete diagonalization of the $(\Nocc \Nvir \times \Nocc \Nvir)$ RPA linear response matrix [see Eq.~\eqref{eq:LR-RPA}], which corresponds to a $\order*{\Nocc^3 \Nvir^3} = \order*{\Norb^6}$ computational cost.
+%Although it might be reduced to $\order*{\Norb^4}$ operations with standard resolution-of-the-identity techniques, \cite{Duchemin_2019,Duchemin_2020} this step is the computational bottleneck in the current implementation.
+%
+%
+%All systems under investigation have a closed-shell singlet ground state.
+%We then adopt a restricted formalism throughout this work.
+%The $GW$ calculations performed to obtain the screened Coulomb operator and the quasiparticle energies are done using a (restricted) HF starting point.
+%Perturbative $GW$ (or {\GOWO}) \cite{Hybertsen_1985a,Hybertsen_1986,vanSetten_2013} quasiparticle energies are employed as starting points to compute the BSE neutral excitations.
+%These quasiparticle energies are obtained by linearizing the frequency-dependent quasiparticle equation, and the entire set of orbitals is corrected.
+%Further details about our implementation of {\GOWO} can be found in Refs.~\onlinecite{Loos_2018b,Veril_2018}.
+%Note that, for the present (small) molecular systems, {\GOWO}@HF and ev$GW$@HF yield similar quasiparticle energies and fundamental gap. 
+%Moreover, {\GOWO} allows to avoid rather laborious iterations as well as the significant additional computational effort of ev$GW$.
+%In the present study, the zeroth-order Hamiltonian [see Eq.~\eqref{eq:LR-PT}] is always the ``full'' BSE static Hamiltonian, \ie, without TDA.
+%The dynamical correction, however, is computed in the dTDA throughout.
+%As one-electron basis sets, we employ the Dunning families cc-pVXZ and aug-cc-pVXZ (X = D, T, and Q) defined with cartesian Gaussian functions. 
+%Finally, the infinitesimal $\eta$ is set to $100$ meV for all calculations.
+%It is important to mention that the small molecular systems considered here are particularly challenging for the BSE formalism, \cite{Hirose_2015,Loos_2018b} which is known to work best for larger systems where the amount of screening is more important.
+\cite{Jacquemin_2017b,Rangel_2017}
+%
+%For comparison purposes, we employ the theoretical best estimates (TBEs) and geometries of Refs.~\onlinecite{Loos_2018a,Loos_2019,Loos_2020b} from which CIS(D), \cite{Head-Gordon_1994,Head-Gordon_1995} ADC(2), \cite{Trofimov_1997,Dreuw_2015} CC2, \cite{Christiansen_1995a} CCSD, \cite{Purvis_1982} and CC3 \cite{Christiansen_1995b} excitation energies are also extracted.
+%Various statistical quantities are reported in the following: the mean signed error (MSE), mean absolute error (MAE), root-mean-square error (RMSE), and the maximum positive [Max($+$)] and maximum negative [Max($-$)] errors.
+%All the static and dynamic BSE calculations have been performed with the software \texttt{QuAcK}, \cite{QuAcK} freely available on \texttt{github}, where the present perturbative correction has been implemented.
 

### 2021-11-03 Manuscript/Tmatrix.tex
abstract

@@
 \begin{abstract}
-We report, for the first time, the static and dynamic Bethe-Salpeter equations (BSE) within the so-called $T$-matrix approximation (BSE@$GT$).
-The performance of the (static) BSE@$GT$ scheme and its perturbative dynamical correction (dBSE@$GT$) are assessed by computed the neutral excited states of molecular systems.
+While the well-established $GW$ approximation corresponds to a resummation of the direct ring diagrams and is particularly well suited for weakly-correlated systems, the $T$-matrix approximation does sum ladder diagrams up to infinity and is supposedly more appropriate in the presence of strong correlation.
+Here, we derive and implement, for the first time, the static and dynamic Bethe-Salpeter equations when one consider $T$-matrix quasiparticle energies as well as a $T$-matrix-based kernel.
+The performance of the static scheme and its perturbative dynamical correction are assessed by computed the neutral excited states of molecular systems.
+Comparison with more conventional schemes as well as other wave function methods are also performed.
 %\bigskip
@@
 The eigenvalues of Eq.~\eqref{eq:BSE} provide $OV$ singlet (\ie, spin-conserved) and $OV$ triplet  (\ie, spin-flip) single excitations.
+Note that the spin structure of the BSE@$GT$ equations are completely analogous to the BSE@$GW$ version. \cite{Monino_2021}
+Therefore, one can compute separately singlet and triplet excitation energies.
+
 Due to the frequency-independent nature of static BSE, it is well known that one cannot access double (and higher) excitations.
 \cite{Loos_2019,Romaniello_2009b,Sangalli_2011,Loos_2020h,Authier_2020,Monino_2021}
-
 In order to go beyond the static approximation, it is possible to consider the dynamical version of the BSE (dBSE) within the Tamm-Dancoff approximation. \cite{Strinati_1988}
@@
 The $GW$ and $GT$ calculations are performed by considering a (restricted) HF starting point and standard gaussian basis sets (defined with cartesian functions) are employed.
+\titou{Discuss the computational cost of the BSE@$GT$ equations.}
 

### 2021-11-03 Manuscript/Tmatrix.tex
adding comments here and there

@@
 These so-called quasiparticle energies can be experimentally measured from direct and inverse photoemission spectroscopies.
-From a more theoretical point of view, it corresponds to an elegant resummation of all direct ring diagrams from the particle-hole (ph) channel which is particularly justified in the high-density or weakly-correlated regime.
+From a more theoretical point of view, $GW$ corresponds to an elegant resummation of all direct ring diagrams from the particle-hole (ph) channel which is particularly justified in the high-density or weakly-correlated regime.
 \cite{Gell-Mann_1957,Nozieres_1958}
@@
 Alternatives to $GW$ do exist.
-For example, the $T$-matrix (or Bethe-Goldstone) approximation, first introduced in nuclear physics, \cite{Bethe_1957,Baym_1961,Baym_1962,Danielewicz_1984a,Danielewicz_1984b} then in condensed matter physics \cite{Liebsch_1981,Bickers_1989,Bickers_1991,Katsnelson_1999,Katsnelson_2002,Zhukov_2005,vonFriesen_2010,Romaniello_2012,Gukelberger_2015} and more recently in quantum chemistry, \cite{Zhang_2017,Li_2021b} sums to infinity the ladder diagrams from the particle-particle (pp) channel and is justified in the low-density or strongly-correlated regime.
+For example, the $T$-matrix (or Bethe-Goldstone) approximation, first introduced in nuclear physics, \cite{Bethe_1957,Baym_1961,Baym_1962,Danielewicz_1984a,Danielewicz_1984b} then in condensed matter physics, \cite{Liebsch_1981,Bickers_1989,Bickers_1991,Katsnelson_1999,Katsnelson_2002,Zhukov_2005,vonFriesen_2010,Romaniello_2012,Gukelberger_2015} and more recently in quantum chemistry, \cite{Zhang_2017,Li_2021b} sums to infinity the ladder diagrams from the particle-particle (pp) channel and is justified in the low-density or strongly-correlated regime.
 \cite{Danielewicz_1984a,Danielewicz_1984b,Liebsch_1981,Shepherd_2014}
@@
 \end{equation}
-The natural idea of combining these two channels is also possible and has been explored in the Hubbard dimer. \cite{Romaniello_2012}
+The natural idea of combining the ph and pp channels is also possible and has been explored in the Hubbard dimer. \cite{Romaniello_2012}
 One of the key features of the $T$-matrix approximation is its exactness up to the second order thanks to the inclusion of second-order exchange diagrams.
-This class of diagrams, which are particularly important in molecular systems, are missing in the $GW$ approximation.
+This class of diagrams, which are particularly important in molecular systems and explain the improvement brought by the second-order screened exchange (SOSEX) correction applied on top of $GW$, \cite{Romaniello_2009a,Ren_2015,Loos_2018b} are known to be missing in the $GW$ approximation.
 
@@
 \begin{equation}
+\label{eq:SigGT}
 	\Sigma^{GT}_{pq}(\omega)
@@
 \end{equation}
+While the dynamical $GW$ self-energy corresponds to the downfolding of the 2h1p and 2p1h configurations on the 1h and 1p configurations via their coupling with the 1h1p configurations, respectively, \cite{Bintrim_2021a} Eq.~\eqref{eq:SigGT} shows that, in the case of the $T$-matrix approximation, the same 2h1p and 2p1h configurations are downfolded on the 1p and 1h configurations via their coupling with the 2h and 2p configurations, respectively.
 
@@
 
-In order to target neutral excited states, we first consider the static version of the BSE employing the $GT$ quasiparticle energies [see Eq.~\eqref{eq:G0T0}] as well as $T$-matrix kernel [\ie, $\Sigma^{\GT}$ in Eq.~\eqref{eq:Xi}].
+In order to target neutral (singly-)excited states, we first consider the static version of the BSE employing the $GT$ quasiparticle energies [see Eq.~\eqref{eq:G0T0}] as well as $T$-matrix kernel [\ie, $\Sigma^{\GT}$ in Eq.~\eqref{eq:Xi}].
 In this case, the BSE@$GT$ linear eigenvalue problem reads
@@
 
-Due to the frequency-independent nature of static BSE, it is well known that one cannot access double (and higher) excitations.
+Due to the frequency-independent nature of the static BSE, it is well known that one cannot access double (and higher) excitations.
 \cite{Loos_2019,Romaniello_2009b,Sangalli_2011,Loos_2020h,Authier_2020,Monino_2021}
-In order to go beyond the static approximation, it is possible to consider the dynamical version of the BSE (dBSE) within the Tamm-Dancoff approximation. \cite{Strinati_1988}
+In order to go beyond the static approximation, it is possible to consider,  within the dynamical Tamm-Dancoff approximation (which neglects the frequency dependence of the coupling block) the dynamical version of the BSE (dBSE).
+\cite{Strinati_1988,Romaniello_2009b,Loos_2020h}
 In this case, one must solve the (non-linear) dynamical eigenvalue problem
@@
 Equation \eqref{eq:dT} highlights the interesting dynamical structure of the $T$ matrix, where, similarly to the dBSE@$GW$ scheme, \cite{Strinati_1988,Romaniello_2009b,Loos_2020h} the 2h2p configurations are downfolded on the 1h1p configurations.
+\cite{Bintrim_2021b}
 
-Because solving a non-linear eigenvalue problem is computationally challenging, here we rely on the perturbative scheme developed in Ref.~\onlinecite{Loos_2020h} in order to access corrected single excitations.
+Because solving a non-linear eigenvalue problem is computationally challenging, here we rely on the perturbative scheme developed in Ref.~\onlinecite{Loos_2020h} in order to access \textit{dynamically-corrected} single excitations for which additional relaxation effects coming from higher excitations are taken into account.
 \cite{Rohlfing_2000,Romaniello_2009b,Ma_2009a,Ma_2009b,Zhang_2013,Rebolini_2016,Olevano_2019,Loos_2020h,Authier_2020,Monino_2021}
@@
 
-Based on Rayleigh-Schr\"odinger perturbation theory, the non-linear eigenproblem \eqref{eq:dBSE} can be split as a zeroth-order static (hence linear) reference and a first-order dynamic (hence non-linear) perturbation, such that
+Based on Rayleigh-Schr\"odinger perturbation theory, the non-linear eigenproblem \eqref{eq:dBSE} can be split as a zeroth-order static reference and a first-order dynamic perturbation, such that
 \begin{multline}
@@
 \end{equation}
-
-Perturbation theory teaches us that the $S$th BSE excitation energy and its corresponding eigenvector can then be expanded as
+As usual, one can naturally expand the $S$th BSE excitation energy and its corresponding eigenvector as
 \begin{subequations}
@@
 \end{subequations}
-Solving the static BSE [see Eq.~\eqref{eq:BSE}] yields the zeroth-order (static) $\Om{S}{\BSE}$ excitation energies and their corresponding eigenvectors $\bX{S}{\BSE}$ and $\bY{S}{\BSE}$. 
-Thanks to first-order perturbation theory, the first-order correction to the $S$th excitation energy is, within the Tamm-Dancoff approximation,
+Solving the static BSE [see Eq.~\eqref{eq:BSE}] yields the (zeroth-order) static $\Om{S}{\BSE}$ excitation energies and their corresponding eigenvectors $\bX{S}{\BSE}$ and $\bY{S}{\BSE}$. 
+The first-order correction to the $S$th excitation energy is, within the dynamical Tamm-Dancoff approximation,
 \begin{equation}
@@
 \end{equation}
-This correction can be renormalized by computing, at basically no extra cost, the renormalization factor which reads
+This correction can be renormalized by computing, at no extra cost, the renormalization factor which reads
 \begin{equation}
@@
 \end{equation}
-This finally yields
+This yields our final expression for the dynamically-corrected BSE excitation energies:
 \begin{equation}
@@
 \end{equation}
-with $\Om{S}{\text{stat}} \equiv \Om{S}{\BSE}$ and $\Delta\Om{S}{\text{dyn}} = \zeta_{S} \Om{S}{(1)}$.
-Note that the present perturbative scheme does not allow to access double excitations as only excitations calculated within the static approach can be dynamically corrected.
+Note again that the present perturbative scheme does not allow to access double excitations as only excitations calculated within the static approach can be dynamically corrected.
 

### 2021-11-04 Manuscript/Tmatrix.tex
OK with theory section of the paper

@@
 While the well-established $GW$ approximation corresponds to a resummation of the direct ring diagrams and is particularly well suited for weakly-correlated systems, the $T$-matrix approximation does sum ladder diagrams up to infinity and is supposedly more appropriate in the presence of strong correlation.
-Here, we derive and implement, for the first time, the static and dynamic Bethe-Salpeter equations when one consider $T$-matrix quasiparticle energies as well as a $T$-matrix-based kernel.
+Here, we derive and implement, for the first time, the static and dynamic Bethe-Salpeter equations when one considers $T$-matrix quasiparticle energies as well as a $T$-matrix-based kernel.
 The performance of the static scheme and its perturbative dynamical correction are assessed by computed the neutral excited states of molecular systems.
-Comparison with more conventional schemes as well as other wave function methods are also performed.
+Comparison with more conventional schemes as well as other wave function methods are also reported.
 %\bigskip
@@
 
-The $GW$ approximation \cite{Hedin_1965} is becoming a method of choice to target charged excitations (\ie, ionization potentials and electron affinities) in molecular systems.
-\cite{Aryasetiawan_1998,Onida_2002,Martin_2016,Reining_2017,Golze_2019}
+The $GW$ approximation \cite{Hedin_1965} of many-body perturbation theory \cite{Martin_2016} is becoming a method of choice to target charged excitations (\ie, ionization potentials and electron affinities) in molecular systems.
+\cite{Aryasetiawan_1998,Onida_2002,Reining_2017,Golze_2019}
 These so-called quasiparticle energies can be experimentally measured from direct and inverse photoemission spectroscopies.
@@
 \cite{Gell-Mann_1957,Nozieres_1958}
-Within the $GW$ approximation, the self-energy --- one of the key quantity of Hedin's equations \cite{Hedin_1965} in many-body perturbation theory --- reads
+Within the $GW$ approximation, the self-energy --- one of the key quantities of Hedin's equations \cite{Hedin_1965} --- reads
 \begin{equation}
@@
 The natural idea of combining the ph and pp channels is also possible and has been explored in the Hubbard dimer. \cite{Romaniello_2012}
+
 One of the key features of the $T$-matrix approximation is its exactness up to the second order thanks to the inclusion of second-order exchange diagrams.
-This class of diagrams, which are particularly important in molecular systems and explain the improvement brought by the second-order screened exchange (SOSEX) correction applied on top of $GW$, \cite{Romaniello_2009a,Ren_2015,Loos_2018b} are known to be missing in the $GW$ approximation.
+This class of diagrams, which are particularly important in molecular systems and explain the improvement brought by the second-order screened exchange (SOSEX) correction applied to $GW$, \cite{Romaniello_2009a,Ren_2015,Loos_2018b} are well known to be missing in the $GW$ approximation.
 
@@
 Contrary to the $GW$ approximation which relies on the (two-point) dynamically-screened Coulomb potential $W$ computed from a ph-random-phase approximation (ph-RPA) problem to target charged excitations, \cite{Hedin_1965,Aryasetiawan_1998,Onida_2002,Martin_2016,Reining_2017,Golze_2019} here we consider the $GT$ approximation where one employs the (four-point) $T$ matrix obtained from solving the pp-RPA equations.
-The non-Hermitian pp-RPA problem reads \cite{Schuck_Book,vanAggelen_2013,Peng_2013,Scuseria_2013,Yang_2013,Yang_2013b,Yang_2014a}
+
+The non-Hermitian pp-RPA problem reads \cite{Schuck_Book,vanAggelen_2013,Peng_2013,Scuseria_2013,Yang_2013,Yang_2013b,vanAggelen_2014,Yang_2014a,Zhang_2015,Zhang_2016}
 \begin{equation}
@@
 \end{equation}
-The pp-RPA problem yields, in the absence of instabilities, $V(V-1)/2$ positive eigenvalues $\Om{n}{N+2}$ and $O(O-1)/2$ negative eigenvalues $\Om{n}{N-2}$, which  correspond respectively to double attachments and double detachments.
+The pp-RPA problem yields, in the absence of instabilities (which should not appear in Coulombic systems with repulsive interactions only \cite{Scuseria_2013}), $V(V-1)/2$ positive eigenvalues $\Om{n}{N+2}$ and $O(O-1)/2$ negative eigenvalues $\Om{n}{N-2}$, which  correspond respectively to double attachments and double detachments.
 The pp-RPA correlation energies is given by \cite{Peng_2013,Scuseria_2013}
@@
 In order to target neutral (singly-)excited states, we first consider the static version of the BSE employing the $GT$ quasiparticle energies [see Eq.~\eqref{eq:G0T0}] as well as $T$-matrix kernel [\ie, $\Sigma^{\GT}$ in Eq.~\eqref{eq:Xi}].
-In this case, the BSE@$GT$ linear eigenvalue problem reads
+In this case, the BSE@$GT$ linear eigenvalue problem simply reads
 \begin{equation}
@@
 \end{subequations}
-The eigenvalues of Eq.~\eqref{eq:BSE} provide $OV$ singlet (\ie, spin-conserved) and $OV$ triplet  (\ie, spin-flip) single excitations.
+The eigenvalues $\Om{m}{\BSE}$ of Eq.~\eqref{eq:BSE} provide $OV$ singlet (\ie, spin-conserved) and $OV$ triplet  (\ie, spin-flip) single excitations.
 Note that the spin structure of the BSE@$GT$ equations are completely analogous to the BSE@$GW$ version. \cite{Monino_2021}
@@
 \cite{Loos_2019,Romaniello_2009b,Sangalli_2011,Loos_2020h,Authier_2020,Monino_2021}
-In order to go beyond the static approximation, it is possible to consider,  within the dynamical Tamm-Dancoff approximation (which neglects the frequency dependence of the coupling block) the dynamical version of the BSE (dBSE).
+In order to go beyond the static approximation, it is possible to consider,  within the dynamical Tamm-Dancoff approximation (which neglects the frequency dependence of the coupling block $\bB{}{}$), the dynamical version of the BSE (dBSE).
 \cite{Strinati_1988,Romaniello_2009b,Loos_2020h}
@@
 \cite{Rohlfing_2000,Romaniello_2009b,Ma_2009a,Ma_2009b,Zhang_2013,Rebolini_2016,Olevano_2019,Loos_2020h,Authier_2020,Monino_2021}
-For the sake of self-containedness, we quickly recap this dynamical perturbative scheme below.
+Below, we quickly recap this dynamical perturbative scheme.
 

### 2022-01-26 Manuscript/Tmatrix.tex
minor corrections on manuscript; ready to add results

@@
 The $GW$ approximation \cite{Hedin_1965} of many-body perturbation theory \cite{Martin_2016} is becoming a method of choice to target charged excitations (\ie, ionization potentials and electron affinities) in molecular systems.
-\cite{Aryasetiawan_1998,Onida_2002,Reining_2017,Golze_2019}
+\cite{Aryasetiawan_1998,Onida_2002,Reining_2017,Golze_2019,Bruneval_2021}
 These so-called quasiparticle energies can be experimentally measured from direct and inverse photoemission spectroscopies.
@@
 \end{equation}
-The natural idea of combining the ph and pp channels is also possible and has been explored in the Hubbard dimer. \cite{Romaniello_2012}
+The natural idea of combining the ph and pp channels is also possible and has been explored, for example, in the Hubbard dimer within many-body perturbation theory \cite{Romaniello_2012} and the uniform electron gas \cite{Loos_2016} within coupled-cluster theory.
+\cite{Shepherd_2014}
 
@@
 Based on the knowledge of the pp-RPA eigenvalues and eigenvectors, one can then construct the $T$ matrix.
-In the spinorbital basis, the correlation part of the $T$ matrix has the following expression
+In the spinorbital basis, the correlation part of the $T$ matrix has the following expression \cite{Zhang_2016}
 \begin{equation}
@@
 	= \sum_{in} \frac{\braket*{pi}{\chi_n^{N+2}}\braket*{qi}{\chi_n^{N+2}}}{\omega + \e{i}{} - \Om{n}{N+2} + i\eta}
-	+ \sum_{an} \frac{\braket*{pa}{\chi_n^{N-2}}\braket*{qa}{\chi_n^{N-2}}}{\omega + \e{a}{} - \Om{n}{N-2} - i\eta}
+	- \sum_{an} \frac{\braket*{pa}{\chi_n^{N-2}}\braket*{qa}{\chi_n^{N-2}}}{\omega + \e{a}{} - \Om{n}{N-2} - i\eta}
 \end{equation}
@@
 \begin{equation}
-	Z_p = \qty[ 1 - \eval{\pdv{\Sigma^{T}_{pq}(\omega)}{\omega}}_{\omega = \e{p}{\HF}} ]^{-1}
+	Z_p = \qty[ 1 - \eval{\pdv{\Sigma^{T}_{pp}(\omega)}{\omega}}_{\omega = \e{p}{\HF}} ]^{-1}
 \end{equation}
@@
 \begin{align}
-	A_{ia,jb}^{\BSE} & = \delta_{ij} \delta_{ab} (\e{a}{\GT} - \e{i}{\GT}) + \mel{ib}{}{aj} + T_{ij,ba}(\omega=0)
+	A_{ia,jb}^{\BSE} & = \delta_{ij} \delta_{ab} (\e{a}{\GT} - \e{i}{\GT}) + \mel{ib}{}{aj} - T_{ib,aj}(\omega=0)
 	\\ 
-	B_{ia,jb}^{\BSE} & = \mel{ij}{}{ab} + T_{ib,ja}(\omega=0)
+	B_{ia,jb}^{\BSE} & = \mel{ij}{}{ab} - T_{ij,ab}(\omega=0)
 \end{align}
@@
 The eigenvalues $\Om{m}{\BSE}$ of Eq.~\eqref{eq:BSE} provide $OV$ singlet (\ie, spin-conserved) and $OV$ triplet  (\ie, spin-flip) single excitations.
-Note that the spin structure of the BSE@$GT$ equations are completely analogous to the BSE@$GW$ version. \cite{Monino_2021}
-Therefore, one can compute separately singlet and triplet excitation energies.
+Note that the spin structure of the BSE@$GT$ equations is analogous to the BSE@$GW$ version, \cite{Monino_2021} and one can compute separately singlet and triplet excitation energies.
 
@@
 \begin{equation}
-	A_{ia,jb}^{\dBSE}(\omega) = \delta_{ij} \delta_{ab} (\e{a}{\GT} - \e{i}{\GT}) + \mel{ib}{}{aj} + \widetilde{T}_{ij,ba}(\omega)
+	A_{ia,jb}^{\dBSE}(\omega) = \delta_{ij} \delta_{ab} (\e{a}{\GT} - \e{i}{\GT}) + \mel{ib}{}{aj} - \widetilde{T}_{ib,aj}(\omega)
 \end{equation}
@@
 \end{equation}
+from which, one can check that we recover the static expression \eqref{eq:T} in the limit $\Om{n}{N\pm2} \to \infty$.
 Equation \eqref{eq:dT} highlights the interesting dynamical structure of the $T$ matrix, where, similarly to the dBSE@$GW$ scheme, \cite{Strinati_1988,Romaniello_2009b,Loos_2020h} the 2h2p configurations are downfolded on the 1h1p configurations.
@@
 	\label{eq:BSE-A1}
-	A_{ia,jb}^{(1)}(\omega) = \widetilde{T}_{ij,ab}(\omega) - T_{ij,ab}(\omega = 0)
+	A_{ia,jb}^{(1)}(\omega) = \widetilde{T}_{ib,aj}(\omega) - T_{ib,aj}(\omega = 0)
 \end{equation}
@@
 
+The present formalism has been implemented in the software package \texttt{QuAcK} \cite{QuAcK} that is freely available on \texttt{github}. 
+We consider here only systems with closed-shell singlet ground states.
+Thus, the $GW$ and $GT$ calculations are performed by considering a (restricted) HF starting point and standard gaussian basis sets (defined with cartesian functions) are employed.
+Note that all quasiparticle energies which are obtained via Eq.~\eqref{eq:G0T0} are corrected in the same way.
+Finally, the infinitesimal $\eta$ is set to zero for all calculations.
+The ev$GT$ and qs$GT$ schemes have been also implemented but are not considered here.
+For the sake of completeness, implementable expressions in the spatial orbital basis are reported in the supporting information.
+
+In terms of computational, the overall scaling of BSE@$GT$ is equivalent to BSE@$GW$ as they both correspond to seeking the lowest eigenvalues of a matrix of size $(\Nocc \Nvir \times \Nocc \Nvir)$. 
+However, the prefactor corresponding to the calculations of the $T$-matrix and more specifically to the eigenvalue of the \titou{T2: Discuss the computational cost of the BSE@$GT$ equations, especially compare to BSE@$GW$.}
 %In terms of computational cost, if one decides to compute the dynamical correction of the $M$ lowest excitation energies, one must perform, first, a conventional (static) BSE calculation and extract the $M$ lowest eigenvalues and their corresponding eigenvectors [see Eq.~\eqref{eq:LR-BSE-stat}].
@@
 %Although it might be reduced to $\order*{\Norb^4}$ operations with standard resolution-of-the-identity techniques, \cite{Duchemin_2019,Duchemin_2020} this step is the computational bottleneck in the current implementation.
-%
-%
-%All systems under investigation have a closed-shell singlet ground state.
-%We then adopt a restricted formalism throughout this work.
-%The $GW$ calculations performed to obtain the screened Coulomb operator and the quasiparticle energies are done using a (restricted) HF starting point.
-%Perturbative $GW$ (or {\GOWO}) \cite{Hybertsen_1985a,Hybertsen_1986,vanSetten_2013} quasiparticle energies are employed as starting points to compute the BSE neutral excitations.
-%These quasiparticle energies are obtained by linearizing the frequency-dependent quasiparticle equation, and the entire set of orbitals is corrected.
-%Further details about our implementation of {\GOWO} can be found in Refs.~\onlinecite{Loos_2018b,Veril_2018}.
-%Note that, for the present (small) molecular systems, {\GOWO}@HF and ev$GW$@HF yield similar quasiparticle energies and fundamental gap. 
-%Moreover, {\GOWO} allows to avoid rather laborious iterations as well as the significant additional computational effort of ev$GW$.
-%In the present study, the zeroth-order Hamiltonian [see Eq.~\eqref{eq:LR-PT}] is always the ``full'' BSE static Hamiltonian, \ie, without TDA.
-%The dynamical correction, however, is computed in the dTDA throughout.
-%As one-electron basis sets, we employ the Dunning families cc-pVXZ and aug-cc-pVXZ (X = D, T, and Q) defined with cartesian Gaussian functions. 
-%Finally, the infinitesimal $\eta$ is set to $100$ meV for all calculations.
-%It is important to mention that the small molecular systems considered here are particularly challenging for the BSE formalism, \cite{Hirose_2015,Loos_2018b} which is known to work best for larger systems where the amount of screening is more important.
-\cite{Jacquemin_2017b,Rangel_2017}
-%
+
 %For comparison purposes, we employ the theoretical best estimates (TBEs) and geometries of Refs.~\onlinecite{Loos_2018a,Loos_2019,Loos_2020b} from which CIS(D), \cite{Head-Gordon_1994,Head-Gordon_1995} ADC(2), \cite{Trofimov_1997,Dreuw_2015} CC2, \cite{Christiansen_1995a} CCSD, \cite{Purvis_1982} and CC3 \cite{Christiansen_1995b} excitation energies are also extracted.
 %Various statistical quantities are reported in the following: the mean signed error (MSE), mean absolute error (MAE), root-mean-square error (RMSE), and the maximum positive [Max($+$)] and maximum negative [Max($-$)] errors.
-%All the static and dynamic BSE calculations have been performed with the software \texttt{QuAcK}, \cite{QuAcK} freely available on \texttt{github}, where the present perturbative correction has been implemented.
 
-The present formalism has been implemented in QuAcK \cite{QuAcK} and we consider here only systems with closed-shell singlet ground states.
-The $GW$ and $GT$ calculations are performed by considering a (restricted) HF starting point and standard gaussian basis sets (defined with cartesian functions) are employed.
-\titou{Discuss the computational cost of the BSE@$GT$ equations.}
+To conclude, the BSE@$GT$ formalism seems to be, overall, less accurate than BSE@$GW$ in the context of the computation of molecular excitation energies.
+However, it still outperforms conventional methods such CIS and TDHF.
+It would be interesting to investigate its performance for the computation of ground-state correlation energies within the adiabatic connection fluctuation dissipation formalism where BSE@$GW$ has been shown to be particularly outstanding.
+\cite{Maggio_2016,Holzer_2018b,Loos_2020e}
+The combination of $GT$ and $GW$ via the range separation of the Coulomb operator to avoid double counting of the low-order diagrams is also a promising avenue.
+Work along these lines are currently under progress.
 

### 2022-02-02 Manuscript/Tmatrix.tex
update work and data

@@
 \documentclass[aip,jcp,reprint,noshowkeys,superscriptaddress]{revtex4-1}
-\usepackage{graphicx,dcolumn,bm,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,longtable,wrapfig,txfonts}
+\usepackage{graphicx,dcolumn,bm,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,longtable,wrapfig,txfonts,siunitx}
 \usepackage[version=4]{mhchem}
@@
 \newcommand{\tabc}[1]{\multicolumn{1}{c}{#1}}
-\newcommand{\SI}{\textcolor{blue}{supporting information}}
+\newcommand{\SupInf}{\textcolor{blue}{supporting information}}
 \newcommand{\QP}{\textsc{quantum package}}
@@
 	\affiliation{\LCPQ}
+%\author{Roberto Orlando}
+%	\affiliation{\LCPQ}
+%	\affiliation{\LPT}
 \author{Pina Romaniello}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
+\label{sec:intro}
+%%%%%%%%%%%%%%%%%%%%%%
 The $GW$ approximation \cite{Hedin_1965} of many-body perturbation theory \cite{Martin_2016} is becoming a method of choice to target charged excitations (\ie, ionization potentials and electron affinities) in molecular systems.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%
+\section{Charged excitations}
+\label{sec:charged}
+%%%%%%%%%%%%%%%%%%%%%%
 By definition, the one-body Green's function is \cite{Martin_2016}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%
+\section{Neutral excitations}
+\label{sec:neutral}
+%%%%%%%%%%%%%%%%%%%%%%
 Like the one-body Green's function is the pillar of the $GW$ and $GT$ approximations, the two-body Green's function $G_2$ is the key quantity of the Bethe-Salpeter equation (BSE) formalism of many-body perturbation theory \cite{Salpeter_1951,Strinati_1988,Blase_2018,Blase_2020} via its link with the two-body correlation function $L$ which satisfies the self-consistent BSE
@@
 
-The present formalism has been implemented in the software package \texttt{QuAcK} \cite{QuAcK} that is freely available on \texttt{github}. 
+%%%%%%%%%%%%%%%%%%%%%%
+\section{Computational details}
+\label{sec:compdet}
+%%%%%%%%%%%%%%%%%%%%%%
+The present formalism has been implemented in the electronic structure package \texttt{QuAcK} \cite{QuAcK} that is freely available on \texttt{github}. 
 We consider here only systems with closed-shell singlet ground states. 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%
+\section{Results and discussion}
+\label{sec:res}
+%%%%%%%%%%%%%%%%%%%%%%
+
+First, we study the excited states of the hydrogen molecule \ce{H2} upon dissociation.
+Examples: hydrogem molecules, breaking the double bond of ethylene, BeH2,
+
+%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Excited states of the hydrogen molecule}
+\label{sec:h2}
+%%%%%%%%%%%%%%%%%%%%%%
+
+%%% FIGURE 1 %%%
+\begin{figure*}
+	\includegraphics[width=\textwidth]{H2}
+	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{H2} as a function of the interelectronic distance $R_{\ce{H-H}}$ (in \si{\angstrom}) obtained at the FCI/cc-pVDZ (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels.}
+\end{figure*}
+%%% %%% %%% %%%
+%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Diatomics}
+\label{sec:diatomics}
+%%%%%%%%%%%%%%%%%%%%%%
+
+%%% TABLE I %%%
+\begin{table*}
+	\begin{ruledtabular}
+		\begin{tabular}{lcccccc}
+					&			&	\mc{5}{c}{Methods}																\\
+			\cline{3-7}
+			Mol.	&	State	&	CIS		&	CIS(D)	&	TDHF	&	BSE@$GW$	&	BSE@$GT$	\\
+			\hline
+			\ce{H2}	&			&	\\
+			\ce{LiH}	&			&	\\
+			\ce{LiF}	&			&	\\
+			\ce{BF}	&			&	\\
+			\ce{CO}	&			&	\\
+			\ce{N2}	&			&	\\
+			\ce{F2}	&			&	\\
+			\ce{FH}	&			&	\\
+		\end{tabular}
+	\end{ruledtabular}
+\end{table*}
+%%% %%% %%% %%%
+
+%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}
+\label{sec:ccl}
+%%%%%%%%%%%%%%%%%%%%%%
 To conclude, the BSE@$GT$ formalism seems to be, overall, less accurate than BSE@$GW$ in the context of the computation of molecular excitation energies.
@@
 Work along these lines are currently under progress.
+Finally, the unrestricted and spin-flip extensions of the present formalism is currently developed.
 

### 2022-02-05 Manuscript/Tmatrix.tex
BeH2

@@
 	\affiliation{\LCPQ}
-%\author{Roberto Orlando}
-%	\affiliation{\LCPQ}
-%	\affiliation{\LPT}
 \author{Pina Romaniello}
@@
 
-First, we study the excited states of the hydrogen molecule \ce{H2} upon dissociation.
-Examples: hydrogem molecules, breaking the double bond of ethylene, BeH2,
-
 %%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%
+As a first didactical example, we consider the excited states of the hydrogen molecule \ce{H2} and the variation of the excitation energies upon dissociation.
+The excitation energies for some low-lying singlet and triplet excited states are represented in Fig.~\ref{fig:H2} as a function of the internuclear distance $R_{\ce{H-H}}$ at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
 
@@
 	\includegraphics[width=\textwidth]{H2}
-	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{H2} as a function of the interelectronic distance $R_{\ce{H-H}}$ (in \si{\angstrom}) obtained at the FCI/cc-pVDZ (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels.}
+	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
+	Raw data are reported in {\SupInf}.}
+	\label{fig:H2}
 \end{figure*}
 %%% %%% %%% %%%
+
+%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Excited states of beryllium hydride}
+\label{sec:beh2}
+%%%%%%%%%%%%%%%%%%%%%%
+
+%%% FIGURE 2 %%%
+\begin{figure*}
+	\includegraphics[width=\textwidth]{BeH2}
+	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{BeH2} as a function of the distance $R_{\ce{Be-H}}$ (in \si{\angstrom}) computed at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels.
+	The dynamically-corrected BSE excitation energies are represented as thin lines for dBSE@$G_0W_0$ (blue), and dBSE@$G_0T_0$ (red) with the cc-pVDZ basis.
+	Raw data are reported in {\SupInf}.}
+	\label{fig:H2}
+\end{figure*}
+%%% %%% %%% %%%
+
 %%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{table*}
+	\caption{Singlet and triplet excitation energies (in \si{\eV}) of various molecular systems at equilibrium geometry computed at various levels of theory with the cc-pVDZ basis set.
+	The corresponding experimental equilibrium geometries have been extracted from the computational chemistry comparison and benchmark database (CCCBDB) at \url{https://cccbdb.nist.gov}.}
+	\label{fig:mol}
 	\begin{ruledtabular}
-		\begin{tabular}{lcccccc}
+		\begin{tabular}{lcccccccc}
 					&			&	\mc{5}{c}{Methods}																\\
 			\cline{3-7}
-			Mol.	&	State	&	CIS		&	CIS(D)	&	TDHF	&	BSE@$GW$	&	BSE@$GT$	\\
+			Mol.	&	State	&	CIS		&	CIS(D)	&	TDHF	&	BSE@$GW$	&	dBSE@$GW$	&	BSE@$GT$	&	dBSE@$GT$	\\
 			\hline
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{acknowledgements}
+The authors thank Roberto Orlando for useful discussions.
+PFL thanks the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481) for funding.
+This project has also received financial support from the CNRS through the 80|Prime program and has been supported through the EUR grant NanoX ANR-17-EURE-0009 in the framework of the ``Programme des Investissements d’Avenir''.
+\end{acknowledgements}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+%\appendix
+%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+%\section{$T$-matrix self-energy in the spatial orbital basis}
+%%%%%%%%%%%%%%%%%%%%%%%%
+
+%Here, we provide implementable expressions for the $T$-matrix self-energy in the spatial orbital basis.
+
 %%%%%%%%%%%%%%%%%%%%%%%%

### 2022-02-09 Manuscript/Tmatrix.tex
comp details and appendix

@@
 Note that the spin structure of the BSE@$GT$ equations is analogous to the BSE@$GW$ version, \cite{Monino_2021} and one can compute separately singlet and triplet excitation energies.
+Neglecting the coupling between excitations and deexcitations, \ie, $\bB{}{\BSE} = \bO$, is known as the Tamm-Dancoff approximation (TDA).
 
@@
 \cite{Loos_2019,Romaniello_2009b,Sangalli_2011,Loos_2020h,Authier_2020,Monino_2021}
-In order to go beyond the static approximation, it is possible to consider,  within the dynamical Tamm-Dancoff approximation (which neglects the frequency dependence of the coupling block $\bB{}{}$), the dynamical version of the BSE (dBSE).
+In order to go beyond the static approximation, it is possible to consider, within the dynamical TDA (dTDA) that neglects the frequency dependence of the coupling block $\bB{}{}$, the dynamical version of the BSE (dBSE).
 \cite{Strinati_1988,Romaniello_2009b,Loos_2020h}
@@
 %%%%%%%%%%%%%%%%%%%%%%
-The present formalism has been implemented in the electronic structure package \texttt{QuAcK} \cite{QuAcK} that is freely available on \texttt{github}. 
+The present formalism has been implemented in the electronic structure package \texttt{QuAcK} \cite{QuAcK} which is freely available at \url{https://github.com/pfloos/QuAcK}. 
 We consider here only systems with closed-shell singlet ground states. 
@@
 The ev$GT$ and qs$GT$ schemes have been also implemented but are not considered here.
-For the sake of completeness, implementable expressions in the spatial orbital basis are reported in the supporting information.
+Although the dynamical correction is computed in the dTDA throughout, the zeroth-order excitonic Hamiltonian [see Eq.~\eqref{eq:BSE}] is always the ``full'' BSE static Hamiltonian, i.e., without TDA.
 
-In terms of computational, the overall scaling of BSE@$GT$ is equivalent to BSE@$GW$ as they both correspond to seeking the lowest eigenvalues of a matrix of size $(\Nocc \Nvir \times \Nocc \Nvir)$. 
-However, the prefactor corresponding to the calculations of the $T$-matrix and more specifically to the eigenvalue of the \titou{T2: Discuss the computational cost of the BSE@$GT$ equations, especially compare to BSE@$GW$.}
-%In terms of computational cost, if one decides to compute the dynamical correction of the $M$ lowest excitation energies, one must perform, first, a conventional (static) BSE calculation and extract the $M$ lowest eigenvalues and their corresponding eigenvectors [see Eq.~\eqref{eq:LR-BSE-stat}].
-%These are then used to compute the first-order correction from Eq.~\eqref{eq:Om1-TDA}, which also require to construct and evaluate the dynamical part of the BSE Hamiltonian for each excitation one wants to dynamically correct.
-%The static BSE Hamiltonian is computed once during the static BSE calculation and does not dependent on the targeted excitation.
-%
-%Searching iteratively for the lowest eigenstates, via Davidson's algorithm for instance, can be performed in $\order*{\Norb^4}$ computational cost.
-%Constructing the static and dynamic BSE Hamiltonians is much more expensive as it requires the complete diagonalization of the $(\Nocc \Nvir \times \Nocc \Nvir)$ RPA linear response matrix [see Eq.~\eqref{eq:LR-RPA}], which corresponds to a $\order*{\Nocc^3 \Nvir^3} = \order*{\Norb^6}$ computational cost.
-%Although it might be reduced to $\order*{\Norb^4}$ operations with standard resolution-of-the-identity techniques, \cite{Duchemin_2019,Duchemin_2020} this step is the computational bottleneck in the current implementation.
-
-%For comparison purposes, we employ the theoretical best estimates (TBEs) and geometries of Refs.~\onlinecite{Loos_2018a,Loos_2019,Loos_2020b} from which CIS(D), \cite{Head-Gordon_1994,Head-Gordon_1995} ADC(2), \cite{Trofimov_1997,Dreuw_2015} CC2, \cite{Christiansen_1995a} CCSD, \cite{Purvis_1982} and CC3 \cite{Christiansen_1995b} excitation energies are also extracted.
-%Various statistical quantities are reported in the following: the mean signed error (MSE), mean absolute error (MAE), root-mean-square error (RMSE), and the maximum positive [Max($+$)] and maximum negative [Max($-$)] errors.
+In terms of computational cost, the overall scaling of BSE@$GT$ is equivalent to BSE@$GW$ as they both correspond to seeking the lowest eigenvalues of a matrix of size $(2OV \times 2OV)$. 
+Searching iteratively for the lowest eigenstates can be routinely performed via Davidson's algorithm with a $\order*{K^4}$ computational cost. \cite{Davidson_1975}
+The cost of the dynamical correction, which is thoroughly discussed in Ref.~\onlinecite{Loos_2020h}, is more expensive but is again equivalent in both formalisms.
+The computational cost associated with the computation of the $T$-matrix and the screening $W$ both scale as $\order*{K^6}$ as one must obtain all the eigenvalues and eigenvectors of the pp-RPA and ph-RPA problem, respectively.
+However, the prefactor of the pp-RPA calculation is significantly larger than its ph-RPA counterpart due to the larger size of the pp-RPA matrices and its non-Hermitian nature.
+\cite{Peng_2013,Scuseria_2013,Yang_2013,Yang_2013b,Yang_2014a,Zhang_2015,Zhang_2016}
+Moreover, within the $T$-matrix formalism, one must compute both the singlet and triplet contributions of the $T$-matrix, while for singlet states, only the singlet contribution of $W$ contributes to the self-energy.
+Although similar approaches remain to be developed for the $T$-matrix formalism, contour deformation and density fitting techniques can be efficiently implemented in the case of $GW$ to reduce the scaling to $\order*{K^3}$.
+\cite{Duchemin_2019,Duchemin_2020,Duchemin_2021}
 
@@
 
+%%% FIGURE 2 %%%
+\begin{figure}
+	\includegraphics[width=\linewidth]{H2_gap}
+	\caption{HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap (in \si{\eV}) of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed at the BSE@$G_0W_0$ (blue) and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
+	Raw data are reported in {\SupInf}.}
+	\label{fig:H2}
+\end{figure}
+%%% %%% %%% %%%
+
 %%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%% FIGURE 2 %%%
+%%% FIGURE 3 %%%
 \begin{figure*}
@@
 \end{figure*}
+%%% %%% %%% %%%
+
+%%% FIGURE 4 %%%
+\begin{figure}
+	\includegraphics[width=\linewidth]{BeH2_gap}
+	\caption{HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap (in \si{\eV}) of \ce{BeH2} as a function of the internuclear distance $R_{\ce{Be-H}}$ (in \si{\angstrom}) computed at the BSE@$G_0W_0$ (blue) and BSE@$G_0T_0$ (red) levels with the cc-pVDZ basis.
+	Raw data are reported in {\SupInf}.}
+	\label{fig:H2}
+\end{figure}
 %%% %%% %%% %%%
@@
 		\begin{tabular}{lcccccccc}
-					&			&	\mc{5}{c}{Methods}																\\
-			\cline{3-7}
+					&			&	\mc{7}{c}{Methods}																\\
+			\cline{3-9}
 			Mol.	&	State	&	CIS		&	CIS(D)	&	TDHF	&	BSE@$GW$	&	dBSE@$GW$	&	BSE@$GT$	&	dBSE@$GT$	\\
@@
 \begin{acknowledgements}
-The authors thank Roberto Orlando for useful discussions.
+%The authors thank Roberto Orlando for useful discussions.
 PFL thanks the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481) for funding.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%
-%\appendix
+\onecolumngrid
+\appendix
 %%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{BSE with a dynamical kernel}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To recast the BSE with a dynamical $T$-matrix kernel as an eigenvalue equation, we follow Ref.~\onlinecite{Strinati_1980} and start from the equation for the BSE amplitude 
+\begin{equation}
+\label{eq:Strinati_1}
+	X_S(1,1^\prime) = \int d3d4d5d6L_0(1,4,1^\prime,3)\Xi(3,5,4,6) X_S(6,5)
+\end{equation}
+with 
+\begin{align}
+\label{eq:T-matrix_kernel}
+	L_0(1,4,1^\prime,3) & =-iG(1,3)G(4,1^\prime)
+	&
+	\Xi(3,5,4,6) & =  i\frac{\delta \Sigma(3,4)}{\delta G(6,5)}\approx -T(3,5,4,6)
+\end{align}
+where we consider the so-called $T$-matrix self-energy \cite{Martin_2016,Romaniello_2012} $\Sigma(3,4)=iG(7,8)T(3,8,4,7)$ with
+\begin{equation}
+\label{eq:T-matrix}
+	T(3,8,4,7) =
+	- v_c(3,8)\delta(3,4)\delta(7,8)
+	+ v_c(3,8)\delta(4,8)\delta(3,7)
+	+ iv_c(3,8)G(3,1')G(8,2')T(1',2',4,7)
+\end{equation}  
+and where we neglect the functional derivative $\delta T/\delta G$ in the kernel $\Xi$.
+Making the time dependence of Eq.~\eqref{eq:Strinati_1} explicit, one gets 
+\begin{multline}
+\label{eqn:DYN_T}
+	X_S(x_1,x_{1^\prime},\tau_{11'})e^{-i\omega_S(t_1+t_{1^\prime})/2}
+	=-i\int d3d4d5d6 G(x_1,x_3;\tau_{13})G(x_4,x_{1^\prime};\tau_{11^\prime})
+	\\
+	\times \bar{T}(x_3,x_5,x_4,x_6;\tau_{34})X_S(x_6,x_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}
+\end{multline}
+where $\tau^+_{ij}=t^+_i-t_j$ with $t^+_i=t_i+\eta$ ($\eta \to 0^+$) and $T(3,5,4,6)=- \delta(\tau^+_{35})\delta(\tau^+_{64})\bar{T}(x_3,x_5,x_4,x_6;\tau_{34})$ with 
+\begin{multline}
+\label{eq:T_bar}
+	\bar{T}(x_3,x_5,x_4,x_6;\tau_{34}) 
+	= v_c(x_3,x_5)\delta(\tau_{34})\delta(x_3,x_4)\delta(x_6,x_5)-v_c(x_3,x_5)\delta(\tau_{34})	\delta(x_3,x_6)\delta(x_4,x_5)
+	\\
+	+ iv_c(x_3,x_5)G(x_3,x_7;\tau_{38})G(x_5,x_8;\tau^+_{38})\bar{T}(x_7,x_8,x_4,x_6;\tau_{84})
+\end{multline}
+Using the Fourier transform $G(\tau)=\int \frac{d\omega}{2\pi}G(\omega)e^{-i\omega\tau}$, changing variable from $t_3$ to $\tau_{34}$ and taking the limit $t_{1^\prime}=t_1^+$ we arrive at
+\begin{multline}
+	X_S(x_1,x_{1^\prime},0^-)
+	= -i\int dx_3 dx_4 dx_5 dx_6\int d\tau_{34} \int \frac{d\nu'}{2\pi}G(x_1,x_3;\nu'+\omega_S)G(x_4,x_{1^\prime};\nu')e^{i\nu'\tau_{34}}
+	\\
+	 \times \bar{T}(x_3,x_5,x_4,x_6;\tau_{34})X_S(x_6,x_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}.
+\end{multline}
+Using the Lehman representation of the one-body Green's function in the quasiparticle approximation, i.e.
+$$G(x_1,x_2;\omega)=\sum_{p}\frac{\psi_p(x_1)\psi_p^*(x_2)}{\omega-\epsilon_p+ i\eta \text{sgn}(\epsilon_p-\mu)},$$ where $\psi_p$ and $\epsilon_p$ are single-particle wavefunctions and energies, respectively, and $\mu$ the chemical potential, and multiply left- and right-hand sides by $(\epsilon_a-\epsilon_i-\omega_S)\int dx_1dx^{\prime}_1 \psi^*_a(x_1)\psi_i(x_1^\prime)$.
+Using the fact that
+\begin{equation}
+	\Theta(\pm\tau)e^{-i\alpha \tau}=\mp\frac{1}{2\pi i}\lim_{\eta\to 0^+}\int d\omega \frac{1}{\omega-\alpha\pm i\eta}e^{-i\omega\tau}
+\end{equation}
+we then arrive at
+\begin{multline}
+\label{eq:General_DYN}
+	(\epsilon_a-\epsilon_i-\omega_S)\int dx_1dx^{\prime}_1 \psi^*_a(x_1)\psi_i(x_1^\prime)  X_S(x_1,x_{1^\prime},0^-) =
+	\\
+	-\int dx_3 dx_4 dx_5 dx_6\int d\tau_{34}\psi_a^*(x_3)\psi_i(x_4)
+	\qty[\Theta(\tau_{34})e^{i\epsilon_{i}\tau_{34}}+\Theta(-\tau_{34})e^{i(\epsilon_{a}-\omega_S)\tau_{34}} ]
+	\\
+	\times \bar{T}(x_3,x_5,x_4,x_6;\tau_{34})X_S(x_6,x_5;-\tau_{34})e^{i\omega_S\tau_{34}/2}
+\end{multline}
+
+We now consider the resonant case $\omega_m>0$, for which 
+\begin{equation}
+\label{Eqn:chi_tau}
+	X_S(x_1,x_{1^\prime},\tau_1) 
+	=-e^{i\omega_S\abs{\tau_1}/2} \sum_{pq}\psi_p(x_1)\psi^*_{q}(x_{1^\prime}) \mel{N}{\hat{c}^\dagger_{q}\hat{c}_p}{N,S}
+  	\qty[\Theta(\tau_1)e^{-i\epsilon_p\tau_1}+\Theta(-\tau_1)e^{-i\epsilon_{q}\tau_1} ]
+\end{equation}
+  where $\hat{c}^\dagger_{q}$ and $\hat{c}_p$ are creation and annihilation operators, respectively, and $\ket{N}$ and $\ket{N,S}$ are the ground state and the $S$-th excited state, respectively, of the $N$-electron system.
+After some algebraic steps we arrive at 
+\begin{multline}
+	-(\epsilon_a-\epsilon_i-\omega_S)\mel{N}{\hat{c}^\dagger_{i}\hat{c}_a}{N,S}
+	\\
+    = -\sum_{pq}\mel{N}{\hat{c}^\dagger_{q}\hat{c}_p}{N,S}
+    \qty{ -\frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\ \bar{T}_{iq,pa}(\omega) e^{-i\omega\eta}\left[\frac{1}{\omega_S-\omega+\epsilon_{q}+\epsilon_i+i\eta}+\frac{1}{\omega_S+\omega-\epsilon_p-\epsilon_a+i\eta}\right] }
+\end{multline}
+where we define 
+\begin{equation}
+	\bar{T}_{iq,pa}(\tau_{34})=\int dx_3x_4x_5x_6\int \psi_a^*(x_3)\psi_i(x_4)\bar{T}(x_3,x_5,x_4,x_6;\tau_{34}) \psi_p(x_6)\psi^*_{q}(x_5)
+\end{equation}
+Using the definition $A_S^{(qp)}=\langle N|\hat{c}^\dagger_{q}\hat{c}_p|N,S\rangle$, we arrive at
+
+\begin{equation}
+	\qty(\epsilon_a-\epsilon_i-\omega_S)A_S^{(ia)}+\sum_{pq}A_S^{(q p)}\widetilde{T}_{iq,pa}(\omega_S)=0,
+\end{equation}
+where we defined
+\begin{equation}
+	\widetilde{T}_{iq,pa}(\omega_S)
+	= \qty{ \frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\bar{T}_{iq,pa}(\omega)e^{-i\omega\eta} \left[\frac{1}{\omega_S-\omega+\epsilon_{q}+\epsilon_i+i\eta}+\frac{1}{\omega_S+\omega-\epsilon_p-\epsilon_a+i\eta}\right]  }
+ \label{Eqn:H2preso_eigen_2_T}
+\end{equation}
+
+This is an eigenvalue equation to calculate the positive excitation energies of a system, which can be rewritten as,
+\begin{equation}
+\label{eq:H2preso_eigen}
+	H^{2p,reso}_{ia,qp}(\omega_S)A_S^{(qp)}=\omega_S A^{(ia)}_S,
+\end{equation}
+with
+\begin{equation}
+	H^{2p,reso}_{ia,qp}(\omega_S)=(\epsilon_a-\epsilon_i)\delta_{iq}\delta_{ap} + \mel{ip}{}{aq}+\widetilde{T}_{iq,pa}(\omega_S).
+\end{equation}
+Here $H^{2p,reso}_{ia,jb}(\omega_S)=A_{ia,jb}(\omega_S)$ and $H^{2p,reso}_{ia,bj}(\omega_S)=B_{ia,jb}(\omega_S)$.
+If we drop the correlation part of $\bar{T}$ [the first two terms on the right-hand side of Eq.~\eqref{eq:T_bar}] we obtain the TDHF equations.
+To calculate the correlation contribution we use \alert{Eq.~(9)} in Eq.~\eqref{Eqn:H2preso_eigen_2_T}, and after integration over the frequency we arrive at \alert{Eq.~(21).}
 
 %%%%%%%%%%%%%%%%%%%%%%%%
-%\section{$T$-matrix self-energy in the spatial orbital basis}
-%%%%%%%%%%%%%%%%%%%%%%%%
-
-%Here, we provide implementable expressions for the $T$-matrix self-energy in the spatial orbital basis.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
+\twocolumngrid
 \bibliography{Tmatrix}

### 2022-02-09 Manuscript/Tmatrix.tex
saving work b4 transfer to overleaf

@@
 The cost of the dynamical correction, which is thoroughly discussed in Ref.~\onlinecite{Loos_2020h}, is more expensive but is again equivalent in both formalisms.
-The computational cost associated with the computation of the $T$-matrix and the screening $W$ both scale as $\order*{K^6}$ as one must obtain all the eigenvalues and eigenvectors of the pp-RPA and ph-RPA problem, respectively.
+The computational cost associated with the computation of the $T$-matrix and the screening $W$ both scale as $\order*{K^6}$ as one must obtain, respectively, all the eigenvalues and eigenvectors of the pp-RPA and ph-RPA problems.
 However, the prefactor of the pp-RPA calculation is significantly larger than its ph-RPA counterpart due to the larger size of the pp-RPA matrices and its non-Hermitian nature.
@@
 %%%%%%%%%%%%%%%%%%%%%%
-As a first didactical example, we consider the excited states of the hydrogen molecule \ce{H2} and the variation of the excitation energies upon dissociation.
-The excitation energies for some low-lying singlet and triplet excited states are represented in Fig.~\ref{fig:H2} as a function of the internuclear distance $R_{\ce{H-H}}$ at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
+As a first didactical example, we consider the lowest singlet and triplet excited states of the hydrogen molecule \ce{H2} and the variation of their respective excitation energies upon dissociation.
+The excitation energies associated with these low-lying singlet and triplet excited states are represented in Fig.~\ref{fig:H2} as a function of the internuclear distance $R_{\ce{H-H}}$ at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
+The variation of the HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:H2_gap}
 
@@
 	\includegraphics[width=\linewidth]{H2_gap}
-	\caption{HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap (in \si{\eV}) of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed at the BSE@$G_0W_0$ (blue) and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
+	\caption{HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap (in \si{\eV}) of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed at the $G_0W_0$ (blue) and $G_0T_0$ (red) levels with the cc-pVTZ basis.
 	Raw data are reported in {\SupInf}.}
-	\label{fig:H2}
+	\label{fig:H2_gap}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%
+As a second example, we consider the symmetric dissociation of the linear molecule beryllium hydride \ce{BeH2}.
+The variation in excitation energies as a function of the distance $R_{\ce{Be-H}}$ is shown in Fig.~\ref{fig:BeH2}.
+The variation of the HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:BeH2_gap}
 
@@
 	Raw data are reported in {\SupInf}.}
-	\label{fig:H2}
+	\label{fig:BeH2}
 \end{figure*}
@@
 	Raw data are reported in {\SupInf}.}
-	\label{fig:H2}
+	\label{fig:BeH2_gap}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%
-\subsection{Diatomics}
-\label{sec:diatomics}
+\subsection{Molecules at equilibrium}
+\label{sec:mol}
 %%%%%%%%%%%%%%%%%%%%%%
+
+Table \ref{tab:mol} reports singlet and triplet vertical excitation energies for various molecular systems at equilibrium geometry.
+In addition to the BSE-based models studied in the present manuscript, we have selected well-known methods \titou{(CIS, CIS(D), TDHF and FCI)}.
 
@@
 	The corresponding experimental equilibrium geometries have been extracted from the computational chemistry comparison and benchmark database (CCCBDB) at \url{https://cccbdb.nist.gov}.}
-	\label{fig:mol}
+	\label{tab:mol}
 	\begin{ruledtabular}

### 2022-02-09 Manuscript/Tmatrix_appendix.tex
add figs and appendix files

\documentclass[a4paper,superscriptaddress,twocolumn,aps,prb,floatfix,citeautoscript]{revtex4-1}\usepackage[utf8]{inputenc}
\usepackage{times} 
\usepackage{graphicx}
\usepackage{color}
%\usepackage{lscape}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{bm}
\usepackage{url}
%\usepackage{ulem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
%\usepackage{subcaption}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}

\begin{document}

\section{BSE with a dynamical  kernel}
\subsection{T-matrix kernel}
To recast the Bethe-Salpeter equation with a dynamical T-matrix kernel as an eigenvalue equation we follow Ref.[Strinati]. We start from the equation for the Bethe-Salpeter amplitude $X_S$
\begin{equation}
X_S(1,1^\prime)=\int d3d4d5d6L_0(1,4,1^\prime,3)\Xi(3,5,4,6) X_S(6,5),
\label{Eqn:Strinati_1}
\end{equation}
with 
\bea
L_0(1,4,1^\prime,3)&=&-iG(1,3)G(4,1^\prime)\\
\Xi(3,5,4,6)&=&i\frac{\delta \Sigma(3,4)}{\delta G(6,5)}\approx -T(3,5,4,6),
\label{Eqn:T-matrix_kernel}
\eea
where we considered $\Sigma(3,4)=iG(7,8)T(3,8,4,7)$  \cite{Lucia_book,pina_PRB2012}with
\bea
T(3,8,4,7) &=&-v_c(3,8)\delta(3,4)\delta(7,8)+v_c(3,8)\delta(4,8)\delta(3,7)\nonumber\\
&+&iv_c(3,8)G(3,1')G(8,2')T(1',2',4,7)
\label{Eqn:T-matrix}
\eea
and we neglect the functional derivative $\delta T/\delta G$ in the kernel $\Xi$.
We now make explicit the time dependence of Eq.\ (\ref{Eqn:Strinati_1}). We get 
\begin{widetext}
\begin{eqnarray}
  X_S(x_1,x_{1^\prime},\tau_{11'})e^{-i\omega_S(t_1+t_{1^\prime})/2}&=&-i\int d3456 G(x_1,x_3;\tau_{13})G(x_4,x_{1^\prime};\tau_{11^\prime})\times\nonumber\\
  &&\bar{T}(x_3,x_5,x_4,x_6;\tau_{34})X_S(x_6,x_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2},
  \label{Eqn:DYN_T}
  \end{eqnarray}
  \end{widetext}
  where we used the notation $\tau^+_{ij}=t^+_i-t_j$, with $t^+_i=t_i+\eta$ ($\eta\rightarrow 0^+$), and we considered $T(3,5,4,6)=- \delta(\tau^+_{35})\delta(\tau^+_{64})\bar{T}(x_3,x_5,x_4,x_6;\tau_{34})$ \cite{Lucia_book}, with 
\begin{widetext}
  \begin{eqnarray}
\bar{T}(x_3,x_5,x_4,x_6;\tau_{34}) &=&v_c(x_3,x_5)\delta(\tau_{34})\delta(x_3,x_4)\delta(x_6,x_5)-v_c(x_3,x_5)\delta(\tau_{34})\delta(x_3,x_6)\delta(x_4,x_5)\nonumber\\
&+&iv_c(x_3,x_5)G(x_3,x_7;\tau_{38})G(x_5,x_8;\tau^+_{38})\bar{T}(x_7,x_8,x_4,x_6;\tau_{84}).
\label{Eqn:T_bar}
\end{eqnarray}
\end{widetext}
Using the Fourier transform $G(\tau)=\int \frac{d\omega}{2\pi}G(\omega)e^{-i\omega\tau}$, changing variable from $t_3$ to $\tau_{34}$ and taking the limit $t_{1^\prime}=t_1^+$ we arrive at
\begin{widetext}
\begin{eqnarray}
X_S(x_1,x_{1^\prime},0^-)
  &=&-i\int dx_3x_4x_5x_6\int d\tau_{34} \int \frac{d\nu'}{2\pi}G(x_1,x_3;\nu'+\omega_S)G(x_4,x_{1^\prime};\nu')e^{i\nu'\tau_{34}}\times\nonumber\\
  &&\bar{T}(x_3,x_5,x_4,x_6;\tau_{34})X_S(x_6,x_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}.
\end{eqnarray}
 \end{widetext}
 We now use  the Lehman representation of the one-body Green's function in the quasiparticle approximation, i.e.
$$G(x_1,x_2;\omega)=\sum_{p}\frac{\psi_p(x_1)\psi_p^*(x_2)}{\omega-\epsilon_p+ i\eta \text{sgn}(\epsilon_p-\mu)},$$ where $\psi_p$ and $\epsilon_p$ are single-particle wavefunctions and energies, respectively, and $\mu$ the chemical potential, and multiply left- and right-hand sides by $(\epsilon_a-\epsilon_i-\omega_m)\int dx_1dx^{\prime}_1 \psi^*_a(x_1)\psi_i(x_1^\prime)$.  
Using the fact that
\begin{equation}
\Theta(\pm\tau)e^{-i\alpha \tau}=\mp\frac{1}{2\pi i}\lim_{\eta\rightarrow 0^+}\int d\omega \frac{1}{\omega-\alpha\pm i\eta}e^{-i\omega\tau},
\end{equation}

%$$\frac{-i}{2\pi} \int  d\nu'\frac{1}{\nu'+\omega_m-\epsilon_{c}+ i\eta}e^{i\nu'\tau_{34}}=\frac{1}{2\pi i}\int  d\nu'\frac{1}{\nu'+\omega_m-\epsilon_{c}+ i\eta}e^{-i\nu'(-\tau_{34}})=-\Theta(-\tau_{34})e^{i(\epsilon_{c}-\omega_m)\tau_{34}}$$
%and
%$$\frac{i}{2\pi} \int  d\nu'\frac{1}{\nu'-\epsilon_{v}- i\eta}e^{i\nu'\tau_{34}}=\frac{-1}{2\pi i}\int  d\nu'\frac{1}{\nu'-\epsilon_{v}- i\eta}e^{-i\nu'(-\tau_{34}})=-\Theta(\tau_{34})e^{i\epsilon_{v}\tau_{34}},$$
we then arrive at
 \begin{eqnarray}
&&(\epsilon_a-\epsilon_i-\omega_S)\int dx_1dx^{\prime}_1 \psi^*_a(x_1)\psi_i(x_1^\prime)  X_S(x_1,x_{1^\prime},0^-)=\nonumber\\
  &-&\int dx_3x_4x_5x_6\int d\tau_{34}\psi_a^*(x_3)\psi_i(x_4)\nonumber\\
  &\times&\left[\Theta(\tau_{34})e^{i\epsilon_{i}\tau_{34}}+\Theta(-\tau_{34})e^{i(\epsilon_{a}-\omega_S)\tau_{34}}\right]\nonumber\\
&\times&\bar{T}(x_3,x_5,x_4,x_6;\tau_{34})X_S(x_6,x_5;-\tau_{34})e^{i\omega_S\tau_{34}/2}.
\label{Eqn:General_DYN}
\end{eqnarray}
%
%
%
% RESONANT
We now consider the resonant case $\omega_m>0$, for which 
\begin{eqnarray}
X_S(x_1,x_{1^\prime},\tau_1)   &=&-e^{i\omega_S|\tau_1|/2} \sum_{pq}\psi_p(x_1)\psi^*_{q}(x_{1^\prime})\langle N|\hat{c}^\dagger_{q}\hat{c}_p|N,S\rangle\nonumber\\
  &\times&\left[\Theta(\tau_1)e^{-i\epsilon_p\tau_1}+\Theta(-\tau_1)e^{-i\epsilon_{q}\tau_1}\right],
  \label{Eqn:chi_tau}
  \end{eqnarray}
  where $\hat{c}^\dagger_{q}$ and $\hat{c}_p$ are creation and annihilation operators, respectively, and $|N\rangle$ and $|N,m\rangle$ are the ground state and the $i$-th excited state, respectively, of the $N$-electron system.
After some algebraic steps we arrive at 
\begin{widetext}
 \begin{eqnarray}
&-&(\epsilon_a-\epsilon_i-\omega_S)\langle N|\hat{c}^\dagger_{i}\hat{c}_a|N,S\rangle\nonumber\\
    &=& -\sum_{pq}\langle N|\hat{c}^\dagger_{q}\hat{c}_p|N,S\rangle\left\{-\frac{i}{2\pi}\int d\omega \lim_{\eta\rightarrow 0^+}\ \bar{T}_{iq,pa}(\omega) e^{-i\omega\eta}\left[\frac{1}{\omega_S-\omega+\epsilon_{q}+\epsilon_i+i\eta}+\frac{1}{\omega_S+\omega-\epsilon_p-\epsilon_a+i\eta}\right]\right\}\nonumber\\
  \end{eqnarray}
\end{widetext}
where we defined $ \bar{T}_{iq,pa}(\tau_{34})=\int dx_3x_4x_5x_6\int \psi_a^*(x_3)\psi_i(x_4)\bar{T}(x_3,x_5,x_4,x_6;\tau_{34}) \psi_p(x_6)\psi^*_{q}(x_5)$. Using the definition $A_S^{(qp)}=\langle N|\hat{c}^\dagger_{q}\hat{c}_p|N,S\rangle$, we arrive at

 \begin{eqnarray}
(\epsilon_a-\epsilon_i-\omega_S)A_S^{(ia)}+\sum_{pq}A_S^{(q p)}\widetilde{T}_{iq,pa}(\omega_S)=0,
  \end{eqnarray}
where we defined
\begin{widetext}
\be
\widetilde{T}_{iq,pa}(\omega_S)=\left\{\frac{i}{2\pi}\int d\omega \lim_{\eta\rightarrow 0^+}\bar{T}_{iq,pa}(\omega)e^{-i\omega\eta} \left[\frac{1}{\omega_S-\omega+\epsilon_{q}+\epsilon_i+i\eta}+\frac{1}{\omega_S+\omega-\epsilon_p-\epsilon_a+i\eta}\right]\right\}\nonumber.
 \label{Eqn:H2preso_eigen_2_T}
\ee
\end{widetext}

This is an eigenvalue equation to calculate the positive excitation energies of a system, which can be rewritten as,
  \begin{equation}
 H^{2p,reso}_{ia,qp}(\omega_S)A_S^{(qp)}=\omega_S A^{(ia)}_S,
 \label{Eqn:H2preso_eigen}
 \end{equation}
 with
\begin{eqnarray}
 H^{2p,reso}_{ia,qp}(\omega_S)&=&(\epsilon_a-\epsilon_i)\delta_{iq}\delta_{ap} +\langle ip||aq\rangle+\widetilde{T}_{iq,pa}(\omega_S).
% \label{Eqn:H2preso_eigen_2_T}
  \end{eqnarray}
  Here  $H^{2p,reso}_{ia,jb}(\omega_S)=A_{ia,jb}(\omega_S)$ and $H^{2p,reso}_{ia,bj}(\omega_S)=B_{ia,jb}(\omega_S)$.
 If we drop the correlation part of $\bar{T}$ (the first two terms on the right-hand side of Eq.~(\ref{Eqn:T_bar})) we obtain the TDHF equations. To calculate the correlation contribution we use Eq. (9) 
 in  Eq.~(\ref{Eqn:H2preso_eigen_2_T}), and after integration over the frequency we arrive at Eq. (21).

%\begin{eqnarray}
% H^{2p,reso}_{(vc)(n^\prime n)}(\omega_m)&=&(\epsilon_a-\epsilon_i)\delta_{vn^\prime}\delta_{cn} +\langle cn'|v|vn\rangle -\langle cn'|v|nv\rangle\nonumber\\
% &+&\sum_m\frac{B^m_{(vc)(n'n)}}{\omega_m-\omega_m^{N+2}+\epsilon_{n'}+\epsilon_i+i\eta}+ \sum_m\frac{C^m_{(vc)(n'n)}}{\omega_m+\omega_m^{N-2}-\epsilon_n-\epsilon_a+i\eta}.
%\label{Eqn:H2preso_eigen_check2}
%  \end{eqnarray}
%
%In the resonant block, $n'n=v'c'$, we get hence $\omega_m=\omega_m^{N+2}-\epsilon_{v'}-\epsilon_i$ and $\omega_m=-\omega_m^{N-2}+\epsilon_{c'}+\epsilon_a$, which are double excitations.
%
%
%
%
%%%%
\subsubsection{Second-order kernel}
%%%%%
We consider the second-order BSE kernel given by Rebolini and Toulouse (Eq. 15 in JCP 144, 094107 (2016)), which reads (for the correlation part) 
\begin{eqnarray}
\Xi^{(2)}_c(1,4,2,3)&=&\delta(t_1,t_3)\delta(t_2,t_4)\Xi^{(2,ph/hp)}_c(x_1,x_4,x_2,x_3;\tau_{12})\nonumber\\
&+&\delta(t_1,t_4)\delta(t_2,t_3)\Xi^{(2,pp/hh)}_c(x_1,x_4,x_2,x_3;\tau_{12}).\nonumber\\
\label{Eqn:SOK}
\end{eqnarray}
This kernel is derived from the second-order self-energy, which corresponds to the self-energy obtained from the first iteration of the T-matrix equation (\ref{Eqn:T-matrix}). We notice that the contribution $\Xi^{(2,pp/hh)}_c$ corresponds to the first iteration of the T-matrix kernel in Eq.~ (\ref{Eqn:T-matrix_kernel}), whereas $\Xi^{(2,eh/ph)}_c$ are contributions coming from the derivative $\delta T/\delta G$ which we have neglected in  (\ref{Eqn:T-matrix_kernel}).

Using a similar derivation as for the frequency-dependent T-matrix kernel, we arrive at the following eigenvalue equation in the case of the frequency-dependent second-order kernel (\ref{Eqn:SOK})

\begin{eqnarray}
  H^{2p,reso}_{ia,qp}(\omega_S)&=&(\epsilon_a-\epsilon_i)\delta_{iq}\delta_{ap} +\langle ip||aq\rangle\nonumber\\
 &-&\sum_{kc}\frac{\langle qc||ik\rangle\langle ka||cp\rangle}{\omega_S-(\epsilon_c+\epsilon_a-\epsilon_{q}-\epsilon_k)+i\eta}\nonumber\\
 &-&\sum_{kc}\frac{\langle qk||ic\rangle\langle ca||kp\rangle}{\omega_S+(\epsilon_k+\epsilon_i-\epsilon_p-\epsilon_c)+i\eta}\nonumber\\
 &+&\frac{1}{2}\sum_{kl}\frac{\langle aq||kl\rangle\langle lk||pi\rangle}{\omega_S-(\epsilon_p+\epsilon_a-\epsilon_k-\epsilon_l)+i\eta}\nonumber\\
 &+&\frac{1}{2}\sum_{cd}\frac{\langle aq||cd\rangle\langle dc||pi\rangle}{
\omega_S-(\epsilon_c+\epsilon_d-\epsilon_{q}-\epsilon_i)+i\eta}\nonumber\\
%\label{Eqn:H2preso_eigen_check2}
  \end{eqnarray}
where we used 
\begin{eqnarray}
\Xi^{ph/hp}_{ia,qp}(\omega)&=&-\sum_{kc}\frac{\langle qc||ik\rangle\langle ka||cp\rangle}{\omega-(\epsilon_c-\epsilon_k)+i\eta}\nonumber\\
&+&\sum_{kc}\frac{\langle qk||ic\rangle\langle ca||kp\rangle}{\omega+(\epsilon_c-\epsilon_k)-i\eta}\\
\Xi^{pp/hh}_{ia,qp}(\omega)&=&-\frac{1}{2}\sum_{kl}\frac{\langle aq||kl\rangle\langle lk||pi\rangle}{\omega-(\epsilon_k+\epsilon_l)-i\eta}\nonumber\\
&+&\frac{1}{2}\sum_{cd}\frac{\langle aq||cd\rangle\langle dc||pi\rangle}{\omega-(\epsilon_c+\epsilon_d)+i\eta}.
\end{eqnarray}
%\begin{eqnarray}
%&-&(\epsilon_c-\epsilon_v-\omega_m)\langle N|\hat{c}^\dagger_{v}a_c|N,i\rangle\nonumber\\
%  &=&\int dx_3x_4x_5x_6\int d\tau_{34}\psi_c^*(x_3)\psi_v(x_4)\nonumber\\
%&&\Xi^{(2,ph/hp)}_c(x_3,x_5,x_4,x_6;\tau_{34}) e^{i\omega_m\tau_{34}/2} e^{i\omega_m|\tau_{34}|/2} \sum_{nn^\prime}\psi_n(x_6)\psi^*_{n^\prime}(x_5)\langle N|\hat{c}^\dagger_{n^\prime}\hat{c}_n|N,i\rangle\times\nonumber\\
%  &&\left[\Theta(\tau_{34})e^{-i(\epsilon_n-\epsilon_v)\tau_{34}}+\Theta(-\tau_{34})e^{-i(\epsilon_{n^\prime}-\epsilon_c+\omega_m)\tau_{34}}\right]\nonumber\\
%  &=&\int dx_3x_4x_5x_6\int d\tau_{34}\psi_c^*(x_3)\psi_v(x_4)\nonumber\\
%&&\Xi^{(2,ph/hp)}_c(x_3,x_5,x_4,x_6;\tau_{34})  \sum_{nn^\prime}\psi_n(x_6)\psi^*_{n^\prime}(x_5)\langle N|\hat{c}^\dagger_{n^\prime}\hat{c}_n|N,i\rangle\times\nonumber\\
%  &&\left[\Theta(\tau_{34})e^{i(\epsilon_n-\epsilon_v-\omega_m)\tau_{34}}+\Theta(-\tau_{34})e^{i(\epsilon_{n^\prime}-\epsilon_c+\omega_m)\tau_{34}}\right]\nonumber\\
%  &=& \sum_{nn^\prime}\langle N|\hat{c}^\dagger_{n^\prime}\hat{c}_n|N,i\rangle\left\{\int d\tau_{34} \Xi^{(2,ph/hp)}_{c,(vc)(n'n)}(\tau_{34})\left[\Theta(\tau_{34})e^{i(\epsilon_n-\epsilon_v-\omega_m)\tau_{34}}+\Theta(-\tau_{34})e^{i(\epsilon_{n^\prime}-\epsilon_c+\omega_m)\tau_{34}}\right]\right\}\nonumber\\
%  &=& \sum_{nn^\prime}\langle N|\hat{c}^\dagger_{n^\prime}\hat{c}_n|N,i\rangle\nonumber\\
%  &&\left\{\frac{i}{2\pi}\int d\tau_{34}\int d\omega' \lim_{\eta\rightarrow 0^+}\Xi^{(2,ph/hp)}_{c,(vc)(n'n)}(\tau_{34}) \left[\frac{1}{\omega'-\epsilon_{n}+\epsilon_v+\omega_m+i\eta}-\frac{1}{\omega'-\epsilon_{n'}+\epsilon_c-\omega_m-i\eta}\right]\right\}e^{-i\omega'\tau_{34}}\nonumber\\
%  &=&- \sum_{nn^\prime}\langle N|\hat{c}^\dagger_{n^\prime}\hat{c}_n|N,i\rangle\nonumber\\
%  &&\left\{\frac{i}{2\pi}\int d\omega \lim_{\eta\rightarrow 0^+}\Xi^{(2,ph/hp)}_{c,(vc)(n'n)}(\omega) e^{-i\omega\eta}\left[\frac{1}{\omega_m+\omega-\epsilon_{n}+\epsilon_v+i\eta}+\frac{1}{\omega_m-\omega+\epsilon_{n'}-\epsilon_c+i\eta}\right]\right\}\nonumber\\
%  \end{eqnarray}
%
%
%We now use  the second-order kernel given by Rebolini and Toulouse in Eq. 29, which reads
%\begin{eqnarray}
%\Xi^{ph/hp}_{(vc)(n'n)}(\omega)=-\sum_{ka}\frac{B^{ka}_{(vc)(n'n)}}{\omega-(\epsilon_a-\epsilon_k)+i\eta}+\sum_{ka}\frac{C^{ka}_{(vc)(n'n)}}{\omega+(\epsilon_a-\epsilon_k)-i\eta}\\
%%\Xi^{pp/hh}_{(vc)(n'n)}(\omega)=-\frac{1}{2}\sum_{kl}\frac{B^{',kl}_{(vc)(n'n)}}{\omega-(\epsilon_k+\epsilon_l)-i\eta}+\frac{1}{2}\sum_{ab}\frac{C^{',ab}_{(vc)(n'n)}}{\omega-(\epsilon_a+\epsilon_b)+i\eta}
%\end{eqnarray}
%Here the indices i, j, k, l refer to occupied spin orbitals and the indices a, b, c, d to virtual
%spin orbitals.
%We hence arrive at
%\begin{eqnarray}
% H^{2p,reso}_{(vc)(n^\prime n)}(\omega_m)&=&(\epsilon_c-\epsilon_v)\delta_{vn^\prime}\delta_{cn} +\langle cn'|v|vn\rangle -\langle cn'|v|nv\rangle\nonumber\\
% &-&\sum_{ka}\frac{B^{ka}_{(vc)(n'n)}}{\omega_m-(\epsilon_a+\epsilon_c-\epsilon_{n^\prime}-\epsilon_k)+i\eta}-\sum_{ka}\frac{C^{ka}_{(vc)(n'n)}}{\omega_m+(\epsilon_k+\epsilon_v-\epsilon_n-\epsilon_a)+i\eta}
%\label{Eqn:H2preso_eigen_check2}
%  \end{eqnarray}
%
%In the resonant block, $n'n=v'c'$, we get hence double excitations.
%
%For the $\Xi^{(2,pp/hh)}_c(x_1,x_4,x_2,x_3;t_1-t_2)$ the derivation is the same as for the T matrix. If we use Eq. (30) given by Rebolini and Toulouse,  which reads
%\begin{eqnarray}
%%\Xi^{ph/hp}_{(vc)(n'n)}(\omega)=-\sum_{ka}\frac{B^{ka}_{(vc)(n'n)}}{\omega-(\epsilon_a-\epsilon_k)+i\eta}+\sum_{ka}\frac{C^{ka}_{(vc)(n'n)}}{\omega+(\epsilon_a-\epsilon_k)-i\eta}\\
%\Xi^{pp/hh}_{(vc)(n'n)}(\omega)=-\frac{1}{2}\sum_{kl}\frac{B^{',kl}_{(vc)(n'n)}}{\omega-(\epsilon_k+\epsilon_l)-i\eta}+\frac{1}{2}\sum_{ab}\frac{C^{',ab}_{(vc)(n'n)}}{\omega-(\epsilon_a+\epsilon_b)+i\eta}
%\end{eqnarray}
%in Eq. (\ref{Eqn:H2preso_eigen_2}) we arrive at
%
%\begin{eqnarray}
% H^{2p,reso}_{(vc)(n^\prime n)}(\omega_m)&=&(\epsilon_c-\epsilon_v)\delta_{vn^\prime}\delta_{cn} +\langle cn'|v|vn\rangle -\langle cn'|v|nv\rangle\nonumber\\
% &+&\frac{1}{2}\sum_{ab}\frac{B^{',kl}_{(vc)(n'n)}}{\omega_m-(\epsilon_n+\epsilon_c-\epsilon_k-\epsilon_l)+i\eta}+\frac{1}{2}\sum_{kl}\frac{C^{',ab}_{(vc)(n'n)}}{
%\omega_m-(\epsilon_a+\epsilon_c-\epsilon_{n^\prime}-\epsilon_v)+i\eta}\nonumber\\
%\label{Eqn:H2preso_eigen_check3}
%  \end{eqnarray}
%In the resonant block, $n'n=v'c'$, we get hence double excitations.

\end{document}

### 2022-02-09 Manuscript/Tmatrix.tex
data availibility statement
significant modifications in the appendix

@@
 
+\DeclareSIUnit\angstrom{\text{\AA}}
+
 % addresses
@@
 \begin{equation}
+\label{eq:SigGW}
 	\Sigma^{GW}(1,2) = i G(1,2) W(1,2)
@@
 \begin{equation}
+\label{eq:SigGT}
 	\Sigma^{GT}(1,2) = i \int G(4,3) T(1,3;2,4) d3 d4
@@
 \begin{align}
+\label{eq:L0}
 	 iL_0(1,4;1',3) & = G(1,3) G(4,1')
 	 \\
+\label{eq:L}
 	 iL(1,2;1',2') & = -G_2(1,2;1',2') + G(1,1')G(2,2')
@@
 
-To recast the BSE with a dynamical $T$-matrix kernel as an eigenvalue equation, we follow Ref.~\onlinecite{Strinati_1980} and start from the equation for the BSE amplitude 
+To recast the BSE with a dynamical $T$-matrix kernel as an eigenvalue equation, we follow Ref.~\onlinecite{Strinati_1980} (see also Ref.~\onlinecite{Loos_2020e}) and start from the equation for the BSE amplitude
 \begin{equation}
 \label{eq:Strinati_1}
-	X_S(1,1^\prime) = \int d3d4d5d6L_0(1,4,1^\prime,3)\Xi(3,5,4,6) X_S(6,5)
+	\chi_S(1,1') = \int d3d4d5d6L_0(1,4,1',3)\Xi(3,5,4,6) \chi_S(6,5)
 \end{equation}
-with 
+where $L_0$ is given by Eq.~\eqref{eq:L0} and the $T$-matrix kernel is
 \begin{align}
 \label{eq:T-matrix_kernel}
-	L_0(1,4,1^\prime,3) & =-iG(1,3)G(4,1^\prime)
-	&
 	\Xi(3,5,4,6) & =  i\frac{\delta \Sigma(3,4)}{\delta G(6,5)}\approx -T(3,5,4,6)
 \end{align}
-where we consider the so-called $T$-matrix self-energy \cite{Martin_2016,Romaniello_2012} $\Sigma(3,4)=iG(7,8)T(3,8,4,7)$ with
+The so-called $T$-matrix self-energy $\Sigma$ is given by Eq.~\eqref{eq:SigGT} with \cite{Martin_2016,Romaniello_2012}
 \begin{equation}
@@
 	+ v_c(3,8)\delta(4,8)\delta(3,7)
-	+ iv_c(3,8)G(3,1')G(8,2')T(1',2',4,7)
+	+ i \int d1'd2' v_c(3,8)G(3,1')G(8,2')T(1',2',4,7)
 \end{equation}  
-and where we neglect the functional derivative $\delta T/\delta G$ in the kernel $\Xi$.
+where \titou{$v_c$ is the bare Coulomb operator} and we neglect the functional derivative $\delta T/\delta G$ in the kernel $\Xi$.
 Making the time dependence of Eq.~\eqref{eq:Strinati_1} explicit, one gets 
@@
 \label{eqn:DYN_T}
-	X_S(x_1,x_{1^\prime},\tau_{11'})e^{-i\omega_S(t_1+t_{1^\prime})/2}
-	=-i\int d3d4d5d6 G(x_1,x_3;\tau_{13})G(x_4,x_{1^\prime};\tau_{11^\prime})
-	\\
-	\times \bar{T}(x_3,x_5,x_4,x_6;\tau_{34})X_S(x_6,x_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}
+	\chi_S(\bx_1,\bx_{1'},\tau_{11'})e^{-i\omega_S(t_1+t_{1'})/2}
+	=-i\int d3d4d5d6 G(\bx_1,\bx_3;\tau_{13})G(\bx_4,\bx_{1'};\tau_{11'})
+	\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}
 \end{multline}
-where $\tau^+_{ij}=t^+_i-t_j$ with $t^+_i=t_i+\eta$ ($\eta \to 0^+$) and $T(3,5,4,6)=- \delta(\tau^+_{35})\delta(\tau^+_{64})\bar{T}(x_3,x_5,x_4,x_6;\tau_{34})$ with 
+[where \titou{$\tau_{ij}=t_i-t_j$} and $\tau^+_{ij}=t^+_i-t_j$ with $t^+_i=t_i+\eta$ ($\eta \to 0^+$)] with $T(3,5,4,6)=- \delta(\tau^+_{35})\delta(\tau^+_{64})\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})$ and
 \begin{multline}
 \label{eq:T_bar}
-	\bar{T}(x_3,x_5,x_4,x_6;\tau_{34}) 
-	= v_c(x_3,x_5)\delta(\tau_{34})\delta(x_3,x_4)\delta(x_6,x_5)-v_c(x_3,x_5)\delta(\tau_{34})	\delta(x_3,x_6)\delta(x_4,x_5)
+	\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34}) 
+	= v_c(\bx_3,\bx_5)\delta(\tau_{34})\delta(\bx_3,\bx_4)\delta(\bx_6,\bx_5)-v_c(\bx_3,\bx_5)\delta(\tau_{34})	\delta(\bx_3,\bx_6)\delta(\bx_4,\bx_5)
 	\\
-	+ iv_c(x_3,x_5)G(x_3,x_7;\tau_{38})G(x_5,x_8;\tau^+_{38})\bar{T}(x_7,x_8,x_4,x_6;\tau_{84})
+	+ iv_c(\bx_3,x_5)G(\bx_3,\bx_7;\tau_{38})G(\bx_5,\bx_8;\tau^+_{38})\Bar{T}(\bx_7,\bx_8,\bx_4,\bx_6;\tau_{84})
 \end{multline}
-Using the Fourier transform $G(\tau)=\int \frac{d\omega}{2\pi}G(\omega)e^{-i\omega\tau}$, changing variable from $t_3$ to $\tau_{34}$ and taking the limit $t_{1^\prime}=t_1^+$ we arrive at
+Using the Fourier transform $G(\tau)=\int \frac{d\omega}{2\pi}G(\omega)e^{-i\omega\tau}$, changing variable from $t_3$ to $\tau_{34}$ and taking the limit $t_{1'}=t_1^+$, we have
 \begin{multline}
-	X_S(x_1,x_{1^\prime},0^-)
-	= -i\int dx_3 dx_4 dx_5 dx_6\int d\tau_{34} \int \frac{d\nu'}{2\pi}G(x_1,x_3;\nu'+\omega_S)G(x_4,x_{1^\prime};\nu')e^{i\nu'\tau_{34}}
+	\chi_S(\bx_1,\bx_{1'},0^-)
+	= -i\int d\bx_3 d\bx_4 d\bx_5 d\bx_6\int d\tau_{34} \int \frac{d\omega'}{2\pi}G(\bx_1,\bx_3;\omega'+\omega_S)G(\bx_4,\bx_{1'};\omega')e^{i\omega'\tau_{34}}
 	\\
-	 \times \bar{T}(x_3,x_5,x_4,x_6;\tau_{34})X_S(x_6,x_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}.
+	 \times \Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}
 \end{multline}
-Using the Lehman representation of the one-body Green's function in the quasiparticle approximation, i.e.
-$$G(x_1,x_2;\omega)=\sum_{p}\frac{\psi_p(x_1)\psi_p^*(x_2)}{\omega-\epsilon_p+ i\eta \text{sgn}(\epsilon_p-\mu)},$$ where $\psi_p$ and $\epsilon_p$ are single-particle wavefunctions and energies, respectively, and $\mu$ the chemical potential, and multiply left- and right-hand sides by $(\epsilon_a-\epsilon_i-\omega_S)\int dx_1dx^{\prime}_1 \psi^*_a(x_1)\psi_i(x_1^\prime)$.
-Using the fact that
+Using the Lehman representation of the one-body Green's function in the quasiparticle approximation given by Eq.~\eqref{eq:G},
+%$$G(x_1,x_2;\omega)=\sum_{p}\frac{\psi_p(x_1)\psi_p^*(x_2)}{\omega-\epsilon_p+ i\eta \text{sgn}(\epsilon_p-\mu)},$$ where $\psi_p$ and $\epsilon_p$ are single-particle wavefunctions and energies, respectively, and $\mu$ the chemical potential,
+and multiply the left- and right-hand sides by $(\e{a}{}-\e{i}{}-\omega_S)\int d\bx_1 d\bx^{\prime}_1 \SO{a}(\bx_1)\SO{i}(\bx_1')$.  
+we then arrive at
+\begin{multline}
+\label{eq:General_DYN}
+	\qty(\e{a}{}-\e{i}{}-\omega_S)\int d\bx_1d\bx^{\prime}_1 \psi^*_a(\bx_1)\psi_i(\bx_1')  \chi_S(\bx_1,\bx_{1'},0^-) =
+	\\
+	-\int d\bx_3 d\bx_4 d\bx_5 d\bx_6\int d\tau_{34}\psi_a(\bx_3)\psi_i(\bx_4)
+	\qty[\Theta(\tau_{34})e^{i\epsilon_{i}\tau_{34}}+\Theta(-\tau_{34})e^{i(\epsilon_{a}-\omega_S)\tau_{34}} ]
+	\\
+	\times \Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{i\omega_S\tau_{34}/2}
+\end{multline}
+(where $\Theta$ is the Heaviside step function) using the fact that
 \begin{equation}
@@
 \end{equation}
-we then arrive at
-\begin{multline}
-\label{eq:General_DYN}
-	(\epsilon_a-\epsilon_i-\omega_S)\int dx_1dx^{\prime}_1 \psi^*_a(x_1)\psi_i(x_1^\prime)  X_S(x_1,x_{1^\prime},0^-) =
-	\\
-	-\int dx_3 dx_4 dx_5 dx_6\int d\tau_{34}\psi_a^*(x_3)\psi_i(x_4)
-	\qty[\Theta(\tau_{34})e^{i\epsilon_{i}\tau_{34}}+\Theta(-\tau_{34})e^{i(\epsilon_{a}-\omega_S)\tau_{34}} ]
-	\\
-	\times \bar{T}(x_3,x_5,x_4,x_6;\tau_{34})X_S(x_6,x_5;-\tau_{34})e^{i\omega_S\tau_{34}/2}
-\end{multline}
 
-We now consider the resonant case $\omega_m>0$, for which 
+We now consider the resonant case $\omega_S>0$, for which 
 \begin{equation}
 \label{Eqn:chi_tau}
-	X_S(x_1,x_{1^\prime},\tau_1) 
-	=-e^{i\omega_S\abs{\tau_1}/2} \sum_{pq}\psi_p(x_1)\psi^*_{q}(x_{1^\prime}) \mel{N}{\hat{c}^\dagger_{q}\hat{c}_p}{N,S}
-  	\qty[\Theta(\tau_1)e^{-i\epsilon_p\tau_1}+\Theta(-\tau_1)e^{-i\epsilon_{q}\tau_1} ]
+	\chi_S(\bx_1,\bx_{1'},\tau_1) 
+	=-e^{i\omega_S\abs{\tau_1}/2} \sum_{pq}\SO{p}(\bx_1)\SO{q}(\bx_{1'}) \mel{N}{\hat{c}^\dagger_{q}\hat{c}_p}{N,S}
+  	\qty[\Theta(\tau_1)e^{-i\e{p}{}\tau_1}+\Theta(-\tau_1)e^{-i\e{q}{}\tau_1} ]
 \end{equation}
   where $\hat{c}^\dagger_{q}$ and $\hat{c}_p$ are creation and annihilation operators, respectively, and $\ket{N}$ and $\ket{N,S}$ are the ground state and the $S$-th excited state, respectively, of the $N$-electron system.
-After some algebraic steps we arrive at 
+After some algebraic steps, one gets
 \begin{multline}
-	-(\epsilon_a-\epsilon_i-\omega_S)\mel{N}{\hat{c}^\dagger_{i}\hat{c}_a}{N,S}
+	-\qty(\e{a}{}-\e{i}{}-\omega_S)\mel{N}{\hat{c}^\dagger_{i}\hat{c}_a}{N,S}
 	\\
     = -\sum_{pq}\mel{N}{\hat{c}^\dagger_{q}\hat{c}_p}{N,S}
-    \qty{ -\frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\ \bar{T}_{iq,pa}(\omega) e^{-i\omega\eta}\left[\frac{1}{\omega_S-\omega+\epsilon_{q}+\epsilon_i+i\eta}+\frac{1}{\omega_S+\omega-\epsilon_p-\epsilon_a+i\eta}\right] }
+    \qty{ -\frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\ \Bar{T}_{iq,pa}(\omega) e^{-i\omega\eta} \qty[\frac{1}{\omega_S-\omega+\e{q}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{p}{}-\e{a}{}+i\eta} ] }
 \end{multline}
@@
 \begin{equation}
-	\bar{T}_{iq,pa}(\tau_{34})=\int dx_3x_4x_5x_6\int \psi_a^*(x_3)\psi_i(x_4)\bar{T}(x_3,x_5,x_4,x_6;\tau_{34}) \psi_p(x_6)\psi^*_{q}(x_5)
+	\Bar{T}_{iq,pa}(\tau_{34})=\int d\bx_3 d\bx_4 d\bx_5 d\bx_6\int \SO{a}(\bx_3) \SO{i}(\bx_4)\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34}) \psi_p(\bx_6)\psi^*_{q}(\bx_5)
 \end{equation}
-Using the definition $A_S^{(qp)}=\langle N|\hat{c}^\dagger_{q}\hat{c}_p|N,S\rangle$, we arrive at
+Using the definition $X_{qp,S}=\mel{N}{\hat{c}^\dagger_{q}\hat{c}_p}{N,S}$, we arrive at
 
 \begin{equation}
-	\qty(\epsilon_a-\epsilon_i-\omega_S)A_S^{(ia)}+\sum_{pq}A_S^{(q p)}\widetilde{T}_{iq,pa}(\omega_S)=0,
+	\qty(\e{a}{}-\e{i}{}-\omega_S) X_{ia,S}+\sum_{pq}X_{qp,S}\widetilde{T}_{iq,pa}(\omega_S)=0,
 \end{equation}
-where we defined
+where we define
 \begin{equation}
 	\widetilde{T}_{iq,pa}(\omega_S)
-	= \qty{ \frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\bar{T}_{iq,pa}(\omega)e^{-i\omega\eta} \left[\frac{1}{\omega_S-\omega+\epsilon_{q}+\epsilon_i+i\eta}+\frac{1}{\omega_S+\omega-\epsilon_p-\epsilon_a+i\eta}\right]  }
+	= \frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\Bar{T}_{iq,pa}(\omega)e^{-i\omega\eta} \left[\frac{1}{\omega_S-\omega+\e{q}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{p}{}-\e{a}{}+i\eta}\right] 
  \label{Eqn:H2preso_eigen_2_T}
@@
 \label{eq:H2preso_eigen}
-	H^{2p,reso}_{ia,qp}(\omega_S)A_S^{(qp)}=\omega_S A^{(ia)}_S,
+	H_{ia,qp}(\omega_S) X_{qp,S}=\omega_S X_{ia,S}
 \end{equation}
@@
 \begin{equation}
-	H^{2p,reso}_{ia,qp}(\omega_S)=(\epsilon_a-\epsilon_i)\delta_{iq}\delta_{ap} + \mel{ip}{}{aq}+\widetilde{T}_{iq,pa}(\omega_S).
+	H_{ia,qp}(\omega_S)=(\e{a}{}-\e{i}{})\delta_{iq}\delta_{ap} + \mel{ip}{}{aq}+\widetilde{T}_{iq,pa}(\omega_S).
 \end{equation}
-Here $H^{2p,reso}_{ia,jb}(\omega_S)=A_{ia,jb}(\omega_S)$ and $H^{2p,reso}_{ia,bj}(\omega_S)=B_{ia,jb}(\omega_S)$.
-If we drop the correlation part of $\bar{T}$ [the first two terms on the right-hand side of Eq.~\eqref{eq:T_bar}] we obtain the TDHF equations.
+Here $H_{ia,jb}(\omega_S)=A_{ia,jb}(\omega_S)$ and $H_{ia,bj}(\omega_S)=B_{ia,jb}(\omega_S)$.
+If we drop the correlation part of $\Bar{T}$ [the first two terms on the right-hand side of Eq.~\eqref{eq:T_bar}] we obtain the TDHF equations.
 To calculate the correlation contribution we use \alert{Eq.~(9)} in Eq.~\eqref{Eqn:H2preso_eigen_2_T}, and after integration over the frequency we arrive at \alert{Eq.~(21).}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\twocolumngrid
+\section*{Data availability statement}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The \hypertarget{SI}{data} that support the findings of this study are openly available in Zenodo at \href{http://doi.org/XX.XXXX/zenodo.XXXXXXX}{http://doi.org/XX.XXXX/zenodo.XXXXXXX}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%
-\twocolumngrid
 \bibliography{Tmatrix}

### 2022-02-09 Manuscript/Tmatrix.tex
final clean up of appendix

@@
 where \titou{$v_c$ is the bare Coulomb operator} and we neglect the functional derivative $\delta T/\delta G$ in the kernel $\Xi$.
-Making the time dependence of Eq.~\eqref{eq:Strinati_1} explicit, one gets 
-\begin{multline}
+Making the time dependence of Eq.~\eqref{eq:Strinati_1} explicit and defining $T(3,5,4,6)=- \delta(\tau^+_{35})\delta(\tau^+_{64})\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})$, one gets 
+\begin{equation}
 \label{eqn:DYN_T}
@@
 	\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}
-\end{multline}
-[where \titou{$\tau_{ij}=t_i-t_j$} and $\tau^+_{ij}=t^+_i-t_j$ with $t^+_i=t_i+\eta$ ($\eta \to 0^+$)] with $T(3,5,4,6)=- \delta(\tau^+_{35})\delta(\tau^+_{64})\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})$ and
+\end{equation}
+[where \titou{$\tau_{ij}=t_i-t_j$} and $\tau^+_{ij}=t^+_i-t_j$ with $t^+_i=t_i+\eta$ ($\eta \to 0^+$)] and
 \begin{multline}
@@
 	\\
-	+ iv_c(\bx_3,x_5)G(\bx_3,\bx_7;\tau_{38})G(\bx_5,\bx_8;\tau^+_{38})\Bar{T}(\bx_7,\bx_8,\bx_4,\bx_6;\tau_{84})
+	+ i \int d7 d8 v_c(\bx_3,x_5)G(\bx_3,\bx_7;\tau_{38})G(\bx_5,\bx_8;\tau^+_{38})\Bar{T}(\bx_7,\bx_8,\bx_4,\bx_6;\tau_{84})
 \end{multline}
@@
 %$$G(x_1,x_2;\omega)=\sum_{p}\frac{\psi_p(x_1)\psi_p^*(x_2)}{\omega-\epsilon_p+ i\eta \text{sgn}(\epsilon_p-\mu)},$$ where $\psi_p$ and $\epsilon_p$ are single-particle wavefunctions and energies, respectively, and $\mu$ the chemical potential,
-and multiply the left- and right-hand sides by $(\e{a}{}-\e{i}{}-\omega_S)\int d\bx_1 d\bx^{\prime}_1 \SO{a}(\bx_1)\SO{i}(\bx_1')$.  
-we then arrive at
+and multiply the left- and right-hand sides by $(\e{a}{}-\e{i}{}-\omega_S)\int d\bx_1 d\bx^{\prime}_1 \SO{a}(\bx_1)\SO{i}(\bx_1')$, we obtain  
 \begin{multline}
 \label{eq:General_DYN}
-	\qty(\e{a}{}-\e{i}{}-\omega_S)\int d\bx_1d\bx^{\prime}_1 \psi^*_a(\bx_1)\psi_i(\bx_1')  \chi_S(\bx_1,\bx_{1'},0^-) =
+	\qty(\e{a}{}-\e{i}{}-\omega_S)\int d\bx_1d\bx^{\prime}_1 \SO{a}(\bx_1)\SO{i}(\bx_1')  \chi_S(\bx_1,\bx_{1'},0^-) =
+	-\int d\bx_3 d\bx_4 d\bx_5 d\bx_6\int d\tau_{34}\SO{a}(\bx_3)\SO{i}(\bx_4)
 	\\
-	-\int d\bx_3 d\bx_4 d\bx_5 d\bx_6\int d\tau_{34}\psi_a(\bx_3)\psi_i(\bx_4)
-	\qty[\Theta(\tau_{34})e^{i\epsilon_{i}\tau_{34}}+\Theta(-\tau_{34})e^{i(\epsilon_{a}-\omega_S)\tau_{34}} ]
-	\\
-	\times \Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{i\omega_S\tau_{34}/2}
+	\times \qty[\Theta(\tau_{34})e^{i\e{i}{}\tau_{34}}+\Theta(-\tau_{34})e^{i(\e{a}{}-\omega_S)\tau_{34}} ]
+	\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{i\omega_S\tau_{34}/2}
 \end{multline}
@@
 
-We now consider the resonant case $\omega_S>0$, for which 
+We now consider the resonant case, \ie, $\omega_S>0$, for which 
 \begin{equation}
@@
 \end{equation}
-  where $\hat{c}^\dagger_{q}$ and $\hat{c}_p$ are creation and annihilation operators, respectively, and $\ket{N}$ and $\ket{N,S}$ are the ground state and the $S$-th excited state, respectively, of the $N$-electron system.
+  where $\hat{c}^\dagger_{p}$ and $\hat{c}_p$ are the usual creation and annihilation operators, respectively, and $\ket{N}$ and $\ket{N,S}$ are the ground state and the $S$th excited state, respectively, of the $N$-electron system.
 After some algebraic steps, one gets
@@
 \end{multline}
-where we define 
+where we have defined 
 \begin{equation}
-	\Bar{T}_{iq,pa}(\tau_{34})=\int d\bx_3 d\bx_4 d\bx_5 d\bx_6\int \SO{a}(\bx_3) \SO{i}(\bx_4)\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34}) \psi_p(\bx_6)\psi^*_{q}(\bx_5)
+	\Bar{T}_{iq,pa}(\tau_{34})=\int d\bx_3 d\bx_4 d\bx_5 d\bx_6 \SO{a}(\bx_3) \SO{i}(\bx_4)\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34}) \psi_p(\bx_6)\psi^*_{q}(\bx_5)
 \end{equation}
@@
 \begin{equation}
-	\qty(\e{a}{}-\e{i}{}-\omega_S) X_{ia,S}+\sum_{pq}X_{qp,S}\widetilde{T}_{iq,pa}(\omega_S)=0,
+	\label{eq:egval}
+	\qty(\e{a}{}-\e{i}{}-\omega_S) X_{ia,S}+\sum_{pq}X_{qp,S}\widetilde{T}_{iq,pa}(\omega_S)=0
 \end{equation}
-where we define
+where the spectral representation of the dynamical $T$-matrix is
 \begin{equation}
@@
 \end{equation}
-
-This is an eigenvalue equation to calculate the positive excitation energies of a system, which can be rewritten as,
+Equation \eqref{eq:egval} represents a non-linear eigenvalue equation to calculate the positive excitation energies of a system, which can be rewritten as
 \begin{equation}
@@
 Here $H_{ia,jb}(\omega_S)=A_{ia,jb}(\omega_S)$ and $H_{ia,bj}(\omega_S)=B_{ia,jb}(\omega_S)$.
-If we drop the correlation part of $\Bar{T}$ [the first two terms on the right-hand side of Eq.~\eqref{eq:T_bar}] we obtain the TDHF equations.
-To calculate the correlation contribution we use \alert{Eq.~(9)} in Eq.~\eqref{Eqn:H2preso_eigen_2_T}, and after integration over the frequency we arrive at \alert{Eq.~(21).}
+If one drops the correlation part of $\Bar{T}$ [the first two terms on the right-hand side of Eq.~\eqref{eq:T_bar}], one ends up the usual time-dependent Hartree-Fock (TDHF) equations. 
+To calculate the correlation contribution, one must employ \eqref{eq:T} in Eq.~\eqref{Eqn:H2preso_eigen_2_T}, and after integration over the frequency, it yields Eq.~\eqref{eq:dT}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-02-09 Manuscript/Tmatrix.tex
minor corrections

@@
 	T(3,8,4,7) =
-	- v_c(3,8)\delta(3,4)\delta(7,8)
-	+ v_c(3,8)\delta(4,8)\delta(3,7)
-	+ i \int d1'd2' v_c(3,8)G(3,1')G(8,2')T(1',2',4,7)
+	- v(3,8)\delta(3,4)\delta(7,8)
+	+ v(3,8)\delta(4,8)\delta(3,7)
+	+ i \int d1'd2' v(3,8)G(3,1')G(8,2')T(1',2',4,7)
 \end{equation}  
-where \titou{$v_c$ is the bare Coulomb operator} and we neglect the functional derivative $\delta T/\delta G$ in the kernel $\Xi$.
+where $v$ is the bare Coulomb operator and we neglect the functional derivative $\delta T/\delta G$ in the kernel $\Xi$.
 Making the time dependence of Eq.~\eqref{eq:Strinati_1} explicit and defining $T(3,5,4,6)=- \delta(\tau^+_{35})\delta(\tau^+_{64})\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})$, one gets 
 \begin{equation}
-\label{eqn:DYN_T}
+\label{eq:DYN_T}
 	\chi_S(\bx_1,\bx_{1'},\tau_{11'})e^{-i\omega_S(t_1+t_{1'})/2}
@@
 \end{equation}
-[where \titou{$\tau_{ij}=t_i-t_j$} and $\tau^+_{ij}=t^+_i-t_j$ with $t^+_i=t_i+\eta$ ($\eta \to 0^+$)] and
+[where $\tau_{ij}=t_i-t_j$ and $\tau^+_{ij}=t^+_i-t_j$ with $t^+_i=t_i+\eta$ ($\eta \to 0^+$)] and
 \begin{multline}
@@
 	\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34}) 
-	= v_c(\bx_3,\bx_5)\delta(\tau_{34})\delta(\bx_3,\bx_4)\delta(\bx_6,\bx_5)-v_c(\bx_3,\bx_5)\delta(\tau_{34})	\delta(\bx_3,\bx_6)\delta(\bx_4,\bx_5)
+	= v(\bx_3,\bx_5)\delta(\tau_{34})\delta(\bx_3,\bx_4)\delta(\bx_6,\bx_5)-v(\bx_3,\bx_5)\delta(\tau_{34})	\delta(\bx_3,\bx_6)\delta(\bx_4,\bx_5)
 	\\
-	+ i \int d7 d8 v_c(\bx_3,x_5)G(\bx_3,\bx_7;\tau_{38})G(\bx_5,\bx_8;\tau^+_{38})\Bar{T}(\bx_7,\bx_8,\bx_4,\bx_6;\tau_{84})
+	+ i \int d7 d8 v(\bx_3,x_5)G(\bx_3,\bx_7;\tau_{38})G(\bx_5,\bx_8;\tau^+_{38})\Bar{T}(\bx_7,\bx_8,\bx_4,\bx_6;\tau_{84})
 \end{multline}
@@
 \begin{equation}
-\label{Eqn:chi_tau}
+\label{eq:chi_tau}
 	\chi_S(\bx_1,\bx_{1'},\tau_1) 
@@
 \begin{equation}
-	\Bar{T}_{iq,pa}(\tau_{34})=\int d\bx_3 d\bx_4 d\bx_5 d\bx_6 \SO{a}(\bx_3) \SO{i}(\bx_4)\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34}) \psi_p(\bx_6)\psi^*_{q}(\bx_5)
+	\Bar{T}_{iq,pa}(\tau_{34})=\int d\bx_3 d\bx_4 d\bx_5 d\bx_6 \SO{a}(\bx_3) \SO{i}(\bx_4)\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34}) \SO{p}(\bx_6)\SO{q}(\bx_5)
 \end{equation}
@@
 	= \frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\Bar{T}_{iq,pa}(\omega)e^{-i\omega\eta} \left[\frac{1}{\omega_S-\omega+\e{q}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{p}{}-\e{a}{}+i\eta}\right] 
- \label{Eqn:H2preso_eigen_2_T}
+ \label{eq:H2preso_eigen_2_T}
 \end{equation}
@@
 If one drops the correlation part of $\Bar{T}$ [the first two terms on the right-hand side of Eq.~\eqref{eq:T_bar}], one ends up the usual time-dependent Hartree-Fock (TDHF) equations. 
-To calculate the correlation contribution, one must employ \eqref{eq:T} in Eq.~\eqref{Eqn:H2preso_eigen_2_T}, and after integration over the frequency, it yields Eq.~\eqref{eq:dT}.
+To calculate the correlation contribution, one must employ \eqref{eq:T} in Eq.~\eqref{eq:H2preso_eigen_2_T}, and after integration over the frequency, it yields Eq.~\eqref{eq:dT}.
 

### 2022-02-09 Manuscript/Tmatrix.tex
saving work

@@
 Here, we derive and implement, for the first time, the static and dynamic Bethe-Salpeter equations when one considers $T$-matrix quasiparticle energies as well as a $T$-matrix-based kernel.
-The performance of the static scheme and its perturbative dynamical correction are assessed by computed the neutral excited states of molecular systems.
+The performance of the static scheme and its perturbative dynamical correction are assessed by computing the neutral excited states of molecular systems.
 Comparison with more conventional schemes as well as other wave function methods are also reported.
@@
 As a first didactical example, we consider the lowest singlet and triplet excited states of the hydrogen molecule \ce{H2} and the variation of their respective excitation energies upon dissociation.
-The excitation energies associated with these low-lying singlet and triplet excited states are represented in Fig.~\ref{fig:H2} as a function of the internuclear distance $R_{\ce{H-H}}$ at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
+The excitation energies associated with these low-lying excited states are represented in Fig.~\ref{fig:H2} as a function of the internuclear distance $R_{\ce{H-H}}$ at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
 The variation of the HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:H2_gap}
+This shows that, as already observed in the Hubbard dimer, \cite{Romaniello_2012} the $G_0W_0$ and $G_0T_0$ quasiparticle energies are very similar near the Fermi level.
+
+The performances of BSE@$G_0W_0$ and BSE@$G_0T_0$ are very similar for this system.
+For the lowest singlet excited state $B{}^1\Sigma_u^+$, the $T$-matrix-based formalism is slightly better when $R_{\ce{H-H}}$ increases but fails ultimately to reproduce the FCI results.
+For the $E{}^1\Sigma_g^+$ state, BSE@$G_0T_0$
+Note that both formalisms cannot see the $F{}^1\Sigma_g^+$ doubly-excited states and cannot model properly the avoided crossing between $E{}^1\Sigma_g^+$ and $F{}^1\Sigma_g^+$.
+Similar observations can be done for the triplet states.
 
@@
 The variation of the HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:BeH2_gap}
+Again, the $G_0W_0$ and $G_0T_0$ quasiparticle energies are very similar near the Fermi level.
+
+Dynamical corrections slightly improves the agreement between BSE and FCI.
 

### 2022-02-09 Manuscript/Tmatrix.tex
discussion on H2

@@
 %%%%%%%%%%%%%%%%%%%%%%
-As a first didactical example, we consider the lowest singlet and triplet excited states of the hydrogen molecule \ce{H2} and the variation of their respective excitation energies upon dissociation.
+As a first didactical example, we consider the lowest singlet and triplet excited states of the hydrogen molecule \ce{H2} and the variation of their respective vertical transition energies upon dissociation.
 The excitation energies associated with these low-lying excited states are represented in Fig.~\ref{fig:H2} as a function of the internuclear distance $R_{\ce{H-H}}$ at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
@@
 
-The performances of BSE@$G_0W_0$ and BSE@$G_0T_0$ are very similar for this system.
+Overall, as evidenced by Fig.~\ref{fig:H2}, the performances of BSE@$G_0W_0$ and BSE@$G_0T_0$ are very similar for this system.
 For the lowest singlet excited state $B{}^1\Sigma_u^+$, the $T$-matrix-based formalism is slightly better when $R_{\ce{H-H}}$ increases but fails ultimately to reproduce the FCI results.
-For the $E{}^1\Sigma_g^+$ state, BSE@$G_0T_0$
-Note that both formalisms cannot see the $F{}^1\Sigma_g^+$ doubly-excited states and cannot model properly the avoided crossing between $E{}^1\Sigma_g^+$ and $F{}^1\Sigma_g^+$.
-Similar observations can be done for the triplet states.
+For the $E{}^1\Sigma_g^+$ state, BSE@$G_0T_0$ is more accurate than BSE@$G_0W_0$ for small bond length and the scenario is reversed after the avoided crossing with the doubly-excited state of $F{}^1\Sigma_g^+$ symmetry.
+Of course, both formalisms cannot ``see'' the $F{}^1\Sigma_g^+$ states as the static BSE formlism is bind to double excitations.
+Therefore, it cannot model properly the avoided crossing between $E{}^1\Sigma_g^+$ and $F{}^1\Sigma_g^+$.
+For the $B'{}^1\Sigma_u^+$ and $C{}^1\Pi_u$ states, BSE@$G_0W_0$ and BSE@$G_0T_0$ reproduces fairly well the potential energy curves with a modest preference for the latter.
+
+Similar observations can be made for the triplet states, the $GW$- and $GT$-based formalisms yielding very similar excitation energies, except maybe for the $c{}^3\Pi_u$ state for which BSE@$G_0W_0$ has clearly the edge.
+Moreover, triplet instabilities seems to affect BSE@$G_0T_0$ slightly earlier than BSE@$G_0W_0$.
 
@@
 As a second example, we consider the symmetric dissociation of the linear molecule beryllium hydride \ce{BeH2}.
-The variation in excitation energies as a function of the distance $R_{\ce{Be-H}}$ is shown in Fig.~\ref{fig:BeH2}.
-The variation of the HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:BeH2_gap}
-Again, the $G_0W_0$ and $G_0T_0$ quasiparticle energies are very similar near the Fermi level.
+The variation of the lowest singlet and triplet excitation energies as a function of the distance $R_{\ce{Be-H}}$ is shown in Fig.~\ref{fig:BeH2}, while the quasiparticle energies of the frontier orbitals and the associated (fundamental) gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:BeH2_gap}
+Again, one notes that the $G_0W_0$ and $G_0T_0$ quasiparticle energies are very similar near the Fermi level.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{BSE with a dynamical kernel}
+\section{BSE with a dynamical $T$-matrix kernel}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-02-09 Manuscript/Tmatrix.tex
adding dBSE for H2

@@
 
+%%% FIGURE 3 %%%
+\begin{figure*}
+	\includegraphics[width=0.4\linewidth]{H2_dBSE1}
+	\hspace{0.1\linewidth}
+	\includegraphics[width=0.4\linewidth]{H2_dBSE3}
+	\caption{
+	Error with respect to FCI for the lowest singlet (left) and lowest triplet (right) excitation energies of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed with and without dynamical correction at the BSE@$G_0W_0$ and BSE@$G_0T_0$ levels with the cc-pVTZ basis.
+	Raw data are reported in {\SupInf}.}
+	\label{fig:H2_dBSE}
+\end{figure*}
+%%% %%% %%% %%%
+
 %%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%% FIGURE 3 %%%
+%%% FIGURE 4 %%%
 \begin{figure*}
@@
 
-%%% FIGURE 4 %%%
+%%% FIGURE 5 %%%
 \begin{figure}

### 2022-02-10 Manuscript/Tmatrix.tex
OK with discussion of H2 and BeH2

--- 2022-02-09 Manuscript/Tmatrix.tex
@@
 % 
-\newcommand{\Norb}{N_\text{orb}}
+\newcommand{\Norb}{K}
 \newcommand{\Nocc}{O}
@@
 \end{equation}
-The pp-RPA problem yields, in the absence of instabilities (which should not appear in Coulombic systems with repulsive interactions only \cite{Scuseria_2013}), $V(V-1)/2$ positive eigenvalues $\Om{n}{N+2}$ and $O(O-1)/2$ negative eigenvalues $\Om{n}{N-2}$, which  correspond respectively to double attachments and double detachments.
+The pp-RPA problem yields, in the absence of instabilities (which should not appear in Coulombic systems with repulsive interactions only \cite{Scuseria_2013}), $\Nvir(\Nvir-1)/2$ positive eigenvalues $\Om{n}{N+2}$ and $\Nocc(\Nocc-1)/2$ negative eigenvalues $\Om{n}{N-2}$, which  correspond respectively to double attachments and double detachments.
 The pp-RPA correlation energies is given by \cite{Peng_2013,Scuseria_2013}
@@
 \end{subequations}
-The eigenvalues $\Om{m}{\BSE}$ of Eq.~\eqref{eq:BSE} provide $OV$ singlet (\ie, spin-conserved) and $OV$ triplet  (\ie, spin-flip) single excitations.
+The eigenvalues $\Om{m}{\BSE}$ of Eq.~\eqref{eq:BSE} provide $\Nocc\Nvir$ singlet (\ie, spin-conserved) and $\Nocc\Nvir$ triplet  (\ie, spin-flip) single excitations.
 Note that the spin structure of the BSE@$GT$ equations is analogous to the BSE@$GW$ version, \cite{Monino_2021} and one can compute separately singlet and triplet excitation energies.
@@
 
-In terms of computational cost, the overall scaling of BSE@$GT$ is equivalent to BSE@$GW$ as they both correspond to seeking the lowest eigenvalues of a matrix of size $(2OV \times 2OV)$. 
-Searching iteratively for the lowest eigenstates can be routinely performed via Davidson's algorithm with a $\order*{K^4}$ computational cost. \cite{Davidson_1975}
+In terms of computational cost, the overall scaling of BSE@$GT$ is equivalent to BSE@$GW$ as they both correspond to seeking the lowest eigenvalues of a matrix of size $(2\Nocc\Nvir \times 2\Nocc\Nvir)$.
+Searching iteratively for the lowest eigenstates can be routinely performed via Davidson's algorithm with a $\order*{\Norb^4}$ computational cost. \cite{Davidson_1975}
 The cost of the dynamical correction, which is thoroughly discussed in Ref.~\onlinecite{Loos_2020h}, is more expensive but is again equivalent in both formalisms.
-The computational cost associated with the computation of the $T$-matrix and the screening $W$ both scale as $\order*{K^6}$ as one must obtain, respectively, all the eigenvalues and eigenvectors of the pp-RPA and ph-RPA problems.
+The computational cost associated with the computation of the $T$-matrix and the screening $W$ both scale as $\order*{\Norb^6}$ as one must obtain, respectively, all the eigenvalues and eigenvectors of the pp-RPA and ph-RPA problems.
 However, the prefactor of the pp-RPA calculation is significantly larger than its ph-RPA counterpart due to the larger size of the pp-RPA matrices and its non-Hermitian nature.
@@
 Moreover, within the $T$-matrix formalism, one must compute both the singlet and triplet contributions of the $T$-matrix, while for singlet states, only the singlet contribution of $W$ contributes to the self-energy.
-Although similar approaches remain to be developed for the $T$-matrix formalism, contour deformation and density fitting techniques can be efficiently implemented in the case of $GW$ to reduce the scaling to $\order*{K^3}$.
+Although similar approaches remain to be developed for the $T$-matrix formalism, contour deformation and density fitting techniques can be efficiently implemented in the case of $GW$ to reduce the scaling to $\order*{\Norb^3}$.
 \cite{Duchemin_2019,Duchemin_2020,Duchemin_2021}
@@
 %%%%%%%%%%%%%%%%%%%%%%
-As a first didactical example, we consider the lowest singlet and triplet excited states of the hydrogen molecule \ce{H2} and the variation of their respective excitation energies upon dissociation.
+As a first didactical example, we consider the lowest singlet and triplet excited states of the hydrogen molecule \ce{H2} and the variation of their respective vertical transition energies upon dissociation.
 The excitation energies associated with these low-lying excited states are represented in Fig.~\ref{fig:H2} as a function of the internuclear distance $R_{\ce{H-H}}$ at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
 The variation of the HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:H2_gap}
-This shows that, as already observed in the Hubbard dimer, \cite{Romaniello_2012} the $G_0W_0$ and $G_0T_0$ quasiparticle energies are very similar near the Fermi level.
+This shows that, as already observed in the Hubbard dimer \cite{Romaniello_2012} and in molecular systems, \cite{Zhang_2017} the $G_0W_0$ and $G_0T_0$ quasiparticle energies are similar near the Fermi level.
 
-The performances of BSE@$G_0W_0$ and BSE@$G_0T_0$ are very similar for this system.
-For the lowest singlet excited state $B{}^1\Sigma_u^+$, the $T$-matrix-based formalism is slightly better when $R_{\ce{H-H}}$ increases but fails ultimately to reproduce the FCI results.
-For the $E{}^1\Sigma_g^+$ state, BSE@$G_0T_0$
-Note that both formalisms cannot see the $F{}^1\Sigma_g^+$ doubly-excited states and cannot model properly the avoided crossing between $E{}^1\Sigma_g^+$ and $F{}^1\Sigma_g^+$.
-Similar observations can be done for the triplet states.
+Overall, as evidenced by Fig.~\ref{fig:H2}, the performances of BSE@$G_0W_0$ and BSE@$G_0T_0$ are analogous for this system.
+For the lowest singlet excited state of $\text{B}\,{}^1\Sigma_u^+$ symmetry, the $T$-matrix-based formalism is slightly better when $R_{\ce{H-H}}$ increases but fails ultimately to reproduce the FCI results.
+For the $\text{E}\,{}^1\Sigma_g^+$ state, BSE@$G_0T_0$ is more accurate than BSE@$G_0W_0$ for small bond length and the scenario is reversed after the avoided crossing with the doubly-excited state of $\text{F}\,{}^1\Sigma_g^+$ symmetry.
+Of course, both formalisms cannot ``see'' the $\text{F}\,{}^1\Sigma_g^+$ states as the static BSE formalism is blind to double excitations.
+Therefore, it cannot model properly the avoided crossing between $\text{E}\,{}^1\Sigma_g^+$ and $\text{F}\,{}^1\Sigma_g^+$ states.
+For the $\text{B'}\,{}^1\Sigma_u^+$ and $\text{C}\,{}^1\Pi_u$ states, BSE@$G_0W_0$ and BSE@$G_0T_0$ reproduces fairly well the FCI potential energy curves with a modest preference for the latter.
+
+Similar observations can be made for the triplet states, the $GW$- and $GT$-based formalisms yielding very similar excitation energies, except maybe for the $\text{c}\,{}^3\Pi_u$ state for which BSE@$G_0W_0$ has clearly the edge.
+Moreover, triplet instabilities seems to affect BSE@$G_0T_0$ slightly earlier than BSE@$G_0W_0$.
 
@@
 
+In Fig.~\ref{fig:H2_dBSE}, we show the energy shift provided by the dynamical correction for the lowest singlet and lowest triplet excited states of \ce{H2} as a function of $R_{\ce{H-H}}$. 
+These dynamically-corrected schemes are labeled dBSE@$G_0W_0$ and dBSE@$G_0T_0$.
+For the singlet state of $\text{B}\,{}^1\Sigma_u^+$ symmetry, the dynamical correction improves slightly the excitation energies at small internuclear distances for both schemes, while, for larger bond lengths, an improvement is only visible at the $T$-matrix level.
+Note that, for this system with few electrons, the dynamical corrections are quite small in magnitude.
+In the case of the triplet state of $\text{b}\,{}^3\Sigma_u^+$ symmetry, the dynamical correction worsens the results compared to FCI, especially in the case of BSE@$G_0W_0$.
+
+%%% FIGURE 3 %%%
+\begin{figure*}
+	\includegraphics[width=0.4\linewidth]{H2_dBSE1}
+	\hspace{0.1\linewidth}
+	\includegraphics[width=0.4\linewidth]{H2_dBSE3}
+	\caption{
+	Error with respect to FCI for the lowest singlet (left) and the lowest triplet (right) excitation energies of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed within the static scheme (BSE@$G_0W_0$ and BSE@$G_0T_0$) and the dynamically-corrected scheme (dBSE@$G_0W_0$ and dBSE@$G_0T_0$) .
+	The cc-pVTZ basis is employed for all calculations.
+	Raw data are reported in {\SupInf}.}
+	\label{fig:H2_dBSE}
+\end{figure*}
+%%% %%% %%% %%%
+
 %%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%
-As a second example, we consider the symmetric dissociation of the linear molecule beryllium hydride \ce{BeH2}.
-The variation in excitation energies as a function of the distance $R_{\ce{Be-H}}$ is shown in Fig.~\ref{fig:BeH2}.
-The variation of the HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:BeH2_gap}
-Again, the $G_0W_0$ and $G_0T_0$ quasiparticle energies are very similar near the Fermi level.
+As a second example, we consider the symmetric dissociation of the linear molecule beryllium hydride (\ce{BeH2}), a system for which one can assume that the screening may play a more important role than in the previous example.
+The variation of the lowest singlet and triplet excitation energies as a function of the distance $R_{\ce{Be-H}}$ is shown in Fig.~\ref{fig:BeH2}, while the quasiparticle energies of the frontier orbitals and the associated (fundamental) gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:BeH2_gap}.
+Again, one notes that the $G_0W_0$ and $G_0T_0$ quasiparticle energies are very similar near the Fermi level.
+Therefore, one can safely assume that any significant variation of the excitation energies computed within the $GW$- and $GT$-based formalisms originates mainly from their distinct kernel.
+The excitation energies computed with the dynamical schemes, dBSE@$G_0W_0$ and dBSE@$G_0T_0$, are reported as thin solid lines.
+Here, one can show that dynamical corrections improves in most cases the agreement between BSE and FCI.
 
-Dynamical corrections slightly improves the agreement between BSE and FCI.
+For the four lowest singlet excited states (left panel of Fig.~\ref{fig:BeH2}), dBSE@$G_0T_0$ is clearly better than dBSE@$G_0W_0$, while the opposite trend is observed for the four lowest triplet states (right panel of Fig.~\ref{fig:BeH2}).
+Note that, for large $R_{\ce{Be-H}}$, the two BSE-based schemes provide only a qualitative description of the excited states with error of several \si{\eV}.
+Nonetheless, the overall ordering of the excited states are globally respected.
 
-%%% FIGURE 3 %%%
+%%% FIGURE 4 %%%
 \begin{figure*}

### 2022-02-10 Manuscript/Tmatrix.tex
moving figures
data for molecules
savig work

@@
 
+\newcommand{\pps}{\pi \to \pi^*}
+\newcommand{\nps}{n \to \pi^*}
 \DeclareSIUnit\angstrom{\text{\AA}}
@@
 Although the dynamical correction is computed in the dTDA throughout, the zeroth-order excitonic Hamiltonian [see Eq.~\eqref{eq:BSE}] is always the ``full'' BSE static Hamiltonian, i.e., without TDA. 
+Reference full configuration interaction (FCI) calculations have been performed with {\QP}. \cite{Garniron_2019}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%
-As a first didactical example, we consider the lowest singlet and triplet excited states of the hydrogen molecule \ce{H2} and the variation of their respective vertical transition energies upon dissociation.
-The excitation energies associated with these low-lying excited states are represented in Fig.~\ref{fig:H2} as a function of the internuclear distance $R_{\ce{H-H}}$ at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
-The variation of the HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:H2_gap}
-This shows that, as already observed in the Hubbard dimer \cite{Romaniello_2012} and in molecular systems, \cite{Zhang_2017} the $G_0W_0$ and $G_0T_0$ quasiparticle energies are similar near the Fermi level.
-
-Overall, as evidenced by Fig.~\ref{fig:H2}, the performances of BSE@$G_0W_0$ and BSE@$G_0T_0$ are analogous for this system.
-For the lowest singlet excited state of $\text{B}\,{}^1\Sigma_u^+$ symmetry, the $T$-matrix-based formalism is slightly better when $R_{\ce{H-H}}$ increases but fails ultimately to reproduce the FCI results.
-For the $\text{E}\,{}^1\Sigma_g^+$ state, BSE@$G_0T_0$ is more accurate than BSE@$G_0W_0$ for small bond length and the scenario is reversed after the avoided crossing with the doubly-excited state of $\text{F}\,{}^1\Sigma_g^+$ symmetry.
-Of course, both formalisms cannot ``see'' the $\text{F}\,{}^1\Sigma_g^+$ states as the static BSE formalism is blind to double excitations.
-Therefore, it cannot model properly the avoided crossing between $\text{E}\,{}^1\Sigma_g^+$ and $\text{F}\,{}^1\Sigma_g^+$ states.
-For the $\text{B'}\,{}^1\Sigma_u^+$ and $\text{C}\,{}^1\Pi_u$ states, BSE@$G_0W_0$ and BSE@$G_0T_0$ reproduces fairly well the FCI potential energy curves with a modest preference for the latter.
-
-Similar observations can be made for the triplet states, the $GW$- and $GT$-based formalisms yielding very similar excitation energies, except maybe for the $\text{c}\,{}^3\Pi_u$ state for which BSE@$G_0W_0$ has clearly the edge.
-Moreover, triplet instabilities seems to affect BSE@$G_0T_0$ slightly earlier than BSE@$G_0W_0$.
 
@@
 
-In Fig.~\ref{fig:H2_dBSE}, we show the energy shift provided by the dynamical correction for the lowest singlet and lowest triplet excited states of \ce{H2} as a function of $R_{\ce{H-H}}$. 
-These dynamically-corrected schemes are labeled dBSE@$G_0W_0$ and dBSE@$G_0T_0$.
-For the singlet state of $\text{B}\,{}^1\Sigma_u^+$ symmetry, the dynamical correction improves slightly the excitation energies at small internuclear distances for both schemes, while, for larger bond lengths, an improvement is only visible at the $T$-matrix level.
-Note that, for this system with few electrons, the dynamical corrections are quite small in magnitude.
-In the case of the triplet state of $\text{b}\,{}^3\Sigma_u^+$ symmetry, the dynamical correction worsens the results compared to FCI, especially in the case of BSE@$G_0W_0$.
-
 %%% FIGURE 3 %%%
@@
 
+As a first didactical example, we consider the lowest singlet and triplet excited states of the hydrogen molecule \ce{H2} and the variation of their respective vertical transition energies upon dissociation.
+The excitation energies associated with these low-lying excited states are represented in Fig.~\ref{fig:H2} as a function of the internuclear distance $R_{\ce{H-H}}$ at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
+The variation of the HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:H2_gap}
+This shows that, as already observed in the Hubbard dimer \cite{Romaniello_2012} and in molecular systems, \cite{Zhang_2017} the $G_0W_0$ and $G_0T_0$ quasiparticle energies are similar near the Fermi level.
+
+Overall, as evidenced by Fig.~\ref{fig:H2}, the performances of BSE@$G_0W_0$ and BSE@$G_0T_0$ are analogous for this system.
+For the lowest singlet excited state of $\text{B}\,{}^1\Sigma_u^+$ symmetry, the $T$-matrix-based formalism is slightly better when $R_{\ce{H-H}}$ increases but fails ultimately to reproduce the FCI results.
+For the $\text{E}\,{}^1\Sigma_g^+$ state, BSE@$G_0T_0$ is more accurate than BSE@$G_0W_0$ for small bond length and the scenario is reversed after the avoided crossing with the doubly-excited state of $\text{F}\,{}^1\Sigma_g^+$ symmetry.
+Of course, both formalisms cannot ``see'' the $\text{F}\,{}^1\Sigma_g^+$ states as the static BSE formalism is blind to double excitations.
+Therefore, it cannot model properly the avoided crossing between $\text{E}\,{}^1\Sigma_g^+$ and $\text{F}\,{}^1\Sigma_g^+$ states.
+For the $\text{B'}\,{}^1\Sigma_u^+$ and $\text{C}\,{}^1\Pi_u$ states, BSE@$G_0W_0$ and BSE@$G_0T_0$ reproduces fairly well the FCI potential energy curves with a modest preference for the latter.
+
+Similar observations can be made for the triplet states, the $GW$- and $GT$-based formalisms yielding very similar excitation energies, except maybe for the $\text{c}\,{}^3\Pi_u$ state for which BSE@$G_0W_0$ has clearly the edge.
+Moreover, triplet instabilities seems to affect BSE@$G_0T_0$ slightly earlier than BSE@$G_0W_0$.
+
+In Fig.~\ref{fig:H2_dBSE}, we show the energy shift provided by the dynamical correction for the lowest singlet and lowest triplet excited states of \ce{H2} as a function of $R_{\ce{H-H}}$. 
+These dynamically-corrected schemes are labeled dBSE@$G_0W_0$ and dBSE@$G_0T_0$.
+For the singlet state of $\text{B}\,{}^1\Sigma_u^+$ symmetry, the dynamical correction improves slightly the excitation energies at small internuclear distances for both schemes, while, for larger bond lengths, an improvement is only visible at the $T$-matrix level.
+Note that, for this system with few electrons, the dynamical corrections are quite small in magnitude.
+In the case of the triplet state of $\text{b}\,{}^3\Sigma_u^+$ symmetry, the dynamical correction worsens the results compared to FCI, especially in the case of BSE@$G_0W_0$.
+
 %%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%
-As a second example, we consider the symmetric dissociation of the linear molecule beryllium hydride (\ce{BeH2}), a system for which one can assume that the screening may play a more important role than in the previous example.
-The variation of the lowest singlet and triplet excitation energies as a function of the distance $R_{\ce{Be-H}}$ is shown in Fig.~\ref{fig:BeH2}, while the quasiparticle energies of the frontier orbitals and the associated (fundamental) gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:BeH2_gap}.
-Again, one notes that the $G_0W_0$ and $G_0T_0$ quasiparticle energies are very similar near the Fermi level.
-Therefore, one can safely assume that any significant variation of the excitation energies computed within the $GW$- and $GT$-based formalisms originates mainly from their distinct kernel.
-The excitation energies computed with the dynamical schemes, dBSE@$G_0W_0$ and dBSE@$G_0T_0$, are reported as thin solid lines.
-Here, one can show that dynamical corrections improves in most cases the agreement between BSE and FCI.
-
-For the four lowest singlet excited states (left panel of Fig.~\ref{fig:BeH2}), dBSE@$G_0T_0$ is clearly better than dBSE@$G_0W_0$, while the opposite trend is observed for the four lowest triplet states (right panel of Fig.~\ref{fig:BeH2}).
-Note that, for large $R_{\ce{Be-H}}$, the two BSE-based schemes provide only a qualitative description of the excited states with error of several \si{\eV}.
-Nonetheless, the overall ordering of the excited states are globally respected.
 
@@
 
+As a second example, we consider the symmetric dissociation of the linear molecule beryllium hydride (\ce{BeH2}), a system for which one can assume that the screening may play a more important role than in the previous example.
+The variation of the lowest singlet and triplet excitation energies as a function of the distance $R_{\ce{Be-H}}$ is shown in Fig.~\ref{fig:BeH2}, while the quasiparticle energies of the frontier orbitals and the associated (fundamental) gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:BeH2_gap}.
+Again, one notes that the $G_0W_0$ and $G_0T_0$ quasiparticle energies are very similar near the Fermi level.
+Therefore, one can safely assume that any significant variation of the excitation energies computed within the $GW$- and $GT$-based formalisms originates mainly from their distinct kernel.
+The excitation energies computed with the dynamical schemes, dBSE@$G_0W_0$ and dBSE@$G_0T_0$, are reported as thin solid lines.
+Here, one can show that dynamical corrections improves in most cases the agreement between BSE and FCI.
+All calculations are performed with the cc-pVDZ basis.
+
+For the four lowest singlet excited states (left panel of Fig.~\ref{fig:BeH2}), dBSE@$G_0T_0$ is clearly better than dBSE@$G_0W_0$, while the opposite trend is observed for the four lowest triplet states (right panel of Fig.~\ref{fig:BeH2}).
+Note that, for large $R_{\ce{Be-H}}$, the two BSE-based schemes provide only a qualitative description of the excited states with error of several \si{\eV}.
+Nonetheless, the overall ordering of the excited states are globally respected.
+
 %%%%%%%%%%%%%%%%%%%%%%
@@
 Table \ref{tab:mol} reports singlet and triplet vertical excitation energies for various molecular systems at equilibrium geometry.
-In addition to the BSE-based models studied in the present manuscript, we have selected well-known methods \titou{(CIS, CIS(D), TDHF and FCI)}.
+In addition to the BSE-based models studied in the present manuscript, we have selected well-known methods, namely CIS, CIS(D), TDHF, and FCI (taken as reference).
 
@@
 \begin{table*}
-	\caption{Singlet and triplet excitation energies (in \si{\eV}) of various molecular systems at equilibrium geometry computed at various levels of theory with the cc-pVDZ basis set.
-	The corresponding experimental equilibrium geometries have been extracted from the computational chemistry comparison and benchmark database (CCCBDB) at \url{https://cccbdb.nist.gov}.}
+	\caption{Singlet and triplet excitation energies (in \si{\eV}) of various molecular systems at equilibrium geometry computed at various levels of theory with the aug-cc-pVDZ basis set.
+	The corresponding equilibrium geometries as well as the reference FCI values have been extracted from the QUEST database. \cite{Veril_2021}}
 	\label{tab:mol}
 	\begin{ruledtabular}
-		\begin{tabular}{lcccccccc}
-					&			&	\mc{7}{c}{Methods}																\\
-			\cline{3-9}
-			Mol.	&	State	&	CIS		&	CIS(D)	&	TDHF	&	BSE@$GW$	&	dBSE@$GW$	&	BSE@$GT$	&	dBSE@$GT$	\\
+		\begin{tabular}{llccccccccc}
+					&			&		&	\mc{8}{c}{Methods}																\\
+			\cline{4-11}
+			Mol.	&	State	&	Nature						&	CIS		&	CIS(D)	&	TDHF	&	BSE@$G_0W_0$	&	dBSE@$G_0W_0$	&	BSE@$G_0T_0$	&	dBSE@$G_0T_0$	&	FCI	\\
 			\hline
-			\ce{H2}	&			&	\\
-			\ce{LiH}	&			&	\\
-			\ce{LiF}	&			&	\\
-			\ce{BF}	&			&	\\
-			\ce{CO}	&			&	\\
-			\ce{N2}	&			&	\\
-			\ce{F2}	&			&	\\
-			\ce{FH}	&			&	\\
+			\ce{H2O}	&	$^1B_1(n \to 3s)$		&	Ryd.	&	8.66	&	6.61	&	8.61	&	7.70	&	7.62	&	6.84	&	6.80	&	7.53\\
+						&	$^1A_2(n \to 3p)$		&	Ryd.	&	10.34	&	8.33	&	10.30	&	9.41	&	9.34	&	8.60	&	8.56	&	9.32\\
+						&	$^3B_1(n \to 3s)$		&	Ryd.	&	7.98	&	6.69	&	7.86	&	7.23	&	7.09	&	6.30	&	6.23	&	7.14\\
+						&	$^3A_2(n \to 3p)$		&	Ryd.	&	10.01	&	8.70	&	9.89	&	9.22	&	9.11	&	8.36	&	8.29	&	9.14\\
+			\ce{HCl}	&	$^1\Pi$					&	CT		&	8.36	&	7.87	&	8.31	&	8.04	&	7.95	&	7.42	&	7.38	&	7.82\\
+			\ce{HC#CH}	&	$^1\Sigma_u^-(\pps)$	&	Val.	&	6.28	&	6.29	&	5.91	&	7.27	&	6.96	&	5.64	&	5.55	&	7.20\\
+						&	$^1\Delta_u(\pps)$		&	Val.	&	6.62	&	6.97	&	6.44	&	7.61	&	7.33	&	5.87	&	5.81	&	7.51\\
+						&	$^3\Sigma_u^+(\pps)$	&	Val.	&	4.52	&	5.75	&	2.19	&	5.63	&	5.12	&	4.02	&	3.83	&	5.50\\
+						&	$^3\Delta_u(\pps)$		&	Val.	&	5.45	&	6.65	&	4.52	&	6.52	&	6.13	&	4.87	&	4.74	&	6.46\\
+			\ce{H2C=NH}	&	$^1A''(\nps)$			&	Val.	&	5.86	&	4.46	&	5.69	&	6.16	&	5.85	&	4.12	&	4.04	&	5.25\\
+						&	$^3A''(\nps)$			&	Val.	&	4.71	&	4.72	&	4.39	&	5.49	&	4.96	&	3.25	&	3.11	&	4.63\\
 		\end{tabular}

### 2022-02-12 Manuscript/Tmatrix.tex
Pina's changes

@@
 \begin{equation}
-	\braket{pq}{rs} = \iint \SO{p}(\bx_1) \SO{q}(\bx_1) \frac{1}{\abs{\br_1 - \br_2}} \SO{r}(\bx_2) \SO{s}(\bx_2)  d\bx_1 d\bx_2
+	\braket{pq}{rs} = \iint \SO{p}(\bx_1) \SO{q}(\bx_2) \frac{1}{\abs{\br_1 - \br_2}} \SO{r}(\bx_1) \SO{s}(\bx_2)  d\bx_1 d\bx_2
 \end{equation}
@@
 
-To recast the BSE with a dynamical $T$-matrix kernel as an eigenvalue equation, we follow Ref.~\onlinecite{Strinati_1980} (see also Ref.~\onlinecite{Loos_2020e}) and start from the equation for the BSE amplitude
+In order to derive the dynamical kernel $\tilde{T}_{ib,aj}$ given in equation Eq.~\eqref{eq:dT}, we follow Ref.~\onlinecite{Strinati_1980} (see also Ref.~\onlinecite{Loos_2020e}) and start from the equation for the BSE right-hand side electron-hole amplitude
 \begin{equation}
@@
 \label{eq:T-matrix_kernel}
-	\Xi(3,5,4,6) & =  i\frac{\delta \Sigma(3,4)}{\delta G(6,5)}\approx -T(3,5,4,6)
+	\Xi(3,5,4,6) & =  i\frac{\delta \Sigma(3,4)}{\delta G(6,5)}\approx -T(3,5,4,6).
 \end{align}
+Equation (\ref{eq:Strinati_1}) is derived by assuming a particular (resonant) pole $\omega_S=E_S-E_0>0$ of $L$ to be isolated from the other poles, which is usually the case for neutral excitations in finite systems, and  by assuming the poles of $L_0$ to be different form $\omega_S$, which is in general the case.
 The so-called $T$-matrix self-energy $\Sigma$ is given by Eq.~\eqref{eq:SigGT} with \cite{Martin_2016,Romaniello_2012}
@@
 where $v$ is the bare Coulomb operator and we neglect the functional derivative $\delta T/\delta G$ in the kernel $\Xi$.
+We also notice that the first two terms on the right-hand side of Eq.~(\ref{eq:T-matrix}) Hartree and exchange contributions to the T matrix ($T^{\text{HF}}$), whereas the last term is the correlation contribution $T^c=T-T^{\text{HF}}$.
 Making the time dependence of Eq.~\eqref{eq:Strinati_1} explicit and defining $T(3,5,4,6)=- \delta(\tau^+_{35})\delta(\tau^+_{64})\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})$, one gets 
@@
 	\\
-	+ i \int d7 d8 v(\bx_3,x_5)G(\bx_3,\bx_7;\tau_{38})G(\bx_5,\bx_8;\tau^+_{38})\Bar{T}(\bx_7,\bx_8,\bx_4,\bx_6;\tau_{84})
+	+ i \int d7 d8 v(\bx_3,\bx_5)G(\bx_3,\bx_7;\tau_{38})G(\bx_5,\bx_8;\tau^+_{38})\Bar{T}(\bx_7,\bx_8,\bx_4,\bx_6;\tau_{84}).
 \end{multline}
@@
 	\\
-	 \times \Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}
+	 \times \Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}.
 \end{multline}
@@
 \begin{equation}
-	\Theta(\pm\tau)e^{-i\alpha \tau}=\mp\frac{1}{2\pi i}\lim_{\eta\to 0^+}\int d\omega \frac{1}{\omega-\alpha\pm i\eta}e^{-i\omega\tau}
+	\Theta(\pm\tau)e^{-i\alpha \tau}=\mp\frac{1}{2\pi i}\lim_{\eta\to 0^+}\int d\omega \frac{1}{\omega-\alpha\pm i\eta}e^{-i\omega\tau}.
 \end{equation}
 
-We now consider the resonant case, \ie, $\omega_S>0$, for which 
+For the resonant case, \ie, $\omega_S>0$, 
 \begin{equation}
@@
 	\chi_S(\bx_1,\bx_{1'},\tau_1) 
-	=-e^{i\omega_S\abs{\tau_1}/2} \sum_{pq}\SO{p}(\bx_1)\SO{q}(\bx_{1'}) \mel{N}{\hat{c}^\dagger_{q}\hat{c}_p}{N,S}
-  	\qty[\Theta(\tau_1)e^{-i\e{p}{}\tau_1}+\Theta(-\tau_1)e^{-i\e{q}{}\tau_1} ]
+	=-e^{i\omega_S\abs{\tau_1}/2} \sum_{jb}\SO{b}(\bx_1)\SO{j}(\bx_{1'}) \mel{N}{\hat{c}^\dagger_{j}\hat{c}_b}{N,S}
+  	\qty[\Theta(\tau_1)e^{-i\e{b}{}\tau_1}+\Theta(-\tau_1)e^{-i\e{j}{}\tau_1} ]
 \end{equation}
@@
 	\\
-    = -\sum_{pq}\mel{N}{\hat{c}^\dagger_{q}\hat{c}_p}{N,S}
-    \qty{ -\frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\ \Bar{T}_{iq,pa}(\omega) e^{-i\omega\eta} \qty[\frac{1}{\omega_S-\omega+\e{q}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{p}{}-\e{a}{}+i\eta} ] }
+    = -\sum_{jb}\mel{N}{\hat{c}^\dagger_{j}\hat{c}_b}{N,S}
+    \qty{ -\frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\ \Bar{T}_{ib,aj}(\omega) e^{-i\omega\eta} \qty[\frac{1}{\omega_S-\omega+\e{j}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{b}{}-\e{a}{}+i\eta} ] }
 \end{multline}
@@
 \begin{equation}
-	\Bar{T}_{iq,pa}(\tau_{34})=\int d\bx_3 d\bx_4 d\bx_5 d\bx_6 \SO{a}(\bx_3) \SO{i}(\bx_4)\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34}) \SO{p}(\bx_6)\SO{q}(\bx_5)
+	\Bar{T}_{ib,aj}(\tau_{34})=\int d\bx_3 d\bx_4 d\bx_5 d\bx_6 \SO{a}(\bx_3) \SO{i}(\bx_4)\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34}) \SO{b}(\bx_6)\SO{j}(\bx_5).
 \end{equation}
@@
 	\label{eq:egval}
-	\qty(\e{a}{}-\e{i}{}-\omega_S) X_{ia,S}+\sum_{pq}X_{qp,S}\widetilde{T}_{iq,pa}(\omega_S)=0
+	\qty(\e{a}{}-\e{i}{}-\omega_S) X_{ia,S}+\sum_{jb}X_{jb,S}\mel{ib}{}{aj}+\sum_{jb}X_{jb,S}\widetilde{T}_{ib,aj}(\omega_S)=0
 \end{equation}
+%with $$\langle ab|ij\rangle=\int d\bx_1d\bx_2 \SO{a}(\bx_1) \SO{b}(\bx_2)v(\bx_1,\bx_2) \SO{i}(\bx_1) \SO{j}(\bx_2),$$ 
 where the spectral representation of the dynamical $T$-matrix is
 \begin{equation}
-	\widetilde{T}_{iq,pa}(\omega_S)
-	= \frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\Bar{T}_{iq,pa}(\omega)e^{-i\omega\eta} \left[\frac{1}{\omega_S-\omega+\e{q}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{p}{}-\e{a}{}+i\eta}\right] 
+	\widetilde{T}_{ib,aj}(\omega_S)
+	= \frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\Bar{T}^c_{ib,aj}(\omega)e^{-i\omega\eta} \left[\frac{1}{\omega_S-\omega+\e{j}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{b}{}-\e{a}{}+i\eta}\right].
  \label{eq:H2preso_eigen_2_T}
@@
 \label{eq:H2preso_eigen}
-	H_{ia,qp}(\omega_S) X_{qp,S}=\omega_S X_{ia,S}
+	A_{ia,jb}(\omega_S) X_{jb,S}=\omega_S X_{ia,S}
 \end{equation}
@@
 \begin{equation}
-	H_{ia,qp}(\omega_S)=(\e{a}{}-\e{i}{})\delta_{iq}\delta_{ap} + \mel{ip}{}{aq}+\widetilde{T}_{iq,pa}(\omega_S).
+	A_{ia,jb}(\omega_S)=(\e{a}{}-\e{i}{})\delta_{ij}\delta_{ab} +\mel{ib}{}{aj}+\widetilde{T}_{ib,aj}(\omega_S).
 \end{equation}
-Here $H_{ia,jb}(\omega_S)=A_{ia,jb}(\omega_S)$ and $H_{ia,bj}(\omega_S)=B_{ia,jb}(\omega_S)$.
-If one drops the correlation part of $\Bar{T}$ [the first two terms on the right-hand side of Eq.~\eqref{eq:T_bar}], one ends up the usual time-dependent Hartree-Fock (TDHF) equations. 
+%Here $H_{ia,jb}(\omega_S)=A_{ia,jb}(\omega_S)$ and $H_{ia,bj}(\omega_S)=B_{ia,jb}(\omega_S)$.
+If one drops the dynamical part $\widetilde{T}$, one ends up with the usual time-dependent Hartree-Fock (TDHF) equations. 
 To calculate the correlation contribution, one must employ \eqref{eq:T} in Eq.~\eqref{eq:H2preso_eigen_2_T}, and after integration over the frequency, it yields Eq.~\eqref{eq:dT}.

### 2022-02-12 Manuscript/Tmatrix.tex
res
water

@@
 \cite{Bintrim_2021b}
+Additional details about the derivation of Eq.~\eqref{eq:dT} are reported in Appendix \ref{app:dBSE}.
 
@@
 \cite{Peng_2013,Scuseria_2013,Yang_2013,Yang_2013b,Yang_2014a,Zhang_2015,Zhang_2016}
-Moreover, within the $T$-matrix formalism, one must compute both the singlet and triplet contributions of the $T$-matrix, while for singlet states, only the singlet contribution of $W$ contributes to the self-energy.
+Moreover, within the $T$-matrix formalism, one must compute both the singlet and triplet contributions of the $T$-matrix, while for singlet states, only the singlet part of $W$ is required.
 Although similar approaches remain to be developed for the $T$-matrix formalism, contour deformation and density fitting techniques can be efficiently implemented in the case of $GW$ to reduce the scaling to $\order*{\Norb^3}$.
@@
 	\caption{
-	Error with respect to FCI for the lowest singlet (left) and the lowest triplet (right) excitation energies of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed within the static scheme (BSE@$G_0W_0$ and BSE@$G_0T_0$) and the dynamically-corrected scheme (dBSE@$G_0W_0$ and dBSE@$G_0T_0$) .
+	Error with respect to FCI for the lowest singlet (left) and the lowest triplet (right) excitation energies of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed within the static schemes (BSE@$G_0W_0$ and BSE@$G_0T_0$) and the dynamically-corrected schemes (dBSE@$G_0W_0$ and dBSE@$G_0T_0$) .
 	The cc-pVTZ basis is employed for all calculations.
@@
 The excitation energies associated with these low-lying excited states are represented in Fig.~\ref{fig:H2} as a function of the internuclear distance $R_{\ce{H-H}}$ at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
-The variation of the HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:H2_gap}
+The variation of the HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:H2_gap}.
 This shows that, as already observed in the Hubbard dimer \cite{Romaniello_2012} and in molecular systems, \cite{Zhang_2017} the $G_0W_0$ and $G_0T_0$ quasiparticle energies are similar near the Fermi level.
@@
 	\includegraphics[width=\textwidth]{BeH2}
-	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{BeH2} as a function of the distance $R_{\ce{Be-H}}$ (in \si{\angstrom}) computed at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels.
-	The dynamically-corrected BSE excitation energies are represented as thin lines for dBSE@$G_0W_0$ (blue), and dBSE@$G_0T_0$ (red) with the cc-pVDZ basis.
+	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{BeH2} as a function of the distance $R_{\ce{Be-H}}$ (in \si{\angstrom}) computed at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVDZ basis.
+	The dynamically-corrected BSE excitation energies are represented as thin lines for dBSE@$G_0W_0$ (blue) and dBSE@$G_0T_0$ (red).
 	Raw data are reported in {\SupInf}.}
@@
 
-As a second example, we consider the symmetric dissociation of the linear molecule beryllium hydride (\ce{BeH2}), a system for which one can assume that the screening may play a more important role than in the previous example.
+As a second example, we consider the symmetric dissociation of the linear molecule beryllium hydride (\ce{BeH2}), a system for which one can assume that the screening plays a more important role than in the previous example.
 The variation of the lowest singlet and triplet excitation energies as a function of the distance $R_{\ce{Be-H}}$ is shown in Fig.~\ref{fig:BeH2}, while the quasiparticle energies of the frontier orbitals and the associated (fundamental) gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:BeH2_gap}.
@@
 %%%%%%%%%%%%%%%%%%%%%%
-\subsection{Molecules at equilibrium}
-\label{sec:mol}
+\subsection{Excited states of water}
+\label{sec:H2O}
 %%%%%%%%%%%%%%%%%%%%%%
 
-Table \ref{tab:mol} reports singlet and triplet vertical excitation energies for various molecular systems at equilibrium geometry.
-In addition to the BSE-based models studied in the present manuscript, we have selected well-known methods, namely CIS, CIS(D), TDHF, and FCI (taken as reference).
+%%% FIGURE 6 %%%
+\begin{figure*}
+	\includegraphics[width=\linewidth]{H2O}
+	\caption{Error with respect to FCI for the singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{H2O} at equilibrium geometry computed at various levels of theory with the aug-cc-pVDZ basis.
+	The geometry as well as the reference FCI values have been extracted from the QUEST database. \cite{Veril_2021}
+	Raw data are reported in {\SupInf}.}
+	\label{fig:H2O}
+\end{figure*}
+%%% %%% %%% %%%
+
+As a third and final example, we compute the excitation energies associated with the two lowest singlet and two lowest triplet excited states of water at equilibrium geometry (see Fig.~\ref{fig:H2O}).
+Note that all these excited states are of Rydberg nature and correspond to $n \to 3s$ and $n \to 3p$ transitions for the $B_1$ and $A_2$ states, respectively.
+In addition to the BSE-based models studied in the present manuscript, we have selected well-known wave function methods, namely CIS, CIS(D), TDHF, and FCI (taken as reference) and computed the excitation energies for these transitions.
+Two key observations can be made:
+i) BSE@$G_0W_0$ is by far the best performer with a slight overestimation of the order of \SI{0.1}{eV} (as compared to FCI);
+ii) BSE@$G_0T_0$ systematically underestimates the excitation energies [similarly to CIS(D)] and outperforms CIS, CIS(D) and TDHF for the singlet states only. 
+These general trends are also observed for other systems and they nicely evidence the crucial role of the screening in $GW$, hinting that a screened version of the $T$-matrix formalism as proposed in Ref.~\onlinecite{Romaniello_2012} might be a promising way for improvement.
 
 %%% TABLE I %%%
-\begin{table*}
-	\caption{Singlet and triplet excitation energies (in \si{\eV}) of various molecular systems at equilibrium geometry computed at various levels of theory with the aug-cc-pVDZ basis set.
-	The corresponding equilibrium geometries as well as the reference FCI values have been extracted from the QUEST database. \cite{Veril_2021}}
-	\label{tab:mol}
-	\begin{ruledtabular}
-		\begin{tabular}{llccccccccc}
-					&			&		&	\mc{8}{c}{Methods}																\\
-			\cline{4-11}
-			Mol.	&	State	&	Nature						&	CIS		&	CIS(D)	&	TDHF	&	BSE@$G_0W_0$	&	dBSE@$G_0W_0$	&	BSE@$G_0T_0$	&	dBSE@$G_0T_0$	&	FCI	\\
-			\hline
-			\ce{H2O}	&	$^1B_1(n \to 3s)$		&	Ryd.	&	8.66	&	6.61	&	8.61	&	7.70	&	7.62	&	6.84	&	6.80	&	7.53\\
-						&	$^1A_2(n \to 3p)$		&	Ryd.	&	10.34	&	8.33	&	10.30	&	9.41	&	9.34	&	8.60	&	8.56	&	9.32\\
-						&	$^3B_1(n \to 3s)$		&	Ryd.	&	7.98	&	6.69	&	7.86	&	7.23	&	7.09	&	6.30	&	6.23	&	7.14\\
-						&	$^3A_2(n \to 3p)$		&	Ryd.	&	10.01	&	8.70	&	9.89	&	9.22	&	9.11	&	8.36	&	8.29	&	9.14\\
-			\ce{HCl}	&	$^1\Pi$					&	CT		&	8.36	&	7.87	&	8.31	&	8.04	&	7.95	&	7.42	&	7.38	&	7.82\\
-			\ce{HC#CH}	&	$^1\Sigma_u^-(\pps)$	&	Val.	&	6.28	&	6.29	&	5.91	&	7.27	&	6.96	&	5.64	&	5.55	&	7.20\\
-						&	$^1\Delta_u(\pps)$		&	Val.	&	6.62	&	6.97	&	6.44	&	7.61	&	7.33	&	5.87	&	5.81	&	7.51\\
-						&	$^3\Sigma_u^+(\pps)$	&	Val.	&	4.52	&	5.75	&	2.19	&	5.63	&	5.12	&	4.02	&	3.83	&	5.50\\
-						&	$^3\Delta_u(\pps)$		&	Val.	&	5.45	&	6.65	&	4.52	&	6.52	&	6.13	&	4.87	&	4.74	&	6.46\\
-			\ce{H2C=NH}	&	$^1A''(\nps)$			&	Val.	&	5.86	&	4.46	&	5.69	&	6.16	&	5.85	&	4.12	&	4.04	&	5.25\\
-						&	$^3A''(\nps)$			&	Val.	&	4.71	&	4.72	&	4.39	&	5.49	&	4.96	&	3.25	&	3.11	&	4.63\\
-		\end{tabular}
-	\end{ruledtabular}
-\end{table*}
+%\begin{table*}
+%	\caption{Singlet and triplet excitation energies (in \si{\eV}) of various molecular systems at equilibrium geometry computed at various levels of theory with the aug-cc-pVDZ basis set.
+%	The corresponding equilibrium geometries as well as the reference FCI values have been extracted from the QUEST database. \cite{Veril_2021}}
+%	\label{tab:mol}
+%	\begin{ruledtabular}
+%		\begin{tabular}{llccccccccc}
+%					&			&		&	\mc{8}{c}{Methods}																\\
+%			\cline{4-11}
+%			Mol.	&	State	&	Nature						&	CIS		&	CIS(D)	&	TDHF	&	BSE@$G_0W_0$	&	dBSE@$G_0W_0$	&	BSE@$G_0T_0$	&	dBSE@$G_0T_0$	&	FCI	\\
+%			\hline
+%			\ce{H2O}	&	$^1B_1(n \to 3s)$		&	Ryd.	&	8.66	&	6.61	&	8.61	&	7.70	&	7.62	&	6.84	&	6.80	&	7.53\\
+%						&	$^1A_2(n \to 3p)$		&	Ryd.	&	10.34	&	8.33	&	10.30	&	9.41	&	9.34	&	8.60	&	8.56	&	9.32\\
+%						&	$^3B_1(n \to 3s)$		&	Ryd.	&	7.98	&	6.69	&	7.86	&	7.23	&	7.09	&	6.30	&	6.23	&	7.14\\
+%						&	$^3A_2(n \to 3p)$		&	Ryd.	&	10.01	&	8.70	&	9.89	&	9.22	&	9.11	&	8.36	&	8.29	&	9.14\\
+%			\ce{HCl}	&	$^1\Pi$					&	CT		&	8.36	&	7.87	&	8.31	&	8.04	&	7.95	&	7.42	&	7.38	&	7.82\\
+%			\ce{HC#CH}	&	$^1\Sigma_u^-(\pps)$	&	Val.	&	6.28	&	6.29	&	5.91	&	7.27	&	6.96	&	5.64	&	5.55	&	7.20\\
+%						&	$^1\Delta_u(\pps)$		&	Val.	&	6.62	&	6.97	&	6.44	&	7.61	&	7.33	&	5.87	&	5.81	&	7.51\\
+%						&	$^3\Sigma_u^+(\pps)$	&	Val.	&	4.52	&	5.75	&	2.19	&	5.63	&	5.12	&	4.02	&	3.83	&	5.50\\
+%						&	$^3\Delta_u(\pps)$		&	Val.	&	5.45	&	6.65	&	4.52	&	6.52	&	6.13	&	4.87	&	4.74	&	6.46\\
+%			\ce{H2C=NH}	&	$^1A''(\nps)$			&	Val.	&	5.86	&	4.46	&	5.69	&	6.16	&	5.85	&	4.12	&	4.04	&	5.25\\
+%						&	$^3A''(\nps)$			&	Val.	&	4.71	&	4.72	&	4.39	&	5.49	&	4.96	&	3.25	&	3.11	&	4.63\\
+%		\end{tabular}
+%	\end{ruledtabular}
+%\end{table*}
 %%% %%% %%% %%%
@@
 To conclude, the BSE@$GT$ formalism seems to be, overall, less accurate than BSE@$GW$ in the context of the computation of molecular excitation energies.
-However, it still outperforms conventional methods such CIS and TDHF.
+However, it still outperforms conventional methods such CIS and TDHF for singlet states.
 It would be interesting to investigate its performance for the computation of ground-state correlation energies within the adiabatic connection fluctuation dissipation formalism where BSE@$GW$ has been shown to be particularly outstanding.
@@
 Work along these lines are currently under progress.
-Finally, the unrestricted and spin-flip extensions of the present formalism is currently developed.
+Finally, the unrestricted and spin-flip extensions of the present formalism are currently being developed.
 
@@
 \begin{acknowledgements}
-%The authors thank Roberto Orlando for useful discussions.
+The authors thank Roberto Orlando for useful discussions.
 PFL thanks the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481) for funding.
@@
 \section{BSE with a dynamical $T$-matrix kernel}
+\label{app:dBSE}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-02-12 Manuscript/Tmatrix.tex
first complete draft

@@
 %%% FIGURE 1 %%%
-\begin{figure*}
+\begin{figure*}[t]
 	\includegraphics[width=\textwidth]{H2}
@@
 %%% FIGURE 2 %%%
-\begin{figure}
+\begin{figure}[t]
 	\includegraphics[width=\linewidth]{H2_gap}
@@
 %%% FIGURE 3 %%%
-\begin{figure*}
+\begin{figure*}[t]
 	\includegraphics[width=0.4\linewidth]{H2_dBSE1}
@@
 %%% FIGURE 4 %%%
-\begin{figure*}
+\begin{figure*}[t]
 	\includegraphics[width=\textwidth]{BeH2}
@@
 %%% FIGURE 5 %%%
-\begin{figure}
+\begin{figure}[t]
 	\includegraphics[width=\linewidth]{BeH2_gap}
@@
 As a third and final example, we compute the excitation energies associated with the two lowest singlet and two lowest triplet excited states of water at equilibrium geometry (see Fig.~\ref{fig:H2O}).
-Note that all these excited states are of Rydberg nature and correspond to $n \to 3s$ and $n \to 3p$ transitions for the $B_1$ and $A_2$ states, respectively.
-In addition to the BSE-based models studied in the present manuscript, we have selected well-known wave function methods, namely CIS, CIS(D), TDHF, and FCI (taken as reference) and computed the excitation energies for these transitions.
+Note that all these excited states are of Rydberg nature and correspond to $n \to 3s$ and $n \to 3p$ transitions for the $B_1$ and $A_2$ states, respectively. \cite{Loos_2018a}
+In addition to the BSE-based models studied in the present manuscript, we have selected well-known wave function methods, \cite{Bene_1971,Head-Gordon_1994,Head-Gordon_1995,Dreuw_2005} namely CIS, CIS(D), TDHF, and FCI (taken as reference) and computed the excitation energies for these transitions.
 Two key observations can be made:
@@
 %%%%%%%%%%%%%%%%%%%%%%
-To conclude, the BSE@$GT$ formalism seems to be, overall, less accurate than BSE@$GW$ in the context of the computation of molecular excitation energies.
+We have derived and implemented, for the first time, the static and dynamic Bethe-Salpeter equations when one considers $T$-matrix quasiparticle energies as well as a $T$-matrix-based kernel.
+The performance of the static scheme and its perturbative dynamical correction have been assessed by computing the neutral excited states of several molecular systems.
+Our results suggest that the BSE@$GT$ formalism seems to be, overall, less accurate than BSE@$GW$ in the context of the computation of molecular excitation energies.
 However, it still outperforms conventional methods such CIS and TDHF for singlet states.
@@
 
-In order to derive the dynamical kernel $\tilde{T}_{ib,aj}$ given in equation Eq.~\eqref{eq:dT}, we follow Ref.~\onlinecite{Strinati_1980} (see also Ref.~\onlinecite{Loos_2020e}) and start from the equation for the BSE right-hand side electron-hole amplitude
+In order to derive the dynamical kernel $\tilde{T}_{ib,aj}$ given in Eq.~\eqref{eq:dT}, we follow Ref.~\onlinecite{Strinati_1980} (see also Ref.~\onlinecite{Loos_2020e}) and start \titou{from the equation for the BSE right-hand side electron-hole amplitude?!}
 \begin{equation}
@@
 where $L_0$ is given by Eq.~\eqref{eq:L0} and the $T$-matrix kernel is
-\begin{align}
+\begin{equation}
 \label{eq:T-matrix_kernel}
-	\Xi(3,5,4,6) & =  i\frac{\delta \Sigma(3,4)}{\delta G(6,5)}\approx -T(3,5,4,6).
-\end{align}
-Equation (\ref{eq:Strinati_1}) is derived by assuming a particular (resonant) pole $\omega_S=E_S-E_0>0$ of $L$ to be isolated from the other poles, which is usually the case for neutral excitations in finite systems, and  by assuming the poles of $L_0$ to be different form $\omega_S$, which is in general the case.
+	\Xi(3,5,4,6) =  i\frac{\delta \Sigma(3,4)}{\delta G(6,5)}\approx -T(3,5,4,6)
+\end{equation}
+Equation (\ref{eq:Strinati_1}) is derived by assuming that i) the (resonant) pole $\omega_S=E_S-E_0>0$ of $L$ is isolated from the other poles (which is usually the case for neutral excitations in finite systems), and  ii) the poles of $L_0$ are different form $\omega_S$ (which is also generally the case).
 The so-called $T$-matrix self-energy $\Sigma$ is given by Eq.~\eqref{eq:SigGT} with \cite{Martin_2016,Romaniello_2012}
@@
 where $v$ is the bare Coulomb operator and we neglect the functional derivative $\delta T/\delta G$ in the kernel $\Xi$. 
-We also notice that the first two terms on the right-hand side of Eq.~(\ref{eq:T-matrix}) Hartree and exchange contributions to the T matrix ($T^{\text{HF}}$), whereas the last term is the correlation contribution $T^c=T-T^{\text{HF}}$.
+The first two terms in the right-hand side of Eq.~\eqref{eq:T-matrix} are the Hartree and exchange contributions to the $T$-matrix, whereas the last term is the correlation contribution.
 Making the time dependence of Eq.~\eqref{eq:Strinati_1} explicit and defining $T(3,5,4,6)=- \delta(\tau^+_{35})\delta(\tau^+_{64})\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})$, one gets 
@@
 \begin{equation}
-	\Theta(\pm\tau)e^{-i\alpha \tau}=\mp\frac{1}{2\pi i}\lim_{\eta\to 0^+}\int d\omega \frac{1}{\omega-\alpha\pm i\eta}e^{-i\omega\tau}.
+	\Theta(\pm\tau)e^{-i\alpha \tau}=\mp\frac{1}{2\pi i}\lim_{\eta\to 0^+}\int d\omega \frac{1}{\omega-\alpha\pm i\eta}e^{-i\omega\tau}
 \end{equation}
@@
 \end{equation}
-Using the definition $X_{qp,S}=\mel{N}{\hat{c}^\dagger_{q}\hat{c}_p}{N,S}$, we arrive at
+Using the definition $X_{ia,S}=\mel{N}{\hat{c}^\dagger_{i}\hat{c}_a}{N,S}$, we arrive at
 
@@
 	\label{eq:egval}
-	\qty(\e{a}{}-\e{i}{}-\omega_S) X_{ia,S}+\sum_{jb}X_{jb,S}\mel{ib}{}{aj}+\sum_{jb}X_{jb,S}\widetilde{T}_{ib,aj}(\omega_S)=0
+	\qty(\e{a}{}-\e{i}{}-\omega_S) X_{ia,S}+\sum_{jb}X_{jb,S}\mel{ib}{}{aj} \titou{-} \sum_{jb}X_{jb,S}\widetilde{T}_{ib,aj}(\omega_S)=0
 \end{equation}
@@
 \label{eq:H2preso_eigen}
-	A_{ia,jb}(\omega_S) X_{jb,S}=\omega_S X_{ia,S}
+	\titou{\sum_{jb}} A_{ia,jb}(\omega_S) X_{jb,S}=\omega_S X_{ia,S}
 \end{equation}
@@
 \begin{equation}
-	A_{ia,jb}(\omega_S)=(\e{a}{}-\e{i}{})\delta_{ij}\delta_{ab} +\mel{ib}{}{aj}+\widetilde{T}_{ib,aj}(\omega_S).
+	A_{ia,jb}(\omega_S)=(\e{a}{}-\e{i}{})\delta_{ij}\delta_{ab} + \mel{ib}{}{aj} \titou{-} \widetilde{T}_{ib,aj}(\omega_S).
 \end{equation}
 %Here $H_{ia,jb}(\omega_S)=A_{ia,jb}(\omega_S)$ and $H_{ia,bj}(\omega_S)=B_{ia,jb}(\omega_S)$.
-If one drops the dynamical part $\widetilde{T}$, one ends up with the usual time-dependent Hartree-Fock (TDHF) equations. 
-To calculate the correlation contribution, one must employ \eqref{eq:T} in Eq.~\eqref{eq:H2preso_eigen_2_T}, and after integration over the frequency, it yields Eq.~\eqref{eq:dT}.
+If one drops the dynamical part $\widetilde{T}$, one ends up with the usual time-dependent Hartree-Fock (TDHF) equations. \cite{Dreuw_2005}
+To calculate the correlation contribution, one must employ Eq.~\eqref{eq:T} in Eq.~\eqref{eq:H2preso_eigen_2_T}, and after integration over the frequency, it yields Eq.~\eqref{eq:dT}.
 

### 2022-02-12 Manuscript/Tmatrix.tex
minor corrections

@@
 One of the key features of the $T$-matrix approximation is its exactness up to the second order thanks to the inclusion of second-order exchange diagrams.
-This class of diagrams, which are particularly important in molecular systems and explain the improvement brought by the second-order screened exchange (SOSEX) correction applied to $GW$, \cite{Romaniello_2009a,Ren_2015,Loos_2018b} are well known to be missing in the $GW$ approximation.
+This class of diagrams, which are particularly important in few-electron molecular systems \cite{Casida_1991,Hirata_2015,Hirata_2017} and explain the improvement brought by the second-order screened exchange (SOSEX) correction applied to $GW$, \cite{Romaniello_2009a,Ren_2015,Loos_2018b} are well known to be missing in the $GW$ approximation.
 
@@
 The pp-RPA problem yields, in the absence of instabilities (which should not appear in Coulombic systems with repulsive interactions only \cite{Scuseria_2013}), $\Nvir(\Nvir-1)/2$ positive eigenvalues $\Om{n}{N+2}$ and $\Nocc(\Nocc-1)/2$ negative eigenvalues $\Om{n}{N-2}$, which  correspond respectively to double attachments and double detachments.
-The pp-RPA correlation energies is given by \cite{Peng_2013,Scuseria_2013}
+The pp-RPA correlation energy is given by \cite{Peng_2013,Scuseria_2013}
 \begin{equation}
@@
 \end{equation}
-is the renormalization factor.
-Other levels of self-consistency can be considered like the partially self-consistent \textit{``eigenvalue''} $GT$ (ev$GT$)  \cite{Hybertsen_1986,Shishkin_2007,Blase_2011,Faber_2011,Rangel_2016,Gui_2018} or the quasiparticle self-consistent $GT$ (qs$GT$) \cite{Faleev_2004,vanSchilfgaarde_2006,Kotani_2007,Ke_2011,Kaplan_2016} schemes.
+is the renormalization factor or weight of the quasiparticle solution.
+Other levels of (partial) self-consistency can be considered like the \textit{``eigenvalue''} self-consistent $GT$ (ev$GT$)  \cite{Hybertsen_1986,Shishkin_2007,Blase_2011,Faber_2011,Rangel_2016,Gui_2018} or the quasiparticle self-consistent $GT$ (qs$GT$) \cite{Faleev_2004,vanSchilfgaarde_2006,Kotani_2007,Ke_2011,Kaplan_2016} schemes.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%
-Like the one-body Green's function is the pillar of the $GW$ and $GT$ approximations, the two-body Green's function $G_2$ is the key quantity of the Bethe-Salpeter equation (BSE) formalism of many-body perturbation theory \cite{Salpeter_1951,Strinati_1988,Blase_2018,Blase_2020} via its link with the two-body correlation function $L$ which satisfies the self-consistent BSE
+Like the one-body Green's function is the pillar of the $GW$ and $GT$ approximations, the two-body Green's function $G_2$ is the central quantity of the Bethe-Salpeter equation (BSE) formalism of many-body perturbation theory \cite{Salpeter_1951,Strinati_1988,Blase_2018,Blase_2020} via its link with the two-body correlation function $L$ which satisfies the self-consistent BSE
 \begin{multline}
@@
 Solving the static BSE [see Eq.~\eqref{eq:BSE}] yields the (zeroth-order) static $\Om{S}{\BSE}$ excitation energies and their corresponding eigenvectors $\bX{S}{\BSE}$ and $\bY{S}{\BSE}$. 
-The first-order correction to the $S$th excitation energy is, within the dynamical Tamm-Dancoff approximation,
+The first-order correction to the $S$th excitation energy is, within the dTDA,
 \begin{equation}

### 2022-02-14 Manuscript/Tmatrix.tex
modifs pina

@@
 
-In order to derive the dynamical kernel $\tilde{T}_{ib,aj}$ given in Eq.~\eqref{eq:dT}, we follow Ref.~\onlinecite{Strinati_1980} (see also Ref.~\onlinecite{Loos_2020e}) and start \titou{from the equation for the BSE right-hand side electron-hole amplitude?!}
+In order to derive the dynamical kernel $\tilde{T}_{ib,aj}$ given in Eq.~\eqref{eq:dT}, we follow Ref.~\onlinecite{Strinati_1980} (see also Ref.~\onlinecite{Loos_2020e}) and start from the equation for the BSE  amplitude
 \begin{equation}
@@
 	\label{eq:egval}
-	\qty(\e{a}{}-\e{i}{}-\omega_S) X_{ia,S}+\sum_{jb}X_{jb,S}\mel{ib}{}{aj} \titou{-} \sum_{jb}X_{jb,S}\widetilde{T}_{ib,aj}(\omega_S)=0
+	\qty(\e{a}{}-\e{i}{}-\omega_S) X_{ia,S}+\sum_{jb}X_{jb,S}\mel{ib}{}{aj} - \sum_{jb}X_{jb,S}\widetilde{T}_{ib,aj}(\omega_S)=0
 \end{equation}
@@
 \label{eq:H2preso_eigen}
-	\titou{\sum_{jb}} A_{ia,jb}(\omega_S) X_{jb,S}=\omega_S X_{ia,S}
+	\sum_{jb} A_{ia,jb}(\omega_S) X_{jb,S}=\omega_S X_{ia,S}
 \end{equation}
@@
 \begin{equation}
-	A_{ia,jb}(\omega_S)=(\e{a}{}-\e{i}{})\delta_{ij}\delta_{ab} + \mel{ib}{}{aj} \titou{-} \widetilde{T}_{ib,aj}(\omega_S).
+	A_{ia,jb}(\omega_S)=(\e{a}{}-\e{i}{})\delta_{ij}\delta_{ab} + \mel{ib}{}{aj} - \widetilde{T}_{ib,aj}(\omega_S).
 \end{equation}

### 2022-02-14 Manuscript/Tmatrix.tex
OK for T2

@@
 \label{eq:Z}
-	\zeta_{S} = \qty[ 1 - \T{(\bX{S}{\BSE})} \cdot \left. \pdv{\bA{}{(1)}(\Om{S}{})}{\Om{S}{}} \right|_{\Om{S}{} = \Om{S}{\BSE}} \cdot \bX{S}{\BSE} ]^{-1}
+	\zeta_{S} = \qty[ 1 - \T{(\bX{S}{\BSE})} \cdot \eval{\pdv{\bA{}{(1)}(\Om{S}{})}{\Om{S}{}}}_{\Om{S}{} = \Om{S}{\BSE}} \cdot \bX{S}{\BSE} ]^{-1}
 \end{equation}
@@
 The cost of the dynamical correction, which is thoroughly discussed in Ref.~\onlinecite{Loos_2020h}, is more expensive but is again equivalent in both formalisms.
-The computational cost associated with the computation of the $T$-matrix and the screening $W$ both scale as $\order*{\Norb^6}$ as one must obtain, respectively, all the eigenvalues and eigenvectors of the pp-RPA and ph-RPA problems.
+The computational cost associated with the computation of the $T$-matrix and the screening $W$ both scale as $\order*{\Norb^6}$ as one must obtain all the eigenvalues and eigenvectors of the pp-RPA and ph-RPA problems, respectively.
 However, the prefactor of the pp-RPA calculation is significantly larger than its ph-RPA counterpart due to the larger size of the pp-RPA matrices and its non-Hermitian nature.
@@
 The variation of the lowest singlet and triplet excitation energies as a function of the distance $R_{\ce{Be-H}}$ is shown in Fig.~\ref{fig:BeH2}, while the quasiparticle energies of the frontier orbitals and the associated (fundamental) gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:BeH2_gap}.
+All calculations are performed with the cc-pVDZ basis.
 Again, one notes that the $G_0W_0$ and $G_0T_0$ quasiparticle energies are very similar near the Fermi level.
@@
 Here, one can show that dynamical corrections improves in most cases the agreement between BSE and FCI.
-All calculations are performed with the cc-pVDZ basis.
 
 For the four lowest singlet excited states (left panel of Fig.~\ref{fig:BeH2}), dBSE@$G_0T_0$ is clearly better than dBSE@$G_0W_0$, while the opposite trend is observed for the four lowest triplet states (right panel of Fig.~\ref{fig:BeH2}).
-Note that, for large $R_{\ce{Be-H}}$, the two BSE-based schemes provide only a qualitative description of the excited states with error of several \si{\eV}.
+Note that, for large $R_{\ce{Be-H}}$, the two BSE-based schemes provide only a qualitative description of the excited states with errors of several \si{\eV}.
 Nonetheless, the overall ordering of the excited states are globally respected.
@@
 	\caption{Error with respect to FCI for the singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{H2O} at equilibrium geometry computed at various levels of theory with the aug-cc-pVDZ basis.
-	The geometry as well as the reference FCI values have been extracted from the QUEST database. \cite{Veril_2021}
+	The geometry and the reference FCI values have been extracted from the QUEST database. \cite{Veril_2021}
 	Raw data are reported in {\SupInf}.}
@@
 Note that all these excited states are of Rydberg nature and correspond to $n \to 3s$ and $n \to 3p$ transitions for the $B_1$ and $A_2$ states, respectively. \cite{Loos_2018a}
-In addition to the BSE-based models studied in the present manuscript, we have selected well-known wave function methods, \cite{Bene_1971,Head-Gordon_1994,Head-Gordon_1995,Dreuw_2005} namely CIS, CIS(D), TDHF, and FCI (taken as reference) and computed the excitation energies for these transitions.
+In addition to the BSE-based models studied in the present manuscript, we have selected well-known wave function methods, \cite{Bene_1971,Head-Gordon_1994,Head-Gordon_1995,Dreuw_2005} namely CIS, CIS(D), TDHF, and FCI (taken as reference) and computed the excitation energies of these transitions.
+It is worth mentioning here that the TDHF (or RPAx) equations within the TDA are strictly equivalent to the CIS equation, \cite{Dreuw_2005} and that CIS(D) is a simple perturbative doubles correction to CIS, and can be considered as an excited-state analog of second-order M{\o}ller-Plesset perturbation theory.
+\cite{Head-Gordon_1994,Head-Gordon_1995}
+
 Two key observations can be made:
@@
 	\\
-	+ i \int d7 d8 v(\bx_3,\bx_5)G(\bx_3,\bx_7;\tau_{38})G(\bx_5,\bx_8;\tau^+_{38})\Bar{T}(\bx_7,\bx_8,\bx_4,\bx_6;\tau_{84}).
+	+ i \int d7 d8 v(\bx_3,\bx_5)G(\bx_3,\bx_7;\tau_{38})G(\bx_5,\bx_8;\tau^+_{38})\Bar{T}(\bx_7,\bx_8,\bx_4,\bx_6;\tau_{84})
 \end{multline}
@@
 	\\
-	 \times \Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}.
+	 \times \Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}
 \end{multline}
-Using the Lehman representation of the one-body Green's function in the quasiparticle approximation given by Eq.~\eqref{eq:G},
-%$$G(x_1,x_2;\omega)=\sum_{p}\frac{\psi_p(x_1)\psi_p^*(x_2)}{\omega-\epsilon_p+ i\eta \text{sgn}(\epsilon_p-\mu)},$$ where $\psi_p$ and $\epsilon_p$ are single-particle wavefunctions and energies, respectively, and $\mu$ the chemical potential,
-and multiply the left- and right-hand sides by $(\e{a}{}-\e{i}{}-\omega_S)\int d\bx_1 d\bx^{\prime}_1 \SO{a}(\bx_1)\SO{i}(\bx_1')$, we obtain  
+Using the Lehman representation of the one-body Green's function in the quasiparticle approximation given by Eq.~\eqref{eq:G}, and multiply the left- and right-hand sides by $(\e{a}{}-\e{i}{}-\omega_S)\int d\bx_1 d\bx^{\prime}_1 \SO{a}(\bx_1)\SO{i}(\bx_1')$, we obtain
 \begin{multline}
@@
 \end{equation}
-%with $$\langle ab|ij\rangle=\int d\bx_1d\bx_2 \SO{a}(\bx_1) \SO{b}(\bx_2)v(\bx_1,\bx_2) \SO{i}(\bx_1) \SO{j}(\bx_2),$$ 
 where the spectral representation of the dynamical $T$-matrix is
@@
 	\widetilde{T}_{ib,aj}(\omega_S)
-	= \frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\Bar{T}^c_{ib,aj}(\omega)e^{-i\omega\eta} \left[\frac{1}{\omega_S-\omega+\e{j}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{b}{}-\e{a}{}+i\eta}\right].
+	= \frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\Bar{T}^c_{ib,aj}(\omega)e^{-i\omega\eta} \qty[\frac{1}{\omega_S-\omega+\e{j}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{b}{}-\e{a}{}+i\eta}] 
  \label{eq:H2preso_eigen_2_T}
@@
 \end{equation}
-%Here $H_{ia,jb}(\omega_S)=A_{ia,jb}(\omega_S)$ and $H_{ia,bj}(\omega_S)=B_{ia,jb}(\omega_S)$.
 If one drops the dynamical part $\widetilde{T}$, one ends up with the usual time-dependent Hartree-Fock (TDHF) equations. \cite{Dreuw_2005}

### 2022-02-14 Cover_Letter/CoverLetter.tex
Cover letter

\documentclass[10pt]{letter}
\usepackage{UPS_letterhead,xcolor,mhchem,mathpazo,ragged2e}
\newcommand{\alert}[1]{\textcolor{red}{#1}}
\definecolor{darkgreen}{HTML}{009900}

\begin{document}

\begin{letter}%
{To the Editors of the Journal of Chemical Physics}

\opening{Dear Editors,}

\justifying
Please find enclosed our manuscript entitled \textit{``Static and Dynamic Bethe-Salpeter Equations in the $T$-Matrix Approximation''}, which we would like you to consider as a Regular Article in the \textit{Journal of Chemical Physics}.
This contribution has never been submitted in total nor in parts to any other journal, and has been seen and approved by all authors.

The many-body Green's function Bethe-Salpeter equation (BSE) formalism is steadily asserting itself as a new efficient and accurate tool in the ensemble of computational methods available to chemists in order to predict optical excitations in molecular systems.
The BSE formalism usually relies on the well-known $GW$ approximation (which corresponds to an elegant resummation of all direct ring diagrams from the particle-hole channel and is particularly justified in the high-density or weakly-correlated regime) to compute the fundamental gap and excitonic effect. 
Here, we study an interesting alternative better suited in the low-density or strongly-correlated regime known as the $T$-matrix (or Bethe-Goldstone) approximation where one sums to infinity the ladder diagrams from the particle-particle channel.

We have derived and implemented, for the first time, the static and dynamic Bethe-Salpeter equations when one considers $T$-matrix quasiparticle energies as well as a $T$-matrix-based kernel. 
The performance of the static scheme and its perturbative dynamical correction have been assessed by computing the neutral excited states of several molecular systems and comparison with standard wave function methods as well as the $GW$-based formalism are presented.
Our results suggest that the present $T$-matrix scheme performs best in few-electron systems where the electron density remains low.
For larger systems, it seems to be, overall, less accurate than BSE@$GW$ but still outperforms conventional methods such CIS and TDHF for singlet states.

Because of the novelty of this work and its potential impact in quantum chemistry and condensed matter physics, we expect it to be of interest to a wide audience within the chemistry and physics communities.
We suggest Xavier Blase, Timothy Berkelbach, Weitao Yang, Wim Klopper, Fabien Bruneval, Patrick Rinke, and Lucia Reining as potential referees.
We look forward to hearing from you soon.

\closing{Sincerely, the authors.}

\end{letter}
\end{document}

### 2022-02-14 Manuscript/Tmatrix.tex
Cover letter

@@
 
-The non-Hermitian pp-RPA problem reads \cite{Schuck_Book,vanAggelen_2013,Peng_2013,Scuseria_2013,Yang_2013,Yang_2013b,vanAggelen_2014,Yang_2014a,Zhang_2015,Zhang_2016}
+The non-Hermitian pp-RPA problem reads \cite{Schuck_Book,vanAggelen_2013,Peng_2013,Scuseria_2013,Yang_2013,Yang_2013b,vanAggelen_2014,Yang_2014a,Zhang_2015,Zhang_2016,Bannwarth_2020}
 \begin{equation}
@@
 The cost of the dynamical correction, which is thoroughly discussed in Ref.~\onlinecite{Loos_2020h}, is more expensive but is again equivalent in both formalisms.
-The computational cost associated with the computation of the $T$-matrix and the screening $W$ both scale as $\order*{\Norb^6}$ as one must obtain all the eigenvalues and eigenvectors of the pp-RPA and ph-RPA problems, respectively.
+The computational cost associated with the computation of the $T$-matrix and the screening $W$ both scale as $\order*{\Norb^6}$ in their standard implementation as one must obtain all the eigenvalues and eigenvectors of the pp-RPA and ph-RPA problems, respectively.
+\cite{Shenvi_2014}
 However, the prefactor of the pp-RPA calculation is significantly larger than its ph-RPA counterpart due to the larger size of the pp-RPA matrices and its non-Hermitian nature.
@@
 The performance of the static scheme and its perturbative dynamical correction have been assessed by computing the neutral excited states of several molecular systems.
-Our results suggest that the BSE@$GT$ formalism seems to be, overall, less accurate than BSE@$GW$ in the context of the computation of molecular excitation energies.
+Our results suggest that, in the context of the computation of molecular excitation energies, the BSE@$GT$ formalism performs best in few-electron systems where the electron density remains low.
+For larger systems where the screening is more important, it seems to be, overall, less accurate than BSE@$GW$.
 However, it still outperforms conventional methods such CIS and TDHF for singlet states.
+
 It would be interesting to investigate its performance for the computation of ground-state correlation energies within the adiabatic connection fluctuation dissipation formalism where BSE@$GW$ has been shown to be particularly outstanding.

### 2022-02-15 Manuscript/Tmatrix.tex
modifs pina

@@
 \usepackage[normalem]{ulem}
+\newcommand{\pina}[1]{\textcolor{blue}{#1}}
 \newcommand{\titou}[1]{\textcolor{red}{#1}}
@@
 The pp-RPA problem yields, in the absence of instabilities (which should not appear in Coulombic systems with repulsive interactions only \cite{Scuseria_2013}), $\Nvir(\Nvir-1)/2$ positive eigenvalues $\Om{n}{N+2}$ and $\Nocc(\Nocc-1)/2$ negative eigenvalues $\Om{n}{N-2}$, which  correspond respectively to double attachments and double detachments.
-The pp-RPA correlation energy is given by \cite{Peng_2013,Scuseria_2013}
+The pp-RPA correlation energy is given by \pina{Is this important? We don't calculate the correlation energy} \cite{Peng_2013,Scuseria_2013}
 \begin{equation}
@@
 Based on the knowledge of the pp-RPA eigenvalues and eigenvectors, one can then construct the $T$ matrix.
-In the spinorbital basis, the correlation part of the $T$ matrix has the following expression \cite{Zhang_2016}
+In the spinorbital basis, the correlation part of the $T$ matrix has the following expression\pina{We have to be careful with the notation, because the relation between this T and the T in the appendix is a minus sign.
+See also supporting information Eqs 0.23-0.24} \cite{Zhang_2016}
 \begin{equation}
@@
 	= \sum_{in} \frac{\braket*{pi}{\chi_n^{N+2}}\braket*{qi}{\chi_n^{N+2}}}{\omega + \e{i}{} - \Om{n}{N+2} + i\eta}
-	- \sum_{an} \frac{\braket*{pa}{\chi_n^{N-2}}\braket*{qa}{\chi_n^{N-2}}}{\omega + \e{a}{} - \Om{n}{N-2} - i\eta}
+	+ \sum_{an} \frac{\braket*{pa}{\chi_n^{N-2}}\braket*{qa}{\chi_n^{N-2}}}{\omega + \e{a}{} - \Om{n}{N-2} - i\eta}
 \end{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%
-Like the one-body Green's function is the pillar of the $GW$ and $GT$ approximations, the two-body Green's function $G_2$ is the central quantity of the Bethe-Salpeter equation (BSE) formalism of many-body perturbation theory \cite{Salpeter_1951,Strinati_1988,Blase_2018,Blase_2020} via its link with the two-body correlation function $L$ which satisfies the self-consistent BSE
+Like the one-body Green's function is the pillar of the $GW$ and $GT$ approximations, the two-body Green's function $G_2$ is the central quantity of the Bethe-Salpeter equation (BSE) formalism of many-body perturbation theory \cite{Salpeter_1951,Strinati_1988,Blase_2018,Blase_2020} via its link with the two-body correlation function $L$ which satisfies the self-consistent BSE \pina{what do u mean?
+BSE as a Dyson equation?
+Maybe like this it seems that we solve self-consistently the BSE, which is not the case}
 \begin{multline}
-	 iL(1,2;1',2') = L_0(1,2;1',2') 
+	 \pina{i}L(1,2;1',2') = L_0(1,2;1',2') 
 	 \\
@@
 \end{equation}
-is the so-called BSE kernel that takes into account the self-consistent variation of $\Sigma$ with respect to the variation of $G$.
+is the so-called BSE kernel that takes into account the self-consistent variation \pina{what do u mean?} of $\Sigma$ with respect to the variation of $G$.
 By taking into account the interaction of the excited electron and its hole left behind (the infamous excitonic effect), the BSE is able to faithfully model (neutral) optical excitations as measured by absorption spectroscopy.
@@
 	\widetilde{T}_{pq,rs}(\omega) 
-		& = \sum_{n} \frac{\braket*{pq}{\chi_n^{N+2}}\braket*{rs}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2} + (\e{i}{\GT} + \e{j}{\GT}) + i\eta}
+		& = \sum_{n} \frac{\braket*{pq}{\chi_n^{N+2}}\braket*{rs}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2} + (\pina{\e{i}{\GT}} + \pina{\e{j}{\GT}}) + i\eta}
 		\\
-		& + \sum_{n} \frac{\braket*{pq}{\chi_n^{N-2}}\braket*{rs}{\chi_n^{N-2}}}{\omega + \Om{n}{N-2} - (\e{a}{\GT} + \e{b}{\GT}) + i\eta}
+		& + \sum_{n} \frac{\braket*{pq}{\chi_n^{N-2}}\braket*{rs}{\chi_n^{N-2}}}{\omega + \Om{n}{N-2} - (\pina{\e{a}{\GT}} + \pina{\e{b}{\GT}}) + i\eta}
 \end{split}
@@
 
-Similar observations can be made for the triplet states, the $GW$- and $GT$-based formalisms yielding very similar excitation energies, except maybe for the $\text{c}\,{}^3\Pi_u$ state for which BSE@$G_0W_0$ has clearly the edge.
+Similar observations can be made for the triplet states, the $GW$- and $GT$-based formalisms yielding very similar excitation energies, except \pina{maybe} for the $\text{c}\,{}^3\Pi_u$ state for which BSE@$G_0W_0$ has clearly the edge.
 Moreover, triplet instabilities seems to affect BSE@$G_0T_0$ slightly earlier than BSE@$G_0W_0$.
@@
 	\chi_S(\bx_1,\bx_{1'},\tau_{11'})e^{-i\omega_S(t_1+t_{1'})/2}
-	=-i\int d3d4d5d6 G(\bx_1,\bx_3;\tau_{13})G(\bx_4,\bx_{1'};\tau_{11'})
+	=-i\int d\bx_3d\bx_4d\bx_5d\bx_6\int dt_3dt_4 G(\bx_1,\bx_3;\tau_{13})G(\bx_4,\bx_{1'};\tau_{11'})
 	\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}
@@
 	\\
-	+ i \int d7 d8 v(\bx_3,\bx_5)G(\bx_3,\bx_7;\tau_{38})G(\bx_5,\bx_8;\tau^+_{38})\Bar{T}(\bx_7,\bx_8,\bx_4,\bx_6;\tau_{84})
+	+ i \int d\bx_7 d\bx_8\int t_ v(\bx_3,\bx_5)G(\bx_3,\bx_7;\tau_{37})G(\bx_5,\bx_8;\tau^+_{37})\Bar{T}(\bx_7,\bx_8,\bx_4,\bx_6;\tau_{74})
 \end{multline}
@@
 	\\
-    = -\sum_{jb}\mel{N}{\hat{c}^\dagger_{j}\hat{c}_b}{N,S}
-    \qty{ -\frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\ \Bar{T}_{ib,aj}(\omega) e^{-i\omega\eta} \qty[\frac{1}{\omega_S-\omega+\e{j}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{b}{}-\e{a}{}+i\eta} ] }
+    = \sum_{jb}\mel{N}{\hat{c}^\dagger_{j}\hat{c}_b}{N,S}
+    \qty{ \frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\ \Bar{T}_{ib,aj}(\omega) e^{-i\omega\eta} \qty[\frac{1}{\omega_S-\omega+\e{j}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{b}{}-\e{a}{}+i\eta} ] }
 \end{multline}
@@
 	\widetilde{T}_{ib,aj}(\omega_S)
-	= \frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\Bar{T}^c_{ib,aj}(\omega)e^{-i\omega\eta} \qty[\frac{1}{\omega_S-\omega+\e{j}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{b}{}-\e{a}{}+i\eta}] 
+	= -\frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\Bar{T}^c_{ib,aj}(\omega)e^{-i\omega\eta} \qty[\frac{1}{\omega_S-\omega+\e{j}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{b}{}-\e{a}{}+i\eta}] 
  \label{eq:H2preso_eigen_2_T}
@@
 If one drops the dynamical part $\widetilde{T}$, one ends up with the usual time-dependent Hartree-Fock (TDHF) equations. \cite{Dreuw_2005}
-To calculate the correlation contribution, one must employ Eq.~\eqref{eq:T} in Eq.~\eqref{eq:H2preso_eigen_2_T}, and after integration over the frequency, it yields Eq.~\eqref{eq:dT}.
+To calculate the correlation contribution, one must employ $\Bar{T}^c_{ib,aj}(\omega)=-{T}_{ib,aj}(\omega)$ (with ${T}_{ib,aj}$ given in Eq.~\eqref{eq:T}) in Eq.~\eqref{eq:H2preso_eigen_2_T}, and after integration over the frequency, it yields Eq.~\eqref{eq:dT}.
 

### 2022-02-15 Manuscript/Tmatrix.tex
clean up tex and figures

@@
 \newcommand{\tabc}[1]{\multicolumn{1}{c}{#1}}
-\newcommand{\SupInf}{\textcolor{blue}{supporting information}}
+\newcommand{\SupMat}{\textcolor{blue}{supplementary material}}
 \newcommand{\QP}{\textsc{quantum package}}
@@
 \begin{figure*}[t]
-	\includegraphics[width=\textwidth]{H2}
+	\includegraphics[width=\textwidth]{fig1}
 	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
-	Raw data are reported in {\SupInf}.}
+	Raw data are reported in {\SupMat}.}
 	\label{fig:H2}
@@
 \begin{figure}[t]
-	\includegraphics[width=\linewidth]{H2_gap}
+	\includegraphics[width=\linewidth]{fig2}
 	\caption{HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap (in \si{\eV}) of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed at the $G_0W_0$ (blue) and $G_0T_0$ (red) levels with the cc-pVTZ basis.
-	Raw data are reported in {\SupInf}.}
+	Raw data are reported in {\SupMat}.}
 	\label{fig:H2_gap}
@@
 \begin{figure*}[t]
-	\includegraphics[width=0.4\linewidth]{H2_dBSE1}
+	\includegraphics[width=0.4\linewidth]{fig3a}
 	\hspace{0.1\linewidth}
-	\includegraphics[width=0.4\linewidth]{H2_dBSE3}
+	\includegraphics[width=0.4\linewidth]{fig3b}
 	\caption{
@@
 	The cc-pVTZ basis is employed for all calculations.
-	Raw data are reported in {\SupInf}.}
+	Raw data are reported in {\SupMat}.}
 	\label{fig:H2_dBSE}
@@
 \begin{figure*}[t]
-	\includegraphics[width=\textwidth]{BeH2}
+	\includegraphics[width=\textwidth]{fig4}
 	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{BeH2} as a function of the distance $R_{\ce{Be-H}}$ (in \si{\angstrom}) computed at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVDZ basis.
 	The dynamically-corrected BSE excitation energies are represented as thin lines for dBSE@$G_0W_0$ (blue) and dBSE@$G_0T_0$ (red).
-	Raw data are reported in {\SupInf}.}
+	Raw data are reported in {\SupMat}.}
 	\label{fig:BeH2}
@@
 \begin{figure}[t]
-	\includegraphics[width=\linewidth]{BeH2_gap}
+	\includegraphics[width=\linewidth]{fig5}
 	\caption{HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap (in \si{\eV}) of \ce{BeH2} as a function of the internuclear distance $R_{\ce{Be-H}}$ (in \si{\angstrom}) computed at the BSE@$G_0W_0$ (blue) and BSE@$G_0T_0$ (red) levels with the cc-pVDZ basis.
-	Raw data are reported in {\SupInf}.}
+	Raw data are reported in {\SupMat}.}
 	\label{fig:BeH2_gap}
@@
 \begin{figure*}
-	\includegraphics[width=\linewidth]{H2O}
+	\includegraphics[width=\linewidth]{fig6}
 	\caption{Error with respect to FCI for the singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{H2O} at equilibrium geometry computed at various levels of theory with the aug-cc-pVDZ basis.
 	The geometry and the reference FCI values have been extracted from the QUEST database. \cite{Veril_2021}
-	Raw data are reported in {\SupInf}.}
+	Raw data are reported in {\SupMat}.}
 	\label{fig:H2O}
@@
 These general trends are also observed for other systems and they nicely evidence the crucial role of the screening in $GW$, hinting that a screened version of the $T$-matrix formalism as proposed in Ref.~\onlinecite{Romaniello_2012} might be a promising way for improvement.
-
-%%% TABLE I %%%
-%\begin{table*}
-%	\caption{Singlet and triplet excitation energies (in \si{\eV}) of various molecular systems at equilibrium geometry computed at various levels of theory with the aug-cc-pVDZ basis set.
-%	The corresponding equilibrium geometries as well as the reference FCI values have been extracted from the QUEST database. \cite{Veril_2021}}
-%	\label{tab:mol}
-%	\begin{ruledtabular}
-%		\begin{tabular}{llccccccccc}
-%					&			&		&	\mc{8}{c}{Methods}																\\
-%			\cline{4-11}
-%			Mol.	&	State	&	Nature						&	CIS		&	CIS(D)	&	TDHF	&	BSE@$G_0W_0$	&	dBSE@$G_0W_0$	&	BSE@$G_0T_0$	&	dBSE@$G_0T_0$	&	FCI	\\
-%			\hline
-%			\ce{H2O}	&	$^1B_1(n \to 3s)$		&	Ryd.	&	8.66	&	6.61	&	8.61	&	7.70	&	7.62	&	6.84	&	6.80	&	7.53\\
-%						&	$^1A_2(n \to 3p)$		&	Ryd.	&	10.34	&	8.33	&	10.30	&	9.41	&	9.34	&	8.60	&	8.56	&	9.32\\
-%						&	$^3B_1(n \to 3s)$		&	Ryd.	&	7.98	&	6.69	&	7.86	&	7.23	&	7.09	&	6.30	&	6.23	&	7.14\\
-%						&	$^3A_2(n \to 3p)$		&	Ryd.	&	10.01	&	8.70	&	9.89	&	9.22	&	9.11	&	8.36	&	8.29	&	9.14\\
-%			\ce{HCl}	&	$^1\Pi$					&	CT		&	8.36	&	7.87	&	8.31	&	8.04	&	7.95	&	7.42	&	7.38	&	7.82\\
-%			\ce{HC#CH}	&	$^1\Sigma_u^-(\pps)$	&	Val.	&	6.28	&	6.29	&	5.91	&	7.27	&	6.96	&	5.64	&	5.55	&	7.20\\
-%						&	$^1\Delta_u(\pps)$		&	Val.	&	6.62	&	6.97	&	6.44	&	7.61	&	7.33	&	5.87	&	5.81	&	7.51\\
-%						&	$^3\Sigma_u^+(\pps)$	&	Val.	&	4.52	&	5.75	&	2.19	&	5.63	&	5.12	&	4.02	&	3.83	&	5.50\\
-%						&	$^3\Delta_u(\pps)$		&	Val.	&	5.45	&	6.65	&	4.52	&	6.52	&	6.13	&	4.87	&	4.74	&	6.46\\
-%			\ce{H2C=NH}	&	$^1A''(\nps)$			&	Val.	&	5.86	&	4.46	&	5.69	&	6.16	&	5.85	&	4.12	&	4.04	&	5.25\\
-%						&	$^3A''(\nps)$			&	Val.	&	4.71	&	4.72	&	4.39	&	5.49	&	4.96	&	3.25	&	3.11	&	4.63\\
-%		\end{tabular}
-%	\end{ruledtabular}
-%\end{table*}
-%%% %%% %%% %%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The \hypertarget{SI}{data} that support the findings of this study are openly available in Zenodo at \href{http://doi.org/XX.XXXX/zenodo.XXXXXXX}{http://doi.org/XX.XXXX/zenodo.XXXXXXX}.
+The data that supports the findings of this study are available within the article and its supplementary material.
 

### 2022-02-15 Manuscript/Tmatrix.tex
pina corrections

@@
 \newcommand{\GOWO}{$G_0W_0$}
-\newcommand{\Hxc}{\text{Hxc}}
-\newcommand{\xc}{\text{xc}}
-\newcommand{\Ha}{\text{H}}
-\newcommand{\co}{\text{c}}
-\newcommand{\x}{\text{x}}
 
@@
 \newcommand{\eKS}[1]{\eps^\text{KS}_{#1}}
-\newcommand{\eQP}[1]{\eps^\text{QP}_{#1}}
-\newcommand{\eGOWO}[1]{\eps^\text{\GOWO}_{#1}}
-\newcommand{\eGW}[1]{\eps^{GW}_{#1}}
-\newcommand{\eevGW}[1]{\eps^\text{\evGW}_{#1}}
-\newcommand{\eGnWn}[2]{\eps^\text{\GnWn{#2}}_{#1}}
 \newcommand{\Om}[2]{\Omega_{#1}^{#2}}
-\newcommand{\tOm}[2]{\Tilde{\Omega}_{#1}^{#2}}
 
 % Matrix elements
-\newcommand{\tA}[2]{\Tilde{A}_{#1}^{#2}}
-\renewcommand{\S}[1]{S_{#1}}
-\newcommand{\ABSE}[2]{A_{#1}^{#2,\text{BSE}}}
-\newcommand{\BBSE}[2]{B_{#1}^{#2,\text{BSE}}}
-\newcommand{\ARPA}[2]{A_{#1}^{#2,\text{RPA}}}
-\newcommand{\BRPA}[2]{B_{#1}^{#2,\text{RPA}}}
-\newcommand{\ARPAx}[2]{A_{#1}^{#2,\text{RPAx}}}
-\newcommand{\BRPAx}[2]{B_{#1}^{#2,\text{RPAx}}}
-\newcommand{\G}[1]{G_{#1}}
-\newcommand{\LBSE}[1]{L_{#1}}
-\newcommand{\XiBSE}[1]{\Xi_{#1}}
-\newcommand{\Po}[1]{P_{#1}}
-\newcommand{\W}[2]{W_{#1}^{#2}}
-\newcommand{\tW}[2]{\widetilde{W}_{#1}^{#2}}
-\newcommand{\Wc}[1]{W^\text{c}_{#1}}
-\newcommand{\vc}[1]{v_{#1}}
 \newcommand{\Sig}[2]{\Sigma_{#1}^{#2}}
 \newcommand{\SigC}[1]{\Sigma^\text{c}_{#1}}
-\newcommand{\SigX}[1]{\Sigma^\text{x}_{#1}}
-\newcommand{\SigXC}[1]{\Sigma^\text{xc}_{#1}}
-\newcommand{\Z}[1]{Z_{#1}}
 \newcommand{\MO}[1]{\phi_{#1}}
@@
 \newcommand{\ERI}[2]{(#1|#2)}
-\newcommand{\rbra}[1]{(#1|}
-\newcommand{\rket}[1]{|#1)}
-\newcommand{\sERI}[2]{[#1|#2]}
-
-%% bold in Table
-\newcommand{\bb}[1]{\textbf{#1}}
-\newcommand{\rb}[1]{\textbf{\textcolor{red}{#1}}}
-\newcommand{\gb}[1]{\textbf{\textcolor{darkgreen}{#1}}}
-
-% excitation energies
-\newcommand{\OmRPA}[1]{\Omega_{#1}^{\text{RPA}}}
-\newcommand{\OmRPAx}[1]{\Omega_{#1}^{\text{RPAx}}}
-\newcommand{\OmBSE}[1]{\Omega_{#1}^{\text{BSE}}}
 
@@
 \newcommand{\bI}{\mathbf{1}}
-\newcommand{\bvc}{\mathbf{v}}
-\newcommand{\bSig}{\mathbf{\Sigma}}
-\newcommand{\bSigX}{\mathbf{\Sigma}^\text{x}}
-\newcommand{\bSigC}{\mathbf{\Sigma}^\text{c}}
-\newcommand{\bSigGW}{\mathbf{\Sigma}^{GW}}
-\newcommand{\be}{\mathbf{\epsilon}}
-\newcommand{\beGW}{\mathbf{\epsilon}^{GW}}
-\newcommand{\beGnWn}[1]{\mathbf{\epsilon}^\text{\GnWn{#1}}}
-\newcommand{\bde}{\mathbf{\Delta\epsilon}}
-\newcommand{\bdeHF}{\mathbf{\Delta\epsilon}^\text{HF}}
-\newcommand{\bdeGW}{\mathbf{\Delta\epsilon}^{GW}}
 \newcommand{\bOm}[1]{\mathbf{\Omega}^{#1}}
@@
 \newcommand{\bY}[2]{\mathbf{Y}_{#1}^{#2}}
-\newcommand{\bZ}[2]{\mathbf{Z}_{#1}^{#2}}
-\newcommand{\bK}{\mathbf{K}}
-\newcommand{\bP}[1]{\mathbf{P}^{#1}}
-
-% units
-\newcommand{\IneV}[1]{#1 eV}
-\newcommand{\InAU}[1]{#1 a.u.}
-\newcommand{\InAA}[1]{#1 \AA}
-\newcommand{\kcal}{kcal/mol}
 
@@
 
-\newcommand{\sig}{\sigma}
-\newcommand{\bsig}{{\Bar{\sigma}}}
-\newcommand{\sigp}{{\sigma'}}
-\newcommand{\bsigp}{{\Bar{\sigma}'}}
-\newcommand{\taup}{{\tau'}}
-
-\newcommand{\up}{\uparrow}
-\newcommand{\dw}{\downarrow}
-\newcommand{\upup}{\uparrow\uparrow}
-\newcommand{\updw}{\uparrow\downarrow}
-\newcommand{\dwup}{\downarrow\uparrow}
-\newcommand{\dwdw}{\downarrow\downarrow}
-\newcommand{\spc}{\text{sc}}
-\newcommand{\spf}{\text{sf}}
-\newcommand{\ssp}{\text{ss}}
-\newcommand{\osp}{\text{os}}
-
-\newcommand{\pps}{\pi \to \pi^*}
-\newcommand{\nps}{n \to \pi^*}
+\newcommand{\cT}{\mathcal{T}}
 \DeclareSIUnit\angstrom{\text{\AA}}
@@
 One of the key features of the $T$-matrix approximation is its exactness up to the second order thanks to the inclusion of second-order exchange diagrams.
-This class of diagrams, which are particularly important in few-electron molecular systems \cite{Casida_1991,Hirata_2015,Hirata_2017} and explain the improvement brought by the second-order screened exchange (SOSEX) correction applied to $GW$, \cite{Romaniello_2009a,Ren_2015,Loos_2018b} are well known to be missing in the $GW$ approximation.
+This class of diagrams, which are particularly important in few-electron molecular systems \cite{Casida_1991,Ortiz_2013,Hirata_2015,Hirata_2017} and explain the improvement brought by the second-order screened exchange (SOSEX) correction applied to $GW$, \cite{Romaniello_2009a,Ren_2015,Loos_2018b} are well known to be missing in the $GW$ approximation.
+\titou{Pina is going to add a comment.}
 
@@
 The pp-RPA problem yields, in the absence of instabilities (which should not appear in Coulombic systems with repulsive interactions only \cite{Scuseria_2013}), $\Nvir(\Nvir-1)/2$ positive eigenvalues $\Om{n}{N+2}$ and $\Nocc(\Nocc-1)/2$ negative eigenvalues $\Om{n}{N-2}$, which  correspond respectively to double attachments and double detachments.
-The pp-RPA correlation energy is given by \pina{Is this important? We don't calculate the correlation energy} \cite{Peng_2013,Scuseria_2013}
+The pp-RPA correlation energy is given by \cite{Peng_2013,Scuseria_2013}
 \begin{equation}
@@
 Based on the knowledge of the pp-RPA eigenvalues and eigenvectors, one can then construct the $T$ matrix.
-In the spinorbital basis, the correlation part of the $T$ matrix has the following expression\pina{We have to be careful with the notation, because the relation between this T and the T in the appendix is a minus sign.
-See also supporting information Eqs 0.23-0.24} \cite{Zhang_2016}
+In the spinorbital basis, the correlation part of the $T$ matrix has the following expression \cite{Zhang_2016}
 \begin{equation}
 \label{eq:T}
-	T_{pq,rs}(\omega) 
+	\cT_{pq,rs}(\omega) 
 		= \sum_{n} \frac{\braket*{pq}{\chi_n^{N+2}}\braket*{rs}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2} + i\eta}
@@
 %%%%%%%%%%%%%%%%%%%%%%
-Like the one-body Green's function is the pillar of the $GW$ and $GT$ approximations, the two-body Green's function $G_2$ is the central quantity of the Bethe-Salpeter equation (BSE) formalism of many-body perturbation theory \cite{Salpeter_1951,Strinati_1988,Blase_2018,Blase_2020} via its link with the two-body correlation function $L$ which satisfies the self-consistent BSE \pina{what do u mean?
-BSE as a Dyson equation?
-Maybe like this it seems that we solve self-consistently the BSE, which is not the case}
+Like the one-body Green's function is the pillar of the $GW$ and $GT$ approximations, the two-body Green's function $G_2$ is the central quantity of the Bethe-Salpeter equation (BSE) formalism of many-body perturbation theory \cite{Salpeter_1951,Strinati_1988,Blase_2018,Blase_2020} via its link with the two-body correlation function $L$ which satisfies the following Dyson equation
 \begin{multline}
-	 \pina{i}L(1,2;1',2') = L_0(1,2;1',2') 
+	 L(1,2;1',2') = L_0(1,2;1',2') 
 	 \\
@@
 \end{equation}
-is the so-called BSE kernel that takes into account the self-consistent variation \pina{what do u mean?} of $\Sigma$ with respect to the variation of $G$.
+is the so-called BSE kernel that takes into account the variation of $\Sigma$ with respect to the variation of $G$.
 By taking into account the interaction of the excited electron and its hole left behind (the infamous excitonic effect), the BSE is able to faithfully model (neutral) optical excitations as measured by absorption spectroscopy.
@@
 \begin{align}
-	A_{ia,jb}^{\BSE} & = \delta_{ij} \delta_{ab} (\e{a}{\GT} - \e{i}{\GT}) + \mel{ib}{}{aj} - T_{ib,aj}(\omega=0)
+	A_{ia,jb}^{\BSE} & = \delta_{ij} \delta_{ab} (\e{a}{\GT} - \e{i}{\GT}) + \mel{ib}{}{aj} - \cT_{ib,aj}(\omega=0)
 	\\ 
-	B_{ia,jb}^{\BSE} & = \mel{ij}{}{ab} - T_{ij,ab}(\omega=0)
+	B_{ia,jb}^{\BSE} & = \mel{ij}{}{ab} - \cT_{ij,ab}(\omega=0)
 \end{align}
@@
 \begin{equation}
-	A_{ia,jb}^{\dBSE}(\omega) = \delta_{ij} \delta_{ab} (\e{a}{\GT} - \e{i}{\GT}) + \mel{ib}{}{aj} - \widetilde{T}_{ib,aj}(\omega)
+	A_{ia,jb}^{\dBSE}(\omega) = \delta_{ij} \delta_{ab} (\e{a}{\GT} - \e{i}{\GT}) + \mel{ib}{}{aj} - \widetilde{\cT}_{ib,aj}(\omega)
 \end{equation}
@@
 \begin{split}
-	\widetilde{T}_{pq,rs}(\omega) 
-		& = \sum_{n} \frac{\braket*{pq}{\chi_n^{N+2}}\braket*{rs}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2} + (\pina{\e{i}{\GT}} + \pina{\e{j}{\GT}}) + i\eta}
+	\widetilde{\cT}_{ib,aj}(\omega) 
+		& = \sum_{n} \frac{\braket*{ib}{\chi_n^{N+2}}\braket*{aj}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2} + (\e{i}{\GT} + \e{j}{\GT}) + i\eta}
 		\\
-		& + \sum_{n} \frac{\braket*{pq}{\chi_n^{N-2}}\braket*{rs}{\chi_n^{N-2}}}{\omega + \Om{n}{N-2} - (\pina{\e{a}{\GT}} + \pina{\e{b}{\GT}}) + i\eta}
+		& + \sum_{n} \frac{\braket*{ib}{\chi_n^{N-2}}\braket*{aj}{\chi_n^{N-2}}}{\omega + \Om{n}{N-2} - (\e{a}{\GT} + \e{b}{\GT}) + i\eta}
 \end{split}
@@
 	\label{eq:BSE-A1}
-	A_{ia,jb}^{(1)}(\omega) = \widetilde{T}_{ib,aj}(\omega) - T_{ib,aj}(\omega = 0)
+	A_{ia,jb}^{(1)}(\omega) = \widetilde{\cT}_{ib,aj}(\omega) - \cT_{ib,aj}(\omega = 0)
 \end{equation}
@@
 
-Similar observations can be made for the triplet states, the $GW$- and $GT$-based formalisms yielding very similar excitation energies, except \pina{maybe} for the $\text{c}\,{}^3\Pi_u$ state for which BSE@$G_0W_0$ has clearly the edge.
+Similar observations can be made for the triplet states, the $GW$- and $GT$-based formalisms yielding very similar excitation energies, except for the $\text{c}\,{}^3\Pi_u$ state for which BSE@$G_0W_0$ has clearly the edge.
 Moreover, triplet instabilities seems to affect BSE@$G_0T_0$ slightly earlier than BSE@$G_0W_0$.
@@
 	\label{eq:egval}
-	\qty(\e{a}{}-\e{i}{}-\omega_S) X_{ia,S}+\sum_{jb}X_{jb,S}\mel{ib}{}{aj} - \sum_{jb}X_{jb,S}\widetilde{T}_{ib,aj}(\omega_S)=0
+	\qty(\e{a}{}-\e{i}{}-\omega_S) X_{ia,S}+\sum_{jb}X_{jb,S}\mel{ib}{}{aj} - \sum_{jb}X_{jb,S}\widetilde{\cT}_{ib,aj}(\omega_S)=0
 \end{equation}
@@
 \begin{equation}
-	\widetilde{T}_{ib,aj}(\omega_S)
+	\widetilde{\cT}_{ib,aj}(\omega_S)
 	= -\frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\Bar{T}^c_{ib,aj}(\omega)e^{-i\omega\eta} \qty[\frac{1}{\omega_S-\omega+\e{j}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{b}{}-\e{a}{}+i\eta}] 
@@
 \begin{equation}
-	A_{ia,jb}(\omega_S)=(\e{a}{}-\e{i}{})\delta_{ij}\delta_{ab} + \mel{ib}{}{aj} - \widetilde{T}_{ib,aj}(\omega_S).
+	A_{ia,jb}(\omega_S)=(\e{a}{}-\e{i}{})\delta_{ij}\delta_{ab} + \mel{ib}{}{aj} - \widetilde{\cT}_{ib,aj}(\omega_S).
 \end{equation}
-If one drops the dynamical part $\widetilde{T}$, one ends up with the usual time-dependent Hartree-Fock (TDHF) equations. \cite{Dreuw_2005}
-To calculate the correlation contribution, one must employ $\Bar{T}^c_{ib,aj}(\omega)=-{T}_{ib,aj}(\omega)$ (with ${T}_{ib,aj}$ given in Eq.~\eqref{eq:T}) in Eq.~\eqref{eq:H2preso_eigen_2_T}, and after integration over the frequency, it yields Eq.~\eqref{eq:dT}.
+If one drops the \titou{correlation} part $\widetilde{\cT}$, one ends up with the usual time-dependent Hartree-Fock (TDHF) equations. \cite{Dreuw_2005}
+\titou{(to reformulate) To calculate the correlation contribution, one must employ $\Bar{T}^c_{ib,aj}(\omega)=-{T}_{ib,aj}(\omega)$ (with ${T}_{ib,aj}$ given in Eq.~\eqref{eq:T}) in Eq.~\eqref{eq:H2preso_eigen_2_T}, and after integration over the frequency, it yields Eq.~\eqref{eq:dT}.}
 

### 2022-02-16 Manuscript/Tmatrix.tex
pina correction for T

@@
 This class of diagrams, which are particularly important in few-electron molecular systems \cite{Casida_1991,Ortiz_2013,Hirata_2015,Hirata_2017} and explain the improvement brought by the second-order screened exchange (SOSEX) correction applied to $GW$, \cite{Romaniello_2009a,Ren_2015,Loos_2018b} are well known to be missing in the $GW$ approximation.
-\titou{Pina is going to add a comment.}
+Moreover, unlike $W$ in the $GW$ approximation, the $T$-matrix
+approximation also contains spin-flip terms; the spin structure of the $T$-matrix allows one to describe important processes like the emission of spin waves in ferromagnetics \cite{Zhukov_2004}.
+
+In this work, we focus on neutral excitations and we explore how the $T$-matrix approximation performs within the Bethe-Salpeter equation (BSE) of many-body perturbation theory.\cite{Salpeter_1951,Strinati_1988,Blase_2018,Blase_2020}
 
@@
 \end{equation}
+Considering the time structure of the $T$-matrix approximation as $T(1,3;2,4)=-\delta(t_1-t_3)\delta(t_2-t_4)\cT(\bx_1,\bx_2;\bx_4,\bx_3;t_1-t_2)$, \cite{Martin_2016} the  frequency-dependent $T$-matrix self-energy can be obtained from the Fourier transform of Eq.~\eqref{eq:SigGT} as
+\begin{multline}
+    \Sigma^{GT}(\bx_1,\bx_2;\omega) 
+    = -i \int d\bx_3 d\bx_4 \int\frac{d\omega'}{2\pi} G(\bx_4,\bx_3;\omega') \\
+    \times \cT(\bx_1,\bx_3;\bx_2,\bx_4;\omega+\omega')
+\end{multline}
 
-Based on the knowledge of the pp-RPA eigenvalues and eigenvectors, one can then construct the $T$ matrix.
-In the spinorbital basis, the correlation part of the $T$ matrix has the following expression \cite{Zhang_2016}
+The correlation part of $T$ matrix can be constructed from the knowledge of the pp-RPA eigenvalues and eigenvectors.
+In the spinorbital basis, it is defined as $\cT_{pq,rs}^c=\cT_{pq,rs}-\mel{pq}{}{rs}$ and it has the following expression \cite{Zhang_2016}}
+%In the spinorbital basis, the correlation part of the $T$ matrix has the following expression \cite{Zhang_2016}
 \begin{equation}
 \label{eq:T}
-	\cT_{pq,rs}(\omega) 
+	\cT^c_{pq,rs}(\omega) 
 		= \sum_{n} \frac{\braket*{pq}{\chi_n^{N+2}}\braket*{rs}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2} + i\eta}
@@
 \end{subequations}
-
 Combining Eqs.~\eqref{eq:G} and \eqref{eq:T}, the correlation part of the $T$-matrix self-energy reads \cite{Romaniello_2012,Martin_2016,Zhang_2017,Li_2021b}
@@
 \end{equation}
+\pina{maybe put also a superscript 'c' to the GT self-energy?}
 While the dynamical $GW$ self-energy corresponds to the downfolding of the 2h1p and 2p1h configurations on the 1h and 1p configurations via their coupling with the 1h1p configurations, respectively, \cite{Bintrim_2021a} Eq.~\eqref{eq:SigGT} shows that, in the case of the $T$-matrix approximation, the same 2h1p and 2p1h configurations are downfolded on the 1p and 1h configurations via their coupling with the 2h and 2p configurations, respectively.
@@
 %%%%%%%%%%%%%%%%%%%%%%
-Like the one-body Green's function is the pillar of the $GW$ and $GT$ approximations, the two-body Green's function $G_2$ is the central quantity of the Bethe-Salpeter equation (BSE) formalism of many-body perturbation theory \cite{Salpeter_1951,Strinati_1988,Blase_2018,Blase_2020} via its link with the two-body correlation function $L$ which satisfies the following Dyson equation
+Like the one-body Green's function is the pillar of the $GW$ and $GT$ approximations, the two-body Green's function $G_2$ is the central quantity of the BSE formalism of many-body perturbation theory \cite{Salpeter_1951,Strinati_1988,Blase_2018,Blase_2020} via its link with the two-body correlation function $L$ which satisfies the following Dyson equation
 \begin{multline}
@@
 \begin{align}
-	A_{ia,jb}^{\BSE} & = \delta_{ij} \delta_{ab} (\e{a}{\GT} - \e{i}{\GT}) + \mel{ib}{}{aj} - \cT_{ib,aj}(\omega=0)
+	A_{ia,jb}^{\BSE} & = \delta_{ij} \delta_{ab} (\e{a}{\GT} - \e{i}{\GT}) + \mel{ib}{}{aj} + \cT^c_{ib,aj}(\omega=0)
 	\\ 
-	B_{ia,jb}^{\BSE} & = \mel{ij}{}{ab} - \cT_{ij,ab}(\omega=0)
+	B_{ia,jb}^{\BSE} & = \mel{ij}{}{ab} + \cT^c_{ij,ab}(\omega=0)
 \end{align}
@@
 \begin{equation}
-	A_{ia,jb}^{\dBSE}(\omega) = \delta_{ij} \delta_{ab} (\e{a}{\GT} - \e{i}{\GT}) + \mel{ib}{}{aj} - \widetilde{\cT}_{ib,aj}(\omega)
+	A_{ia,jb}^{\dBSE}(\omega) = \delta_{ij} \delta_{ab} (\e{a}{\GT} - \e{i}{\GT}) + \mel{ib}{}{aj} + \widetilde{\cT}^c_{ib,aj}(\omega)
 \end{equation}
@@
 \begin{split}
-	\widetilde{\cT}_{ib,aj}(\omega) 
+	\widetilde{\cT}^c_{ib,aj}(\omega) 
 		& = \sum_{n} \frac{\braket*{ib}{\chi_n^{N+2}}\braket*{aj}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2} + (\e{i}{\GT} + \e{j}{\GT}) + i\eta}
@@
 	\label{eq:BSE-A1}
-	A_{ia,jb}^{(1)}(\omega) = \widetilde{\cT}_{ib,aj}(\omega) - \cT_{ib,aj}(\omega = 0)
+	A_{ia,jb}^{(1)}(\omega) = \widetilde{\cT}^c_{ib,aj}(\omega) - \cT^c_{ib,aj}(\omega = 0)
 \end{equation}
@@
 
-In order to derive the dynamical kernel $\tilde{T}_{ib,aj}$ given in Eq.~\eqref{eq:dT}, we follow Ref.~\onlinecite{Strinati_1980} (see also Ref.~\onlinecite{Loos_2020e}) and start from the equation for the BSE  amplitude
+In order to derive the dynamical kernel $\widetilde{T}_{ib,aj}$ given in Eq.~\eqref{eq:dT}, we follow Ref.~\onlinecite{Strinati_1980} (see also Ref.~\onlinecite{Loos_2020e}) and start from the equation for the BSE amplitude
 \begin{equation}
@@
 The first two terms in the right-hand side of Eq.~\eqref{eq:T-matrix} are the Hartree and exchange contributions to the $T$-matrix, whereas the last term is the correlation contribution.
-Making the time dependence of Eq.~\eqref{eq:Strinati_1} explicit and defining $T(3,5,4,6)=- \delta(\tau^+_{35})\delta(\tau^+_{64})\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})$, one gets 
+Making the time dependence of Eq.~\eqref{eq:Strinati_1} explicit and defining $T(3,5,4,6)=- \delta(\tau^+_{35})\delta(\tau^+_{64})\cT(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})$, one gets 
 \begin{equation}
@@
 	=-i\int d\bx_3d\bx_4d\bx_5d\bx_6\int dt_3dt_4 G(\bx_1,\bx_3;\tau_{13})G(\bx_4,\bx_{1'};\tau_{11'})
-	\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}
+	\cT(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}
 \end{equation}
@@
 \label{eq:T_bar}
-	\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34}) 
+	\cT(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34}) 
 	= v(\bx_3,\bx_5)\delta(\tau_{34})\delta(\bx_3,\bx_4)\delta(\bx_6,\bx_5)-v(\bx_3,\bx_5)\delta(\tau_{34})	\delta(\bx_3,\bx_6)\delta(\bx_4,\bx_5)
 	\\
-	+ i \int d\bx_7 d\bx_8\int t_ v(\bx_3,\bx_5)G(\bx_3,\bx_7;\tau_{37})G(\bx_5,\bx_8;\tau^+_{37})\Bar{T}(\bx_7,\bx_8,\bx_4,\bx_6;\tau_{74})
+	+ i \int d\bx_7 d\bx_8\int dt_ 7 v(\bx_3,\bx_5)G(\bx_3,\bx_7;\tau_{37})G(\bx_5,\bx_8;\tau^+_{37})\cT(\bx_7,\bx_8,\bx_4,\bx_6;\tau_{74})
 \end{multline}
@@
 	\\
-	 \times \Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}
+	 \times \cT(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}
 \end{multline}
@@
 	\times \qty[\Theta(\tau_{34})e^{i\e{i}{}\tau_{34}}+\Theta(-\tau_{34})e^{i(\e{a}{}-\omega_S)\tau_{34}} ]
-	\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{i\omega_S\tau_{34}/2}
+	\cT(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{i\omega_S\tau_{34}/2}
 \end{multline}
@@
     = \sum_{jb}\mel{N}{\hat{c}^\dagger_{j}\hat{c}_b}{N,S}
-    \qty{ \frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\ \Bar{T}_{ib,aj}(\omega) e^{-i\omega\eta} \qty[\frac{1}{\omega_S-\omega+\e{j}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{b}{}-\e{a}{}+i\eta} ] }
+    \qty{ \frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\ \cT_{ib,aj}(\omega) e^{-i\omega\eta} \qty[\frac{1}{\omega_S-\omega+\e{j}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{b}{}-\e{a}{}+i\eta} ] }
 \end{multline}
@@
 \begin{equation}
-	\Bar{T}_{ib,aj}(\tau_{34})=\int d\bx_3 d\bx_4 d\bx_5 d\bx_6 \SO{a}(\bx_3) \SO{i}(\bx_4)\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34}) \SO{b}(\bx_6)\SO{j}(\bx_5).
+	\cT_{ib,aj}(\tau_{34})=\int d\bx_3 d\bx_4 d\bx_5 d\bx_6 \SO{a}(\bx_3) \SO{i}(\bx_4)\cT(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34}) \SO{b}(\bx_6)\SO{j}(\bx_5).
 \end{equation}
@@
 	\label{eq:egval}
-	\qty(\e{a}{}-\e{i}{}-\omega_S) X_{ia,S}+\sum_{jb}X_{jb,S}\mel{ib}{}{aj} - \sum_{jb}X_{jb,S}\widetilde{\cT}_{ib,aj}(\omega_S)=0
+	\qty(\e{a}{}-\e{i}{}-\omega_S) X_{ia,S}+\sum_{jb}X_{jb,S}\mel{ib}{}{aj} + \sum_{jb}X_{jb,S}\widetilde{\cT}^c_{ib,aj}(\omega_S)=0
 \end{equation}
@@
 \begin{equation}
-	\widetilde{\cT}_{ib,aj}(\omega_S)
-	= -\frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\Bar{T}^c_{ib,aj}(\omega)e^{-i\omega\eta} \qty[\frac{1}{\omega_S-\omega+\e{j}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{b}{}-\e{a}{}+i\eta}] 
+	\widetilde{\cT}^c_{ib,aj}(\omega_S)
+	= \frac{i}{2\pi}\int d\omega \lim_{\eta \to 0^+}\cT^c_{ib,aj}(\omega)e^{-i\omega\eta} \qty[\frac{1}{\omega_S-\omega+\e{j}{}+\e{i}{}+i\eta}+\frac{1}{\omega_S+\omega-\e{b}{}-\e{a}{}+i\eta}] 
  \label{eq:H2preso_eigen_2_T}
 \end{equation}
+with $\cT^c_{ib,aj}=\cT_{ib,aj}-\mel{ib}{}{aj}$ the correlation part of $\cT$. 
 Equation \eqref{eq:egval} represents a non-linear eigenvalue equation to calculate the positive excitation energies of a system, which can be rewritten as
@@
 \begin{equation}
-	A_{ia,jb}(\omega_S)=(\e{a}{}-\e{i}{})\delta_{ij}\delta_{ab} + \mel{ib}{}{aj} - \widetilde{\cT}_{ib,aj}(\omega_S).
+	A_{ia,jb}(\omega_S)=(\e{a}{}-\e{i}{})\delta_{ij}\delta_{ab} + \mel{ib}{}{aj} - \widetilde{\cT}^c_{ib,aj}(\omega_S).
 \end{equation}
-If one drops the \titou{correlation} part $\widetilde{\cT}$, one ends up with the usual time-dependent Hartree-Fock (TDHF) equations. \cite{Dreuw_2005}
-\titou{(to reformulate) To calculate the correlation contribution, one must employ $\Bar{T}^c_{ib,aj}(\omega)=-{T}_{ib,aj}(\omega)$ (with ${T}_{ib,aj}$ given in Eq.~\eqref{eq:T}) in Eq.~\eqref{eq:H2preso_eigen_2_T}, and after integration over the frequency, it yields Eq.~\eqref{eq:dT}.}
+If one drops the dynamical part $\widetilde{\cT}^c$, one ends up with the usual time-dependent Hartree-Fock (TDHF) equations.
+\cite{Dreuw_2005} To calculate the correlation contribution, one can employ Eq.~\eqref{eq:T} in Eq.~\eqref{eq:H2preso_eigen_2_T}, and, after integration over the frequency, one gets Eq.~\eqref{eq:dT}.
 

### 2022-02-16 Manuscript/Tmatrix.tex
final modifs

@@
 \end{equation}
-The natural idea of combining the ph and pp channels is also possible and has been explored, for example, in the Hubbard dimer within many-body perturbation theory \cite{Romaniello_2012} and the uniform electron gas \cite{Loos_2016} within coupled-cluster theory.
+The natural idea of combining the ph and pp channels is also possible and has been explored, for example, in the Hubbard dimer within many-body perturbation theory (see Ref.~\onlinecite{Romaniello_2012} and references therein) and the uniform electron gas \cite{Loos_2016} within coupled-cluster theory.
 \cite{Shepherd_2014}
@@
 Moreover, unlike $W$ in the $GW$ approximation, the $T$-matrix
-approximation also contains spin-flip terms; the spin structure of the $T$-matrix allows one to describe important processes like the emission of spin waves in ferromagnetics \cite{Zhukov_2004}.
+approximation also contains spin-flip terms; the spin structure of the $T$-matrix allows one to describe important processes like the emission of spin waves in ferromagnetics. \cite{Zhukov_2004}
 
@@
 \end{equation}
+
 Considering the time structure of the $T$-matrix approximation as $T(1,3;2,4)=-\delta(t_1-t_3)\delta(t_2-t_4)\cT(\bx_1,\bx_2;\bx_4,\bx_3;t_1-t_2)$, \cite{Martin_2016} the  frequency-dependent $T$-matrix self-energy can be obtained from the Fourier transform of Eq.~\eqref{eq:SigGT} as
@@
 The correlation part of $T$ matrix can be constructed from the knowledge of the pp-RPA eigenvalues and eigenvectors. 
-In the spinorbital basis, it is defined as $\cT_{pq,rs}^c=\cT_{pq,rs}-\mel{pq}{}{rs}$ and it has the following expression \cite{Zhang_2016}}
-%In the spinorbital basis, the correlation part of the $T$ matrix has the following expression \cite{Zhang_2016}
+In the spinorbital basis, it is defined as $\cT^c_{pq,rs}=\cT_{pq,rs}-\mel{pq}{}{rs}$ and it has the following form \cite{Zhang_2016}
 \begin{equation}
@@
 \begin{equation}
-\label{eq:SigGT}
+\label{eq:SigGTpq}
 	\Sigma^{GT}_{pq}(\omega)
@@
 \end{equation}
-\pina{maybe put also a superscript 'c' to the GT self-energy?}
-While the dynamical $GW$ self-energy corresponds to the downfolding of the 2h1p and 2p1h configurations on the 1h and 1p configurations via their coupling with the 1h1p configurations, respectively, \cite{Bintrim_2021a} Eq.~\eqref{eq:SigGT} shows that, in the case of the $T$-matrix approximation, the same 2h1p and 2p1h configurations are downfolded on the 1p and 1h configurations via their coupling with the 2h and 2p configurations, respectively.
+While the dynamical $GW$ self-energy corresponds to the downfolding of the 2h1p and 2p1h configurations on the 1h and 1p configurations via their coupling with the 1h1p configurations, respectively, \cite{Bintrim_2021a} Eq.~\eqref{eq:SigGTpq} shows that, in the case of the $T$-matrix approximation, the same 2h1p and 2p1h configurations are downfolded on the 1p and 1h configurations via their coupling with the 2h and 2p configurations, respectively.
 
@@
 
-In order to derive the dynamical kernel $\widetilde{T}_{ib,aj}$ given in Eq.~\eqref{eq:dT}, we follow Ref.~\onlinecite{Strinati_1980} (see also Ref.~\onlinecite{Loos_2020e}) and start from the equation for the BSE amplitude
+In order to derive the dynamical kernel $\widetilde{\cT}^c_{ib,aj}$ given in Eq.~\eqref{eq:dT}, we follow Ref.~\onlinecite{Strinati_1980} (see also Ref.~\onlinecite{Loos_2020e}) and start from the equation for the BSE amplitude
 \begin{equation}
@@
 \end{equation}
-Equation (\ref{eq:Strinati_1}) is derived by assuming that i) the (resonant) pole $\omega_S=E_S-E_0>0$ of $L$ is isolated from the other poles (which is usually the case for neutral excitations in finite systems), and  ii) the poles of $L_0$ are different form $\omega_S$ (which is also generally the case).
+Equation (\ref{eq:Strinati_1}) is derived by assuming that i) the (resonant) pole $\omega_S=E_S-E_0>0$ of $L$ is isolated from the other poles (which is usually the case for neutral excitations in finite systems), and  ii) the poles of $L_0$ are different from $\omega_S$ (which is also generally the case).
 The so-called $T$-matrix self-energy $\Sigma$ is given by Eq.~\eqref{eq:SigGT} with \cite{Martin_2016,Romaniello_2012}
@@
 
-For the resonant case, \ie, $\omega_S>0$, 
+For the resonant case, \ie, $\omega_S>0$, we have
 \begin{equation}
@@
 \begin{equation}
-	A_{ia,jb}(\omega_S)=(\e{a}{}-\e{i}{})\delta_{ij}\delta_{ab} + \mel{ib}{}{aj} - \widetilde{\cT}^c_{ib,aj}(\omega_S).
+	A_{ia,jb}(\omega_S)=(\e{a}{}-\e{i}{})\delta_{ij}\delta_{ab} + \mel{ib}{}{aj} + \widetilde{\cT}^c_{ib,aj}(\omega_S).
 \end{equation}

### 2022-03-28 Response_Letter/Response_Letter.tex
response letter

\documentclass[10pt]{letter}
\usepackage{UPS_letterhead,xcolor,mhchem,ragged2e,hyperref}
\newcommand{\alert}[1]{\textcolor{red}{#1}}
\definecolor{darkgreen}{HTML}{009900}

\begin{document}

\begin{letter}%
{To the Editors of the Journal of Chemical Physics,}

\opening{Dear Editors,}

\justifying
Please find attached a revised version of the manuscript entitled 
\begin{quote}
	\textit{``Static and Dynamic Bethe-Salpeter Equations in the $T$-Matrix Approximation''}.
\end{quote}
We thank the reviewers for their constructive comments.
Our detailed responses to their comments can be found below.
For convenience, changes are highlighted in red in the revised version of the manuscript.

We look forward to hearing from you.

\closing{Sincerely, the authors.}

\newpage

%%% REVIEWER 1 %%%
\noindent \textbf{\large Authors' answer to Reviewer \#1}

{The manuscript reports neutral excitation energy calculations with the Bethe-Salpeter equation in the $T$-matrix approximation. 
The paper is well written and reports important new results.

However general conclusions like "BSE@GT performs best for few-electron systems whereas BSE@GW is better for larger systems" 
are drawn out of only 3 systems: H2, H2O and BeH2. None of the 3 can be considered as a "large" system.

I think the work would be much stronger with a more comprehensive benchmark set.}
\\
\alert{
We thanks the reviewer for these positive comments.
We are planning on performing a comprehensive benchmark in a forthcoming paper but we feel that it is currently outside the scope of the present paper which is dedicated to the introduction of a new theory and test calculations.
In accordance with the reviewer's comment, we have soften our conclusion about the accuracy of the BSE@GT.
}

\begin{enumerate}

\item 
{Eq. (3) shows the non-interacting Green's function. 
The word "non-interacting" is missing in the text (else $i$ and $a$ are not orbital indices). }
\\
\alert{
}

\item 
{In Eq. (23), the block $B^\text{BSE}$ should not have a dependence wrt $\Omega_S$ to be consistent with Eq. (20).}
\\
\alert{
Thank you for spotting this typo. 
This has been corrected.
}

\item 
{In Figs. 2 \& 5, some curves are hidden behind other curves. For instance the G0W0 LUMO is virtually impossible to distinguish. 
Having HOMO, LUMO and the band gap on the same plot is maybe not a good representation.}
\\
\alert{
We have improved Figs.~2 and 5 and we plot separately these three quantities.
}

\item 
{The GT self-energy in Eq. (12) is very different from the GW self-energy. 
But according to Fig 2 and 5, the quasiparticle energies are very similar. 
Is it something that expected? 
Are all the GW diagrams included in the the GT self-energy?}
\\
\alert{
}

\end{enumerate}

%%% REVIEWER 2 %%%
\noindent \textbf{\large Authors' answer to Reviewer \#2}

{In this work Loos and Romaniello discuss a new implementation of the Bethe-Salpeter equation (BSE) based on the T-matrix approximation. The formalism is thoroughly discussed and both a static and dynamical BSE kernel are developed. Numerical applications include the calculation of excitation energies of the H2, BeH, and H2O molecules; for the dimers different interatomic distances are considered. To establish the accuracy of the new BSE approach based on the T-matrix (BSE@G0T0), full CI reference results are provided. 
Looking at the results it seems that the T-matrix based approaches do not provide a significant improvement with respect to the traditional GW-BSE approach. This confirms that in general it is challenging to develop approximations that improve the traditional GW-BSE approach based on the ph-RPA screening. 
Nevertheless, this paper represents a significant effort in going beyond the traditional BSE and could be of interest for the ab initio simulation community and at the base of important future developments. By also considering the quality of the presentation and the soundness of the results, I recommend its publication in the Journal of Chemical Physics.}
\\
\alert{
}

\begin{enumerate}

\item 
{The abstract discusses the research that has been carried out, but one or two sentences should be added to describe the outcome/conclusions of this work.}
\\
\alert{
We have modified the abstract to include an additional sentence on the main outcome of the paper.
}

\item 
{In figures 2 and 5 the LUMO@GT curve (diamonds) is completely covered by the LUMO@GW curve (squares). 
This could confuse the reader. 
It would be better, for example, to increase the size of the diamonds to make this curve visible.}
\\
\alert{
We have improved Figs.~2 and 5 and we plot separately these three quantities.
}

\item 
{The Green's functions are built from a HF starting point but the authors mention that a self-consistent implementation is available (but not considered in the paper). 
I understand that this implementation might not be fully ready for production, but the authors could at least discuss if they expect improvements from self-consistency or by changing the starting point.}
\\
\alert{
For these small molecular systems, the improvement brought by the self-consistent schemes is going to be marginal.
We have mentioned this in the revised version of the manuscript.
}

\item 
{Since the authors provide an extensive literature review on the BSE for molecular systems (Refs. 70-87 and many others), they should also include in their references the work of D. Rocca, D. Lu, and G. Galli, J. Chem. Phys. 2010, which has been among the first ones to apply the BSE to molecules. 
}
\\
\alert{
Sorry for the omission. 
We have added the reference to the work of Galli and coworkers in due place.
}

\end{enumerate}

\end{letter}
\end{document}

### 2022-03-28 Manuscript/Tmatrix.tex
response letter

@@
 	\affiliation{\LCPQ}
-\author{Pina Romaniello}
+\author{Pina \surname{Romaniello}}
 	\email{romaniello@irsamc.ups-tlse.fr}
@@
 The moderate cost of the BSE [which scales as $\order*{K^4}$ in its standard implementation] and its all-round accuracy are the main reasons behind its growing popularity in the molecular electronic structure community.
-\cite{Rohlfing_1999a,Horst_1999,Puschnig_2002,Tiago_2003,Boulanger_2014,Jacquemin_2015a,Bruneval_2015,Jacquemin_2015b,Hirose_2015,Jacquemin_2017a,Jacquemin_2017b,Rangel_2017,Krause_2017,Gui_2018,Blase_2018,Liu_2020,Blase_2020,Holzer_2018a,Holzer_2018b,Loos_2020e,Loos_2021}
+\cite{Rohlfing_1999a,Horst_1999,Puschnig_2002,Tiago_2003,Rocca_2010,Boulanger_2014,Jacquemin_2015a,Bruneval_2015,Jacquemin_2015b,Hirose_2015,Jacquemin_2017a,Jacquemin_2017b,Rangel_2017,Krause_2017,Gui_2018,Blase_2018,Liu_2020,Blase_2020,Holzer_2018a,Holzer_2018b,Loos_2020e,Loos_2021}
 
@@
 	\begin{pmatrix}
-		\bA{}{\dBSE}(\Om{S}{})		&	\bB{}{\BSE}(\Om{S}{})	\\
-		-\bB{}{\BSE}(-\Om{S}{})	&	-\bA{}{\BSE}(-\Om{S}{})	\\
+		\bA{}{\dBSE}(\Om{S}{})		&	\bB{}{\BSE}	\\
+		-\bB{}{\BSE}	&	-\bA{}{\BSE}(-\Om{S}{})	\\
 	\end{pmatrix}

### 2022-03-28 Response_Letter/Response_Letter.tex
almost done

@@
 We are planning on performing a comprehensive benchmark in a forthcoming paper but we feel that it is currently outside the scope of the present paper which is dedicated to the introduction of a new theory and test calculations.
-In accordance with the reviewer's comment, we have soften our conclusion about the accuracy of the BSE@GT.
+Accordingly with the reviewer's comment, we have soften our conclusion about the accuracy of the BSE@GT for large systems while mentioning that a more comprehensive benchmark study would be required:
+``The overall accuracy of the present scheme still needs to be assessed for larger systems (where the screening is known to be more important). 
+For such purposes, a comprehensive benchmark study would be required and we are planning to do so in the future''
 }
@@
 \alert{
+We thank the reviewer for his/her kind comments.
 }
@@
 \alert{
-We have modified the abstract to include an additional sentence on the main outcome of the paper.
+We have modified the abstract to include an additional sentence on the main outcome of the paper: ``Our results suggest that the $T$-matrix-based formalism performs best in few-electron systems where the electron density remains low.''
 }
@@
 \alert{
-We have improved Figs.~2 and 5 and we plot separately these three quantities.
+We have improved Figs.~2 and 5 and we plot separately the three main quantities (HOMO, LUMO and gap).
 }
@@
 \alert{
-For these small molecular systems, the improvement brought by the self-consistent schemes is going to be marginal.
-We have mentioned this in the revised version of the manuscript.
+For these small molecular systems, the differences in quasiparticle energies between one-shoot and self-consistent schemes are small.
+We have mentioned this observation in the revised version of the manuscript: ``The ev$GT$ and qs$GT$ schemes have been also implemented but are not considered here, mainly because, for the small molecular systems studied here (see below), we have observed very small differences between one-shot and self-consistent quasiparticle energies.''
 }

### 2022-03-28 Manuscript/Tmatrix.tex
almost done

@@
 Comparison with more conventional schemes as well as other wave function methods are also reported.
+\alert{Our results suggest that the $T$-matrix-based formalism performs best in few-electron systems where the electron density remains low.}
 %\bigskip
@@
 Finally, the infinitesimal $\eta$ is set to zero for all calculations.
-The ev$GT$ and qs$GT$ schemes have been also implemented but are not considered here.
+\alert{The ev$GT$ and qs$GT$ schemes have been also implemented but are not considered here, mainly because, for the small molecular systems studied here (see below), we have observed very small differences between one-shot and self-consistent quasiparticle energies.}
 Although the dynamical correction is computed in the dTDA throughout, the zeroth-order excitonic Hamiltonian [see Eq.~\eqref{eq:BSE}] is always the ``full'' BSE static Hamiltonian, i.e., without TDA. 
@@
 Our results suggest that, in the context of the computation of molecular excitation energies, the BSE@$GT$ formalism performs best in few-electron systems where the electron density remains low.
-For larger systems where the screening is more important, it seems to be, overall, less accurate than BSE@$GW$.
-However, it still outperforms conventional methods such CIS and TDHF for singlet states.
+\alert{The overall accuracy of the present scheme still needs to be assessed for larger systems (where the screening is known to be more important). 
+For such purposes, a comprehensive benchmark study would be required and we are planning to do so in the future}
+%However, it still outperforms conventional methods such CIS and TDHF for singlet states.
 

### 2022-03-29 Response_Letter/Response_Letter.tex
update response letter and mansucript

@@
 We are planning on performing a comprehensive benchmark in a forthcoming paper but we feel that it is currently outside the scope of the present paper which is dedicated to the introduction of a new theory and test calculations.
-Accordingly with the reviewer's comment, we have soften our conclusion about the accuracy of the BSE@GT for large systems while mentioning that a more comprehensive benchmark study would be required:
+Accordingly to the reviewer's comment, we have soften our conclusion about the accuracy of BSE@GT for large systems while mentioning that a more comprehensive benchmark study would be required:
 ``The overall accuracy of the present scheme still needs to be assessed for larger systems (where the screening is known to be more important). 
@@
 \alert{
+This is actually not the definition of the non-interacting Green's function, but the definition of the Green's function in the quasiparticle approximations [which can be defined at the Hartree-Fock, Kohn-Sham, or $GW$ level as mentioned just below Eq.~(3)].
+Thank you for pointing out this misunderstanding; we have clarified this statement.
 }

### 2022-03-29 Manuscript/Tmatrix.tex
update response letter and mansucript

@@
 \documentclass[aip,jcp,reprint,noshowkeys,superscriptaddress]{revtex4-1}
-\usepackage{graphicx,dcolumn,bm,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,longtable,wrapfig,txfonts,siunitx}
+\usepackage{graphicx,dcolumn,bm,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,longtable,wrapfig,txfonts,siunitx,float}
 \usepackage[version=4]{mhchem}
@@
 %%%%%%%%%%%%%%%%%%%%%%
-By definition, the one-body Green's function is \cite{Martin_2016}
+By definition, \alert{in the quasiparticle approximation,} the one-body Green's function is \cite{Martin_2016}
 \begin{equation}
@@
 %%% FIGURE 1 %%%
-\begin{figure*}[t]
+\begin{figure*}
 	\includegraphics[width=\textwidth]{fig1}
@@
 %%% FIGURE 2 %%%
-\begin{figure}[t]
+\begin{figure}
 	\includegraphics[width=\linewidth]{fig2}
@@
 %%% FIGURE 3 %%%
-\begin{figure*}[t]
+\begin{figure*}
 	\includegraphics[width=0.4\linewidth]{fig3a}
@@
 %%% FIGURE 4 %%%
-\begin{figure*}[t]
+\begin{figure*}
 	\includegraphics[width=\textwidth]{fig4}
@@
 %%% FIGURE 5 %%%
-\begin{figure}[t]
+\begin{figure}
 	\includegraphics[width=\linewidth]{fig5}
@@
 \alert{The overall accuracy of the present scheme still needs to be assessed for larger systems (where the screening is known to be more important). 
-For such purposes, a comprehensive benchmark study would be required and we are planning to do so in the future}
+For such purposes, a comprehensive benchmark study would be required and we are planning to do so in the future.}
 %However, it still outperforms conventional methods such CIS and TDHF for singlet states.
@@
 \cite{Dreuw_2005} To calculate the correlation contribution, one can employ Eq.~\eqref{eq:T} in Eq.~\eqref{eq:H2preso_eigen_2_T}, and, after integration over the frequency, one gets Eq.~\eqref{eq:dT}.
-
+\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-03-29 Response_Letter/Response_Letter.tex
adding references

@@
 \\
-\alert{
-This is actually not the definition of the non-interacting Green's function, but the definition of the Green's function in the quasiparticle approximations [which can be defined at the Hartree-Fock, Kohn-Sham, or $GW$ level as mentioned just below Eq.~(3)].
-Thank you for pointing out this misunderstanding; we have clarified this statement.
+\alert{The referee is correct, Eq.~3 is not the fully interacting Green's function with the notation used in the manuscript. 
+To avoid confusion with the non-interacting Green's function, which usually refers to the case where the electron-electron interaction is switched off, we have now added to the manuscript that Eq.~3 is the Green's function within the quasiparticle approximation, meaning that it is built from one-electron energies and orbitals corresponding to a given electronic structure method, such as Hartree-Fock, Kohn-Sham, or $GW$ (retaining only the quasiparticle part).
+We have hence changed the text before Eq.
+3 as "By definition, in the quasiparticle approximation, the one-body Green's function is".
 }
@@
 \\
-\alert{
-}
+\alert{The $T$-matrix self-energy contains all the diagrams of the $GW$ self-energy up to second order in the bare Coulomb interaction (this means the Hartree-Fock self energy and the second order direct term).
+At higher order, the two approximations differ, since, as mentioned in the manuscripts, $GW$ contains the so-called bubble diagrams and the $T$-matrix the ladder diagrams. 
+Probably the fact that both approximations give similar quasiparticle energies for the small systems we study in the manuscript is due to the fact that the second-order diagrams are the most important ones in this case.
+As already mentioned in the manuscript, this trend has already been observed in the Hubbard dimer and in molecular systems. 
+We should also mention that in the case of the Hubbard dimer, the two approximations do not give similar satellite energies and amplitudes. 
+Hence, it is difficult to draw conclusions on the observed trends.}
 

### 2022-03-29 Manuscript/Tmatrix.tex
adding references

@@
 Alternatives to $GW$ do exist.
-For example, the $T$-matrix (or Bethe-Goldstone) approximation, first introduced in nuclear physics, \cite{Bethe_1957,Baym_1961,Baym_1962,Danielewicz_1984a,Danielewicz_1984b} then in condensed matter physics, \cite{Liebsch_1981,Bickers_1989,Bickers_1991,Katsnelson_1999,Katsnelson_2002,Zhukov_2005,vonFriesen_2010,Romaniello_2012,Gukelberger_2015} and more recently in quantum chemistry, \cite{Zhang_2017,Li_2021b} sums to infinity the ladder diagrams from the particle-particle (pp) channel and is justified in the low-density or strongly-correlated regime.
+For example, the $T$-matrix (or Bethe-Goldstone) approximation, first introduced in nuclear physics, \cite{Bethe_1957,Baym_1961,Baym_1962,Danielewicz_1984a,Danielewicz_1984b} then in condensed matter physics, \cite{Liebsch_1981,Bickers_1989,Bickers_1991,Katsnelson_1999,Katsnelson_2002,Zhukov_2005,vonFriesen_2010,Romaniello_2012,Gukelberger_2015,Muller_2019,Friedrich_2019,Biswas_2021} and more recently in quantum chemistry, \cite{Zhang_2017,Li_2021b} sums to infinity the ladder diagrams from the particle-particle (pp) channel and is justified in the low-density or strongly-correlated regime.
 \cite{Danielewicz_1984a,Danielewicz_1984b,Liebsch_1981,Shepherd_2014}
